---
title: "notebook20190409"
author: "Mark Hagemann"
date: "4/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I need to come up with a way to show how errors and uncertainties accumulate from nodes to reaches. 

I don't know why I haven't done this scatterplot before:

```{r}
valdf1 <- rt_valdata(rodir(18))

valdf1 %>% 
  rt_val_scatter(xvar = "gdem_val", variables = "area_total") +
  facet_wrap(~reach_id, scales = "free") +
  scale_x_log10() + scale_y_log10()

```

Now show uncertainty and stdev as errors are accumulated across nodes.

```{r}

cummse <- function(x, debias = FALSE) {
  if (debias) x <- x - mean(x)
  cumsum(x^2) / seq_along(x)
}

valdf1 %>% 
  filter(variable == "width") %>% 
  group_by(reach_id) %>% 
  arrange(node_id) %>% 
  mutate(cumul_mse = cummse(pixc_err),
         cumul_uncert = cummse(sigma_est)) %>% 
  ungroup() %>% 
  ggplot(aes(x = node_id, y = sqrt(cumul_mse))) +
  geom_line() + 
  geom_line(aes(y = sqrt(cumul_uncert)), color = "red") +
  facet_wrap(~reach_id, scales = "free_x") +
  scale_y_log10()
```


Show as width--i.e. divide by node length. 

```{r}


plotdf1 <- rodir(18) %>% 
  rt_valdata(flag_out_nodes = TRUE) %>% 
  filter(variable == "area_total") %>% 
  group_by(reach_id) %>% 
  arrange(node_id) %>% 
  mutate(cumul_err = (cumsum(pixc_err) / cumsum(nodelen)),
         cumul_mse = cumul_err^2 / seq_along(node_id),
         cumul_uncert = cumsum(sigma_est^2) / cumsum(nodelen)^2) %>% 
  ungroup()
ggplot(plotdf1, aes(x = node_id, y = cumul_err)) +
  geom_line() + 
  geom_line(aes(y = sqrt(cumul_uncert)), color = "red") +
  geom_line(aes(y = -sqrt(cumul_uncert)), color = "red") +
  facet_wrap(~reach_id, scales = "free_x")

ggplot(plotdf1, aes(x = node_id, y = cumul_err^2)) +
  geom_line() + 
  geom_line(aes(y = cumul_uncert), color = "red") +
  facet_wrap(~reach_id, scales = "free_x") +
  scale_y_log10()
```


Now again as area

```{r, fig.width = 7, fig.height=8}

plotdf2 <- rodir(18) %>% 
  rt_valdata(flag_out_nodes = FALSE) %>% 
  filter(variable == "area_total") %>% 
  group_by(reach_id) %>% 
  arrange(node_id) %>% 
  transmute(node_id, 
            pixc_err,
            rel_err = pixc_err / sigma_est,
            cumul_err = cumsum(pixc_err),
            cumul_uncert = sqrt(cumsum(sigma_est^2)),
            cumul_relerr = cumul_err / cumul_uncert,
            sigma_est) %>% 
  ungroup() %>% 
  gather(key = "variable", value = "value", -reach_id, -node_id, -cumul_uncert, -sigma_est) %>% 
  mutate(uncert = case_when(variable == "pixc_err" ~ sigma_est,
                            variable == "rel_err" | variable == "cumul_relerr" ~ 1,
                            variable == "cumul_err" ~ cumul_uncert))


nodebreaks <- unique(plotdf2$node_id) %>% `[`(.%%20 == 0)

ggplot(plotdf2, aes(x = node_id, y = value)) +
  geom_line() + 
  geom_line(aes(y = uncert), color = "red") +
  geom_line(aes(y = -uncert), color = "red") +
  geom_line(aes(y = 1.96 * uncert), color = "red", linetype = 2) +
  geom_line(aes(y = -1.96 * uncert), color = "red", linetype = 2) +
  # facet_wrap(~reach_id, scales = "free_x") +
  facet_grid(variable~reach_id, scales = "free", space = "free_x") +
  scale_x_continuous(breaks = nodebreaks, expand = expand_scale(0, 0)) +
  theme(panel.spacing = unit(2, "points"))


```

```{r}
rodir(18) %>% 
  rt_valdata("reaches") %>% 
  rt_val_scatter(yvar = "relerr", variables = c("area_total", "width"))
```

Think through next steps. I would ideally like show side-by-side: 

- map with pixels for a given node
- node area aggregation plot
    - ideally with crosstalk to leaflet map
- reachwise node scatterplots
- reach scatterplots

So what does this require? 

- Put reachwise node series into a function
- Modify shiny app to include only these bits


Here's a function for the noeseries plot. 

```{r}
rodir(18) %>% 
  rt_valdata() %>% 
  rt_nodewise_error()
```

Cool. Put that into a lib/ script. Good. Next I can start on a shiny dashboard. 

