---
title: "notebook20190729"
author: "Mark Hagemann"
date: "7/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Last time I tried to recreate (and found a strange discrepancy) the pixel cloud reported water fraction uncertainty, using an intermediate product. Toay I reported this discrepancy to Brent, and now I shall plunge forward with getting the "true" land and water powers. 

Referring to Brent's pdf from last week, I need to get:

- $\phi_ref$ from "phase" variable in intermediate_conditioned_refloc_new_0.nc file.
- $\gamma_t$ and $\phi_t$ from functions of "no noise ifgram imag", "no noise ifgram real",
"power right", "power left", variables in inf_truth.LeftSwath.nc file. This one is really big, so do some kind of subsetting on the hydro server. 
- other values from pixel_cloud.nc

```{r}
list.files(rodir(65))
```

## Some needed variables from Friday's notebook

```{r}
# function to get variable from intermediate (2-D) to pixel-cloud (1-D) form
intermed2pixc <- function(nc_inter, varid, pixcdf, outname = varid) {
  ranges <- pixcdf$range_index
  azims <- pixcdf$azimuth_index
  
  varray <- ncvar_get(nc_inter, varid = varid, collapse_degen = FALSE)
  
  # Check if nc_inter is already subset along range ("num_pixels__") 
  # and/or azimuth ("num_lines__"). If so, revalue the dimnames 
  # of the returned array before melting. 
  
  rowids <- if (is.null(nc_inter$var[["num_pixels__"]]))
    1:nrow(varray) else
      as.vector(ncvar_get(nc_inter, "num_pixels__"))
  colids <- if (is.null(nc_inter$var[["num_lines__"]]))
    1:ncol(varray) else
      as.vector(ncvar_get(nc_inter, "num_lines__"))
  
  rownames(varray) <- rowids - 1 # Adjust to match python-based indexing in pixc
  colnames(varray) <- colids - 1
  
  outdf <- setNames(reshape2::melt(varray), 
                    c("range_index", "azimuth_index", outname)) %>% 
    mutate(range_index = as.numeric(range_index), 
           azimuth_index = as.numeric(azimuth_index)) %>% 
    left_join(x = pixcdf, y = ., by = c("range_index", "azimuth_index"))
  outdf
}

pixcdf <- pixc_read(path(rodir(65), "pixel_cloud.nc"))
rangeinds <- unique(pixcdf$range_index) + 1 # adjust zero-referenced indices
aziminds <- unique(pixcdf$azimuth_index) + 1 


```


## Values from intermediate_conditioned_refloc_new_0.nc

```{r}
reflocnc <- nc_open(path(rodir(65), "intermediate_conditioned_refloc_new_0.nc"))
names(reflocnc$dim)
reflocnc_ss <- nc_subset(reflocnc, num_pixels %in% rangeinds, num_lines %in% aziminds)

```

Nice, this has same dimensions as the other intermediate file, so I may be able to use the same function as last time to get the variables in the form I need. 

```{r}
phasevardf <- intermed2pixc(reflocnc_ss, "phase", pixcdf, outname = "phase")
glimpse(phasevardf)


randrow <- sample_n(phasevardf, 1)
phasevardf %>% 
  filter(range_index %in% (randrow$range_index + -30:30), 
         azimuth_index %in% (randrow$azimuth_index + -30:30)) %>% 
  glimpse() %>% 
  ggplot(aes(x = range_index, y = azimuth_index, fill = phase)) + 
  geom_raster()
  
```

Neat. So I have the reference phase. Next steps are maybe going to be difficult. 

## Variables from inf_truth file

Get on hydro and:

- locate the inf_truth... file for this run
  - Make a symlink to it DONE.
- scope out its structure

I'm finding I need to do this in python, since there is no R on the hydro server. 

- use `numpy.apply_along_axis` with downsampling-averaging function. 
  - Prototype in R, then migrate to python


### downsampling-averaging function

```{r}
x <- rnorm(100)
x <- 1:100
n <- 3
offset <- 0

ds_avg <- function(x, n = 3, offset = 0) {
  stopifnot(length(x) > n)
  x <- x[(offset + 1):length(x)]
  
  out <- cumsum(x)
  out[(n + 1):length(x)] <- out[(n + 1):length(x)] - out[1:(length(x) - n)]
  out <- (out[n:length(out)] / n)[seq(1, length(out), by = n)]
  out
}
```

Eh, I'll scrap this approach and do it in pandas. 


- convert the np.array to pandas DataFrame. DONE
  - nrow is not a multiple of 7--remainder is 6. Take off 6 rows from some combo of beggining and/or end.
- make a group variable like `rep(1, nrow(df), each = 7)`


Make a python function.

```{python}
import numpy as np
import pandas as pd
def agg_df(df, n, offset = 0):
  # trim df to have rows that are a multiple of n
  # print(df)
  # print(offset)
  df = df.iloc[int(offset): ,]
  # print(df)
  trimno = df.shape[0] % n
  # print(trimno)
  if trimno > 0:
    df = df.iloc[:-trimno, ]
  aggvar = np.repeat(range(int(df.shape[0] / n)), n)
  df['agg_var'] = aggvar
  #
  # # Group by operation
  out = df.groupby('agg_var').apply(np.mean)
  return(out)

mtcardf = pd.DataFrame(r.mtcars)

testagg1 = agg_df(mtcardf, 5, offset = 3)
testagg1
# testagg1
```

That appears to work. Next, get this with offsets 0:6 (7 would wrap), and repeat for the variables: 

- no_noise_ifgram_imag
- no_noise_ifgram_real

Put these commands in a code chunk to copy/paste into terminal. 

```{python}
import netCDF4 as nc4
import numpy as np
import pandas as pd


ds1 = nc4.Dataset('./inf_truth.LeftSwath.nc')

# var1 = ds1.get_variables_by_attributes(name='no_noise_ifgram_imag')[0]
var1 = ds1.get_variables_by_attributes(name='classification')[0]
val1 = np.array(var1)
df1 = pd.DataFrame(val1)

for i in range(7):
  print(i)
  dfi_agg = agg_df(df1, 7, offset = i)
  filei = "classif" + str(i) + ".pkl"
  print(filei)
  dfi_agg.to_pickle(filei)

```

The aggregated data frame has the correct number of columns, but it has an extra 27 or so rows. Try doing a ccf to get the correct offset, both pre- and post-aggregation for a variable in both the pixel_cloud and the inf_truth aggregated data.frame. 

- Use `height`, I guess? 
- transfer a binary file (use `pickle`)


```{python}
import pickle
import pandas as pd

df1 = pd.read_pickle('../output/area-error/heightdata0.pkl') 
df1
# df1.shape
```

```{r}
library(reticulate)

foo <- py$df1

foo[foo == foo[1,1]] <- NA
min(foo, na.rm = TRUE)
```

Missing values are messing things up. How to deal with these when aggregating? 

```{r}
height_pixc <- pixcdf %>% 
  select(height, range_index, azimuth_index) %>% 
  reshape2::acast(range_index ~ azimuth_index, value.var = "height")

dim(height_pixc)
```

Also, how to make sure I'm doing the right comparison to pixc? 

Try with classification instead of height--that way I can compare to classnc variables, don't have to go to pixel cloud. 

```{r}
classclass <- ncvar_get(classnc, "classification")
pryr::object_size(classclass)

colsums <- apply(classclass, 2, sum)
which(colsums > 0)

rowsums <- apply(classclass, 1, sum)
which(rowsums > 0)

pklread <- import("pandas")$read_pickle

pklclass <- pklread("../output/area-error/classif2.pkl")
pklclass[pklclass < 0] <- 0

colsums_pkl <- apply(pklclass, 2, sum)
which(colsums_pkl > 0)

rowsums_pkl <- apply(pklclass, 1, sum)

```

Compare classnc classification to pickle classification

```{r}
sum(colsums > 0)
sum(colsums_pkl > 0)

sum(rowsums > 0)
sum(rowsums_pkl > 0)

```

