---
title: "notebook20190424"
author: "Mark Hagemann"
date: "4/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today I'm moving on to validating riverobs output. Keep in mind axes of validation. Important ones are cross-track distance and number of pixels. This will require reading in all runs' output as validation data.frames. 

- Can't do this yet, since for some reason the output folders didn't copy to my desktop. Redoing that now, but it will take some time to download 6.2 GB.
    - Compress it first. Duh.

```{r}
valdirs <- list.dirs("../output/hydro/sac")[-1]

valnames <- list.dirs("../output/hydro/sac", full.names = FALSE)[-1]

valdfs <- map(valdirs, ~rt_valdata(.)) %>% 
  setNames(valnames)

```

Add information about the runs

```{r}
runinfo <- read.csv("../src/roruns37.csv")
glimpse(runinfo)
```


```{r}
valdf_master <- bind_rows(valdfs[-1:-12], .id = "outno") %>% 
  mutate(outno = as.numeric(outno)) %>% 
  left_join(runinfo, by = "outno")

valdf_master %>% 
  group_by(pass) %>% 
  summarize(minxt = min(xtrk_dist), maxxt = max(xtrk_dist), n = n())
glimpse(valdf_master)
```

```{r}
valdf_master %>% 
  filter(variable == "height") %>% 
  mutate(relerr = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  ggplot(aes(x = xtrk_dist, color = pass)) + 
  
  # geom_point(aes(y = pixc_err)) + ggtitle("Empirical height error")
  # ggsave("../fig/err_xtrk.png")


  # geom_point(aes(y = sigma_est)) + ggtitle("Estimated height uncertainty")
  # ggsave("../fig/unc_xtrk.png")

  geom_point(aes(y = relerr)) + ggtitle("Scaled height error")
  ggsave("../fig/stderr_xtrk.png")

```

```{r}
valdf_master %>% 
  filter(variable == "height") %>% 
  mutate(relerr = pixc_err / sigma_est, 
         pass = as.factor(pass)) %>% 
  # sample_n(5000) %>% 
  ggplot(aes(x = n_good_pix, color = pass)) + 
  
  geom_point(aes(y = sigma_est)) + ggtitle("Estimated height uncertainty")
  ggsave("../fig/unc_pix.png")

  # geom_point(aes(y = pixc_err)) + ggtitle("Empirical height error")
  # ggsave("../fig/err_pix.png")

  # geom_point(aes(y = relerr)) + ggtitle("Scaled height error")
  # ggsave("../fig/stderr_pix.png")

```


```{r}
valdf_master %>% 
  filter(variable %in% c("latitude", "longitude"),
         pass == 264) %>% 
  select(reach_id, node_id, variable, gdem_val) %>% # glimpse()
  unique() %>% 
  spread(key = variable, value = gdem_val) %>%
  leaflet() %>% 
  addTiles() %>% 
  addCircles(stroke = FALSE, fillOpacity = 0.8, radius = 50)
```


Alright, this is good--I am getting my first real plots of errors as a function of cross-track distance. What's missing is control for other factors. 

- uncertainty estimate: I can control for this using standardized error. 
- flow condition. This is info I can get and put into a model. How to express it? Log deviations from geometric mean?
- spatial extent. Filter to only include nodes that are in common across all runs? No, just roll with it. It's the same river. 
- run characteristics (sigma0, prior db, ref dem resolution)
- Truth flagging. 

Proposal: Do a set of preliminary analysis with only outline/bullet-point text and all evental figures and tables. 

The scope of this is already rather large, especially if/when I add in different cases. But I should leave those as a separate section. Or I could just not include other cases. The main advantages of having more cases are:

- increase range of x-track
- increase range of npixels
- Address multichannel? 


### Maps of passes, nodes colored by number of runs observing

```{r}
pixcnc <- path(rodir(18), "pixel_cloud.nc")
pass_mapdf <- function(pixcnc, outlen = 100) {
  dfin <- pixc_read(pixcnc, group = "tvp")
  nrin <- nrow(dfin)
  sampint <- floor(nrin / outlen)
  sampinds <- seq(1, nrin, by = sampint)
  out <- dfin[c("time", "latitude", "longitude")][sampinds, ]
  out
}

passmapdf <- paste0(valdirs, "/pixel_cloud.nc") %>% 
  map(pass_mapdf) %>% 
  setNames(valnames) %>% 
  bind_rows(.id = "run") %>% 
  mutate(outno = as.numeric(run)) %>% 
  left_join(runinfo, by = "outno")
```

Nodes map colored by number of runs observing. For this I will need the prior db. But I can get the other info pretty easily

```{r}
# ncloc <- path("D:/data/SWOT-prior/PriorDistributionFolder/netcdfV4/", "NA07.nc")
ncloc <- "~/Documents/swot-error/data/priordb-update/Sac_sample_db14.nc"
priornc <- nc_open(ncloc)
ncnodeids <- ncvar_get(priornc, "nodes/node_id") %>% as.vector()
nc_close(priornc)
length(ncnodeids)

nodecov <- valdf_master %>% 
  filter(variable == "latitude") %>% 
  group_by(node_id) %>% 
  summarize(n = n())
  
ncinds <- which(ncnodeids %in% nodecov$node_id)

priornode_read <- function(nodeids, ncfile) {
  nc <- nc_open(ncfile)
  on.exit(nc_close(nc))
  
  getvar <- function(var, ...) as.vector(ncvar_get(nc, var, ...))
  ncnodeids <- getvar("nodes/node_id")
  ncinds <- which(ncnodeids %in% nodeids)
  outinds <- ncinds - min(ncinds) + 1
  
  readstart <- min(ncinds)
  readlen <- max(ncinds) - min(ncinds) + 1
  
  out <- data.frame(
    node_id = nodeids,
    latitude = getvar("nodes/y", start = readstart, count = readlen)[outinds],
    longitude = getvar("nodes/x", start = readstart, count = readlen)[outinds])
  out
}

nodemapdf <- priornode_read(nodecov$node_id, ncloc) %>% 
  left_join(nodecov, by = "node_id")
```


```{r}
passmapdf %>% 
  ggplot(aes(x = longitude, y = latitude)) + 
  geom_line(aes(group = as.factor(pass))) + 
  geom_point(aes(color = n), data = nodemapdf)
```

Put a background map on it. 

```{r, fig.width = 8}
# library(ggmap)
# allat <- c(passmapdf$latitude, nodemapdf$latitude)
# allon <- c(passmapdf$longitude, nodemapdf$longitude)
# bbox <- c(min(allon), min(allat), max(allon), max(allat))

# bgmap <- get_map(location = bbox, maptype = "terrain")
# osmap <- get_map(location = bbox, source = "osm")


# ggmap(bgmap)

ggm3 <- ggmap(bgmap, darken = c(0.2, "white")) +
    # ggplot(aes()) + 
  geom_line(aes(x = longitude, y = latitude,
                group = as.factor(pass),
                linetype = pass),
            data = mutate(passmapdf, pass = as.factor(pass)),
            size = 1) + 
  geom_point(aes(x = longitude, y = latitude, color = n), 
             data = nodemapdf) +
  scale_color_viridis_c()
ggm3

ggsave(ggm3, filename = "../fig/3pass_map.jpg", dpi = 300)

```

### Histograms of npix, xtrack

```{r}
# glimpse(valdf_master)

ggnpxhist <- valdf_master %>% 
  filter(variable == "latitude") %>% 
  mutate(pass = as.factor(pass)) %>% 
  ggplot(aes(x = n_good_pix, fill = pass)) +
  geom_histogram()

ggsave(ggnpxhist, filename = "../fig/npix_hist.png", width = 6, height = 4)

```

```{r}
ggxtkhist <- valdf_master %>% 
  filter(variable == "latitude") %>% 
  mutate(pass = as.factor(pass)) %>% 
  ggplot(aes(x = xtrk_dist, fill = pass)) +
  geom_histogram()

ggsave(ggxtkhist, filename = "../fig/xtrk_hist.png", width = 6, height = 4)

```


Now flow condition

```{r}
library(lubridate)
flowdf <- read.csv("../data/sac_flow.csv", stringsAsFactors = FALSE) %>% 
  transmute(date = lubridate::ymd_hm(DATE.TIME, tz = "America/Los_Angeles"),
            date = as.Date(date),
            flow = as.numeric(VALUE),
            logdev = log(flow) - mean(log(flow), na.rm = TRUE))
cdffun <- ecdf(na.omit(flowdf$flow))
flowdf$qtl <- cdffun(flowdf$flow)

rundates <- ymd(sprintf("2009%04d", runinfo$day))
rundatedf <- data.frame(date = rundates, day = as.factor(runinfo$day))

glimpse(flowdf)

cdfdf <- data.frame(
  flow = exp(seq(log(1000), log(max(flowdf$flow, na.rm = TRUE)), 
                 length.out = 200))
) %>% 
  mutate(cdf = cdffun(flow))

flowdf$cdf <- cdffun(flowdf$flow)

flowdf_plot <- flowdf %>% 
  filter(date %in% rundates) %>% 
  left_join(rundatedf, by = "date")

gg_ecdf3 <- cdfdf %>% 
  ggplot(aes(x = flow, y = cdf)) + 
  geom_line() + 
  geom_point(aes(color = day), data = flowdf_plot, size = 3) +
  scale_x_log10() +
  annotation_logticks()

ggsave(gg_ecdf3, width = 5, height = 4, dpi = 250, filename = "../fig/ecdf3.png")


```




## More work on connectivity algorithm. 

I need to put this into a function. Actually several functions, but all with the same input--a joined pixc, pcv data.frame as returned by `join_pixc()`.

```{r}
testdf <- join_pixc(rodir(18))
pcdf <- testdf %>% 
  dplyr::filter(node_index %in% 210:225)
```

First a recursive R version.
```{r}
connect1 <- function(pcdf) {
  rangeinds <- pcdf$range_index
  aziminds <- pcdf$azimuth_index
  seglabs <- pcdf$segmentation_label
  reachinds <- pcdf$reach_index
  nodeinds <- pcdf$node_index
  pixcinds <- pcdf$pixc_index
  
  # modify along_reach to continue across reach boundaries and coerce 
  # downstream-ness across node boundaries
  along_split <- split(pcdf$along_reach, reachinds)
  along_rezero <- map(along_split, function(x) x - min(x))
  shifts <- c(0, map_dbl(along_rezero, max))[1:length(along_split)] %>% 
    cumsum()
  along <- map2(along_rezero, shifts, function(x, y) x + y) %>% 
    unsplit(reachinds)

  # Find indices of up/downstream neighbors for a given index
  stream_neighbors <- function(index, nn = 2, which = c("up", "down")) {
    which <- match.arg(which)
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighbormask <- (rangeinds %in% (this_range + -nn:nn)) & 
                    (aziminds %in% (this_azimuth + -nn:nn))
    us_submask <- along[neighbormask] <= this_along
    if (which == "down") us_submask <- !us_submask
    neighbormask[neighbormask] <- us_submask
    out <- which(neighbormask)
    out
  }
  
  # Initialize connectivity vectors to prep for recursion
  connected_ds <- rep(FALSE, length(rangeinds))
  connected_us <- rep(FALSE, length(rangeinds))
  uscount <- 1
  dscount <- 1
  
  startinds_up <- which(pcdf$node_index == max(pcdf$node_index))
  startinds_dn <- which(pcdf$node_index == min(pcdf$node_index))

  options(expressions = 100000)
  
  connect_downstream <- function(ind) {
    if (connected_ds[ind]) return() #|| !segmask[ind]) return()
    connected_ds[ind] <<- TRUE
    if (dscount %% 1000 == 0)
      cat(sprintf("Connected %s of %s pixels\n", sum(connected_ds), 
            length(connected_ds)))
    dscount <<- dscount + 1
    # Recurse upstream
    nbrs <- stream_neighbors(ind, nn = 2, which = "down")
    nbrs <- nbrs[!connected_ds[nbrs]]
    for (neighbor in nbrs) {
      connect_downstream(neighbor)
    }
  }
  connect_upstream <- function(ind) {
    if (connected_us[ind]) return() #|| !segmask[ind]) return()
    connected_us[ind] <<- TRUE
    if (uscount %% 1000 == 0) 
      cat(sprintf("Connected %s of %s pixels\n", sum(connected_us), 
                  length(connected_us)))
    uscount <<- uscount + 1
    # Recurse upstream
    nbrs <- stream_neighbors(ind, nn = 2, which = "up")
    nbrs <- nbrs[!connected_us[nbrs]]
    for (neighbor in nbrs) {
      connect_upstream(neighbor)
    }
  }  
  
  # Do the recursion
  for (index in startinds_dn) {
    connect_downstream(index)
  }
  message("Downstream connection complete")
  for (index in startinds_up) {
    connect_upstream(index)
  }
  message("Upstream connection complete")
  
  out <- data.frame(up = connected_us, dn = connected_ds, 
                    connected = (connected_us & connected_ds))
  out
}

con1 <- connect1(pcdf)
# con1 <- connect1(testdf %>% filter(node_index %in% 210:250))
sum(con1$connected)
```

Now an iterative version. 

```{r}
connect2 <- function(pcdf) {
  rangeinds <- pcdf$range_index
  aziminds <- pcdf$azimuth_index
  seglabs <- pcdf$segmentation_label
  reachinds <- pcdf$reach_index
  nodeinds <- pcdf$node_index
  pixcinds <- pcdf$pixc_index
  
  # modify along_reach to continue across reach boundaries and coerce 
  # downstream-ness across node boundaries
  along_split <- split(pcdf$along_reach, reachinds)
  along_rezero <- map(along_split, function(x) x - min(x))
  shifts <- c(0, map_dbl(along_rezero, max))[1:length(along_split)] %>% 
    cumsum()
  along <- map2(along_rezero, shifts, function(x, y) x + y) %>% 
    unsplit(reachinds)

  # Find indices of up/downstream neighbors for a given index
  stream_neighbors <- function(index, nn = 2, which = c("up", "down")) {
    which <- match.arg(which)
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighbormask <- (rangeinds %in% (this_range + -nn:nn)) & 
                    (aziminds %in% (this_azimuth + -nn:nn))
    us_submask <- along[neighbormask] <= this_along
    if (which == "down") us_submask <- !us_submask
    neighbormask[neighbormask] <- us_submask
    out <- which(neighbormask)
    out
  }
  
  # Initialize connectivity vectors to prep for recursion
  connected_ds <- rep(FALSE, length(rangeinds))
  connected_us <- rep(FALSE, length(rangeinds))
  uscount <- 1
  dscount <- 1
  
  startinds_up <- which(pcdf$node_index == max(pcdf$node_index))
  startinds_dn <- which(pcdf$node_index == min(pcdf$node_index))

  options(expressions = 100000)
  
  current_inds <- startinds_dn
  count1 <- 1
  while (length(current_inds)) {
    nbrs <- current_inds %>% 
      map(stream_neighbors, nn = 2, which = "down") %>% 
      unlist() %>% 
      unique() %>% 
      setdiff(y = current_inds)
    connected_ds[nbrs] <- TRUE
    current_inds <- nbrs
    count1 <- count1 + 1
    if ((count1 %% 100) == 0) return()
  }

  message("Downstream connection complete")

  current_inds <- startinds_up
  
  count1 <- 1
  while (length(current_inds)) {
    nbrs <- current_inds %>% 
      lapply(stream_neighbors, nn = 2, which = "up") %>% 
      unlist() %>% 
      unique() %>% 
      setdiff(y = current_inds)
    connected_us[nbrs] <- TRUE
    current_inds <- nbrs
    count1 <- count1 + 1
    if ((count1 %% 1000) == 0) cat(count1, "\n")
  }
  message("Upstream connection complete")
  
  out <- data.frame(up = connected_us, dn = connected_ds, 
                    connected = (connected_us & connected_ds))
  out
}


con2 <- connect2(pcdf)
```

```{r}
library(profvis)
profvis(connect2(pcdf))
```

Can I vectorize stream_neighbors?

```{r}
  stream_neighbors <- function(index, nn = 2, which = c("up", "down")) {
    which <- match.arg(which)
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighbormask <- (rangeinds %in% (this_range + -nn:nn)) & 
                    (aziminds %in% (this_azimuth + -nn:nn))
    us_submask <- along[neighbormask] <= this_along
    if (which == "down") us_submask <- !us_submask
    neighbormask[neighbormask] <- us_submask
    out <- which(neighbormask)
    out
  }

  # Find indices of up/downstream neighbors for a given indices
  stream_neighbors_vec <- function(indices, nn = 2, which = c("up", "down")) {
    which <- match.arg(which)
    this_range <- rangeinds[indices]
    this_azimuth <- aziminds[indices]
    
    for (index in indices) {
      
    }
    this_along <- along[indices]
    neighbormask <- (rangeinds %in% (this_range + -nn:nn)) & 
                    (aziminds %in% (this_azimuth + -nn:nn))
    us_submask <- along[neighbormask] <= this_along
    if (which == "down") us_submask <- !us_submask
    neighbormask[neighbormask] <- us_submask
    out <- which(neighbormask)
    out
  }


```


I have another idea.

```{r}
connect3 <- function(pcdf) {
  rangeinds <- pcdf$range_index
  aziminds <- pcdf$azimuth_index
  seglabs <- pcdf$segmentation_label
  reachinds <- pcdf$reach_index
  nodeinds <- pcdf$node_index
  pixcinds <- pcdf$pixc_index
  
  # modify along_reach to continue across reach boundaries and coerce 
  # downstream-ness across node boundaries
  along_split <- split(pcdf$along_reach, reachinds)
  along_rezero <- map(along_split, function(x) x - min(x))
  shifts <- c(0, map_dbl(along_rezero, max))[1:length(along_split)] %>% 
    cumsum()
  along <- map2(along_rezero, shifts, function(x, y) x + y) %>% 
    unsplit(reachinds)

  # Find indices of up/downstream neighbors for a given index
  stream_neighbors <- function(index, nn = 2, which = c("up", "down")) {
    which <- match.arg(which)
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighbormask <- (rangeinds %in% (this_range + -nn:nn)) & 
                    (aziminds %in% (this_azimuth + -nn:nn))
    us_submask <- along[neighbormask] <= this_along
    if (which == "down") us_submask <- !us_submask
    neighbormask[neighbormask] <- us_submask
    out <- which(neighbormask)
    out
  }
  
  # Initialize connectivity vectors to prep for recursion
  connected_ds <- rep(FALSE, length(rangeinds))
  connected_us <- rep(FALSE, length(rangeinds))
  uscount <- 1
  dscount <- 1
  
  startinds_up <- which(pcdf$node_index == max(pcdf$node_index))
  startinds_dn <- which(pcdf$node_index == min(pcdf$node_index))

  connect_downstream <- function(inds) {

    # Start collection of neighbors. Track start index, end index
    nbrs <- inds
    nbr_start <- 2
    nbr_end <- 2
    
    connected_ds[inds[2:(inds[1] + 1)]] <<- TRUE
    # connected_ds[inds[2:(inds[1] + 1)]] <- TRUE # for debugging
    
    for (indind in 1:inds[1]) {
      ind <- inds[indind + 1] # account for first index being length

      newnbrs <- setdiff(stream_neighbors(ind, nn = 2, which = "down"),
                         c(nbrs[nbr_start:nbr_end], which(connected_ds)))
      if (!length(newnbrs)) next
      new_nbr_end <- nbr_end + length(newnbrs)
      nbrs[nbr_end:new_nbr_end] <- newnbrs
      nbr_end <- new_nbr_end + 1
      indind <- indind + 1 # for debugging
    }
    nbrs[1] <- nbr_end - 1
    nbrs
  }
  connect_upstream <- function(ind) {
    if (connected_us[ind]) return() #|| !segmask[ind]) return()
    connected_us[ind] <<- TRUE
    if (uscount %% 1000 == 0) 
      cat(sprintf("Connected %s of %s pixels\n", sum(connected_us), 
                  length(connected_us)))
    uscount <<- uscount + 1
    # Recurse upstream
    nbrs <- stream_neighbors(ind, nn = 2, which = "up")
    nbrs <- nbrs[!connected_us[nbrs]]
    nbrs
  }  
  
  # Do the recursion
  inds_dn <- c(length(startinds_dn), startinds_dn)
  # while(ninds_dn > 0) {
  for (i in 1:3) {
    ninds_dn <- inds_dn[1] # hack to make the first index the number of current inds
    print(inds_dn[2:(ninds_dn + 1)])
    # cat("\n")
    inds_dn <- connect_downstream(inds_dn)
  }
  return(connected_ds)
  
  for (index in startinds_dn) {
    connect_downstream(index)
  }
  message("Downstream connection complete")
  for (index in startinds_up) {
    connect_upstream(index)
  }
  message("Upstream connection complete")
  
  out <- data.frame(up = connected_us, dn = connected_ds, 
                    connected = (connected_us & connected_ds))
  out
}

con3 <- connect3(pcdf)
```

need to vectorize connect_downstream, etc. 

Stripping down and making modular

```{r}
connect4 <- function(pcdf) {
  rangeinds <- as.numeric(pcdf$range_index)
  aziminds <- as.numeric(pcdf$azimuth_index)
  # seglabs <- pcdf$segmentation_label
  reachinds <- as.numeric(pcdf$reach_index)
  nodeinds <- as.numeric(pcdf$node_index)
  pixcinds <- as.numeric(pcdf$pixc_index)
  
  # modify along_reach to continue across reach boundaries and coerce 
  # downstream-ness across node boundaries
  along_split <- split(pcdf$along_reach, nodeinds)
  along_rezero <- map(along_split, function(x) x - min(x))
  shifts <- c(0, map_dbl(along_rezero, max))[1:length(along_split)] %>% 
    cumsum()
  along <- map2(along_rezero, shifts, function(x, y) x + y) %>% 
    unsplit(nodeinds)
  

  # Lookup table for range-azimuth combos
  ra_table <- rangeinds * 1e5 + aziminds
  match_range_azim <- function(r_inds, a_inds) {
    # tomatch <- outer(r_inds * 1e5, a_inds, "+")
    tomatch <- rep(r_inds * 1e5, length(a_inds)) + 
               rep(a_inds, each = length(r_inds))
    
    out <- fmatch(tomatch, ra_table)
    out[!is.na(out)]
  }
  
  # Find indices of up/downstream neighbors for a given index
  dnstream_neighbors <- function(index, nn = 2) {
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighborinds <- match_range_azim(this_range + -nn:nn, 
                                     this_azimuth + -nn:nn)
    ds_inds <- neighborinds[along[neighborinds] >= this_along]
    ds_inds
  }
  
  upstream_neighbors <- function(index, nn = 2L) {
    this_range <- rangeinds[index]
    this_azimuth <- aziminds[index]
    this_along <- along[index]
    neighborinds <- match_range_azim(this_range + -nn:nn, 
                                     this_azimuth + -nn:nn)
    us_inds <- neighborinds[along[neighborinds] <= this_along]
    us_inds
  }
  
  # Initialize connectivity vectors to prep for recursion
  connected_ds <- rep(FALSE, length(rangeinds))
  connected_us <- rep(FALSE, length(rangeinds))
  uscount <- 1
  dscount <- 1
  
  startinds_up <- which(pcdf$node_index == max(pcdf$node_index))
  startinds_dn <- which(pcdf$node_index == min(pcdf$node_index))

  advance_front_ds <- function(front) {
    new_front <- numeric(length(front) * 10L)
    starti <- 1
    for (index in front) {
      new_nbrs <- dnstream_neighbors(index, nn = 2L)
      if (!(n_new_nbrs <- length(new_nbrs))) next
      endi <- starti + n_new_nbrs - 1
      new_front[starti:endi] <- new_nbrs
      starti <- endi + 1
    }
    # setdiff(new_front[1:endi], front)
    setdiff(new_front[1:endi], which(connected_ds))
  }
  
  advance_front_us <- function(front) {
    new_front <- numeric(length(front) * 10L)
    starti <- 1
    for (index in front) {
      new_nbrs <- upstream_neighbors(index, nn = 2L)
      if (!(n_new_nbrs <- length(new_nbrs))) next
      endi <- starti + n_new_nbrs - 1
      new_front[starti:endi] <- new_nbrs
      starti <- endi + 1
    }
    setdiff(new_front[1:endi], which(connected_us))
  }
  
  # Do the iteration
  front_ds <- startinds_dn
  frontno_ds <- integer(length(connected_ds)) # Track which front each pixel belongs to
  frontno_ds[front_ds] <- 1L # Track which front each pixel belongs to
  connected_ds[startinds_dn] <- TRUE
  count_ds <- 1L
  while(length(front_ds)) {
  # for (i in 1:600) {
    front_ds <- advance_front_ds(front_ds)
    connected_ds[front_ds] <- TRUE
    
    count_ds <- count_ds + 1L
    frontno_ds[front_ds] <- count_ds

    if (count_ds %% 100 == 0) {
      cat(sum(connected_ds), length(front_ds), "\n")
    }
  }

  message("Downstream connection complete")

  front_us <- startinds_up
  frontno_us <- integer(length(connected_us)) # Track which front each pixel belongs to
  frontno_us[front_us] <- 1L # Track which front each pixel belongs to
  connected_us[startinds_up] <- TRUE
  count_us <- 1
  while(length(front_us)) {
  # for (i in 1:100) {
    front_us <- advance_front_us(front_us)
    connected_us[front_us] <- TRUE
    count_us <- count_us + 1
    frontno_us[front_us] <- count_us
    if (count_us %% 100 == 0) {
        cat(sum(connected_us), length(front_us), "\n")
    }
  }
  message("Upstream connection complete")
  
  out <- data.frame(up = connected_us, dn = connected_ds, 
                    connected = (connected_us & connected_ds),
                    along = along,
                    frontno_us = frontno_us,
                    frontno_ds = frontno_ds)
  out
}

con4 <- connect4(testdf)
# profvis(connect4(testdf))
```

Now map it, showing that it works.

```{r}
library(leaflet)


mapdf <- testdf %>% 
  cbind(con4) %>% 
  mutate(con_no = as.factor(up * 2 + dn), radius = sqrt(pixel_area / pi)) %>% 
  select(latitude, longitude, con_no, node_index, reach_index, pixc_index, 
         radius, along, frontno_ds, frontno_us) %>% 
  filter(reach_index == 5) %>% 
  # sample_n(10000) %>% 
  glimpse()


conpal <- colorFactor(palette = c("black", "green", "cyan", "purple"), 
                      domain = mapdf$con_no)

leaflet(mapdf) %>% 
  addTiles() %>% 
  addCircles(stroke = FALSE, fillOpacity = 0.8, fillColor = ~conpal(con_no), 
             popup = ~paste(node_index, reach_index),
             # popup = ~paste(node_index, reach_index),
             radius = ~radius) 

```



Animate a map

```{r}
library(gganimate)

gg4 <- ggplot(select(mapdf, -frontno_ds), aes(y = longitude, x = latitude)) +
  geom_point(size = 0.2) +
  geom_point(size = 0.1, aes(group = frontno_ds),
             color = "green",
             alpha = 1,
             # alpha = 0.1,
             data = filter(mapdf, frontno_ds > 1)) +
  # coord_map()
  coord_equal()
  # coord_flip()
gg4

gganim4 <- gg4 + transition_time(frontno_ds) +
  shadow_mark(alpha = 0.1)


```

Now the opposite direction.

```{r}
gg5 <- ggplot(select(mapdf, -frontno_us), aes(y = longitude, x = latitude)) +
  geom_point(size = 0.2) +
  geom_point(size = 0.1, aes(group = frontno_us),
             color = "cyan",
             alpha = 1,
             # alpha = 0.1,
             data = filter(mapdf, frontno_us > 1)) +
  # coord_map()
  coord_equal()
  # coord_flip()
gg5

gganim5 <- gg5 + transition_time(frontno_us) +
  shadow_mark(alpha = 0.1)
```

```{r}

animate(gganim4, duration = 12, renderer = av_renderer(file = "../fig/downstream.mp4"), 
        width = 600, height = 250)

# animate(gganim5, duration = 12, renderer = av_renderer(file = "../fig/upstream.mp4"), 
#         width = 600, height = 250)

```

