---
title: "notebook20190109"
author: "Mark Hagemann"
date: "January 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Time to get R and Python to join forces. I'll try using `reticulate` for that. 

```{r}
library(reticulate)

use_condaenv("RiverObs", required = TRUE)
```

That appears to have worked. Now how do I use python commands?

```{r}
source_python("../src/imports.py")
pygdal <- import("osgeo")
```

Now that that works (after updating reticulate), see if I can flat-out run the script.

```{r}
source_python("../src/7SAC_264_l2_newfields.py")
```

It works!

Now back to the previous task: inspecting Brent's sample uncertainty file.

- Map the heights
- Map the estimated uncertainty
- Calculate empirical uncertainty

```{r}
ncfile <- "../../riverobs-data/uncertainty_example/pixel_cloud.nc"

ncobj <- nc_open(ncfile)
names(ncobj$var)

nc_close(ncobj)
```

How about a function to plot from an open pixc netcdf file?

```{r}
pixc_map <- function(ncobj, varname, subset = 500, 
                     prefix = "pixel_cloud/", plot = TRUE) {
  lats <- ncvar_get(ncobj, "pixel_cloud/latitude")
  len <- attr(lats, "dim")
  keepinds <- sort(sample(1:len, size = min(len, subset)))
  
  lats <- as.vector(lats[keepinds])
  lons <- as.vector(ncvar_get(ncobj, "pixel_cloud/longitude")[keepinds])
  vars <- as.vector(ncvar_get(ncobj, paste0(prefix, varname))[keepinds])
  
  plotdf <- setNames(data.frame(lat = lats, lon = lons, var = vars),
                     c("lat", "lon", varname))
  if (!plot) return(plotdf)
  
  pal <- colorNumeric(palette = "YlOrRd", domain = vars)
  out <- leaflet(plotdf) %>% 
    addTiles() %>% 
    addCircleMarkers(lng = ~lon, lat = ~lat, color = ~pal(plotdf[[varname]]))
  out
}
```



