---
title: "notebook20190821"
author: "Mark Hagemann"
date: "8/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Looking today at usds connected riverobs results. 

```{r}

pcvi <- rodir(65, "simple") %>% 
  join_pixc("pcv_usds.nc", "pixel_cloud_new_usds.nc")
pcvi_gdem <- rodir(65, "simple") %>% 
  join_pixc("pcv_gdem_usds.nc", pixcname = "../fake_pixc_usds.nc")

# unique(pcvi_gdem$node_index)

library(ggforce)
map_node_pixc(pcvi_gdem, 416, real_area = TRUE)
```

Don't get ahead of myself. First do the validation. 

```{r}
nodevaldf1 <- rt_valdata(rodir(65, "simple"), rtname = "rt_usds.nc", 
                        gdname = "rt_gdem_usds.nc")

nodevaldf2 <- rt_valdata(rodir(65, "simple"), rtname = "rt.nc", 
                        gdname = "rt_gdem.nc")


rt_val_scatter(nodevaldf1, "width", yvar = "relerr")
rt_val_scatter(nodevaldf2, "width", yvar = "relerr")

badnodes(nodevaldf1, "width", standardize = TRUE, which = "min")
# map_node_pixc(pcvi, 587, gdemdf = pcvi_gdem, real_area = TRUE)
map_node_pixc(pcvi, 683, gdemdf = pcvi_gdem, real_area = TRUE)
```


Time to go back to the usds algorithm and see what it's doing in this case.

```{r}
origpixdf <- rodir(65, "simple") %>% 
  join_pixc(pixcname =  "pixel_cloud_new.nc") %>% 
  left_join(us_ds(., start = "midstream"), by = c("range_index", "azimuth_index"))

origpixdf %>% 
  filter(node_index %in% (587 + -5:5)) %>% 
  ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc)) +
  geom_point(aes(color = connected)) +
  coord_map()


```

Works fine now. Go back and repeat the code verbatim. 

```{r}
dir <- rodir(65, "simple")
pixcfile <- fs::path(dir, "pixel_cloud_new.nc")
pcvfile <- fs::path(dir, "pcv.nc")
newfile <- "pixel_cloud_new_usds.nc"

# # modified from update_pixc()
# usds_pixc <- function(pixcfile, pcvfile, newfile = "pixel_cloud_usds.nc",
#                       is_gdem = FALSE) {
  stopifnot(file.exists(pixcfile))
  putdir <- normalizePath(paste0(pixcfile, "/.."))
  putfile <- file.path(putdir, newfile)
  file.copy(pixcfile, putfile, overwrite = TRUE)
  outnc <- nc_open(putfile, write = TRUE)
  # on.exit(nc_close(outnc))
  
  origpixcnc <- nc_open(pixcfile)
  # on.exit(nc_close(origpixcnc))
  origpixcdf <- pixc_read(pixcfile) %>% 
    mutate(rangeazim = range_index * 1e5 + azimuth_index)
  origpcvdf <- pixcvec_read(pcvfile)
  
  subsetdf0 <- us_ds(origpcvdf) %>% filter(connected) %>% 
    left_join(origpcvdf, by = c("range_index", "azimuth_index"))
  rangeazim_587 <- subsetdf0 %>% 
    filter(node_index == 587) %>% 
    select(range_index, azimuth_index) %>% 
    mutate(rangeazim = range_index * 1e5 + azimuth_index)
  rangeazim_587 %>% 
    ggplot(aes(x = range_index, y = azimuth_index)) + geom_point()
  
  matchra <- match(rangeazim_587$rangeazim, origpixcdf$rangeazim)
  
  
  subsetdf0 %>% 
    filter(node_index %in% (587 + -5:5)) %>% 
    ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc)) +
    geom_point(aes(color = connected)) +
    coord_map()
  
  subsetdf <- subsetdf0 %>% 
    select(range_index, azimuth_index) %>% 
    mutate(rangeazim = range_index * 1e5 + azimuth_index)
  # browser()
  
  keepdim <- match(subsetdf$rangeazim, origpixcdf$rangeazim)
  
  # Better approach: get the range and azimuth indices from us_ds(), 
  # use these directly to match from netcdf. 
  
  ncrange <- ncvar_get(outnc, "pixel_cloud/range_index")
  ncazim <- ncvar_get(outnc, "pixel_cloud/azimuth_index")
  ncrangeazim <- ncrange * 1e5 + ncazim
  
  keepdim <- match(subsetdf$rangeazim, ncrangeazim)
  
  outclass <- ncvar_get(outnc, "pixel_cloud/classification")
  
  if (is_gdem) {
    outclass[-keepdim] <- 0
  } else {
    outclass[-keepdim] <- 1
  }
  ncvar_put(outnc, "pixel_cloud/classification", outclass, 
            start = 1, count = length(outclass))      

  
  checkdf <- data.frame(range_index = as.vector(ncrange),
                        azimuth_index = as.vector(ncazim),
                        class = as.vector(outclass)) %>% 
    left_join(origpcvdf, by = c("range_index", "azimuth_index")) %>% 
    filter(node_index %in% (587 + -5:5))
  
  checkdf %>% 
    ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc, color = class)) + 
    geom_point()
# }

nc_close(outnc)
nc_close(origpixcnc)

outnc2 <- nc_open(putfile, write = FALSE)
checkdf2 <- data.frame(range_index = as.vector(ncrange),
              azimuth_index = as.vector(ncazim),
              class = as.vector(ncvar_get(outnc2, "pixel_cloud/classification"))) %>% 
  left_join(origpcvdf, by = c("range_index", "azimuth_index")) %>% 
  filter(node_index %in% (587 + -5:5))

  
  checkdf2 %>% 
    ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc, color = class)) + 
    geom_point()
nc_close(outnc2)
```

OK, I've got it sorted. Verified it works for a single case. Now redo the netcdf creation and riverobs runs. 


Meanwhile, get started on the slides I'll show tomorrow. And send them to Brent.

- regularization issues in composite aggregation
- Issues in water fraction aggregation
- questionable truth

Go through the map figs and select some cases. 

- composite, regularization issue: 
  - composite/68/map2 (node 286)
  - composite/80/map1 (node 78)
  - composite/80/map2 (node 372) -- this one has weird spatial otliers
- Other issues: 
  - composite/82/map1 (node 68)
  - composite/68/map1 (node 567) -- this one is pretty meh. 
- Water frac issues
  - frac/82/map4 (node 38)

Remake these ones to take advantage of new real_area argument.

```{r}
library(ggforce)
compnos <-   c(68,  80, 80,  82, 68)
compnodes <- c(286, 78, 372, 68, 567)

fracnos <- c(82)
fracnodes <- c(38)

i <- 1
runi <- compnos[i]
nodei <- compnodes[i]

pixdfi <- rodir(runi, "composite") %>% 
  join_pixc()
gdemdfi <- rodir(runi, "composite") %>% 
  join_pixc(pcvname = "pcv_gdem.nc", pixcname = "../fake_pixc.nc")

map_node_pixc(pixdf = pixdfi, nodes = nodei, gdemdf = gdemdfi, 
              scale = FALSE, real_area = TRUE)
```

Eh, better to just use the original figs? I think so. 
