---
title: "notebook20190708"
author: "Mark Hagemann"
date: "7/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today I'm getting to the bottom of the bad area error estimates. Possible issues are

- water fraction error
- classification error
- node assignment error
- pixel area error

Ideas for what/how to test:

- toggle area estimate method ("simple" or "composite") -- easy
- return decomposition of error budget -- hard


I'll need to set up a test environment. Pick a simulation run--pixc and gdem--and note effects on: 

- scaled area error qq plot
- individual nodes' pixel-area plot
- reach area scaled error



I choose pass 249, day 130, GDEM-dem (all nodes visible in middle-ish swath, lowest flow)

```{r}
ro_manifest() %>% 
  filter(day == 130, pass == 249) %>% 
  glimpse()
```


That's number 65. Make a directory for this set of investigations. 

```{r}
dir.create("../output/area-error")
dir_copy(rodir(65), "../output/area-error/orig")
```

Now do runs. Redo original, just to be sure. 

Here's simple validation:

```{r}
nodes_simple <- rt_read("../output/area-error/simple/rt.nc")

rt_simple <- rt_read("../output/area-error/simple/rt.nc")
val_simple <- rt_valdata("../output/area-error/simple/", flag_out_nodes = FALSE)
# add in composite validation
rt_composite <- rt_read("../output/area-error/composite/rt.nc")
val_composite <- rt_valdata("../output/area-error/composite/", flag_out_nodes = FALSE)

rt_composite_fixed <- rt_read("../output/area-error/composite_fixed/rt.nc")
val_composite_fixed <- rt_valdata("../output/area-error/composite_fixed/", 
                                  flag_out_nodes = FALSE)

```

Slight detour: need to fix attribute data.frame creation, since some attributes are vector-valued (e.g. flag_values). Possible workarounds:

- `base::I()` to make a list column
- `tidyr::tible()` to make list column by default


```{r}

foonc <- nc_open("../output/area-error/simple/rt.nc")
names(foonc$var)
foo <- ncatt_get(foonc, "nodes/ice_dyn_f")

foolen <- map_int(foo, length)
foo[foolen > 1] <- lapply(foo[foolen > 1], list)

vecfun(foo)
data.frame(foo)
nc_close(foonc)

bar <- rt_read("../output/area-error/simple/rt.nc")

```


Looks like variable names have been changed in the data product. That may really affect my analysis. What variables do I explicitly mention in my scripts, and what are they now? See `uncnames` variable in R/validate.R

- height : wse
- height_u : wse_r_u (intermediate name: wse_std)
- height2 : wse
- height2_u : wse_u
- width : same
- width_u : same
- area_detct : same
- area_det_u : same
- area_total : same
- area_tot_u : same
- latitude : same
- latitude_u : same
- longitude : same
- longitud_u : same



Back to validation.

```{r}
rt_val_nodeseries(val_simple, variable = "width")
rt_val_nodeseries(val_composite, variable = "width")

valvars <- c("wse", "area_total", "width")
valvars <- "area_total"

val_simple %>% 
  dplyr::filter(variable %in% valvars) %>% 
  group_by(variable) %>% 
  mutate(rel_err = pixc_err / sigma_est, 
         theoretical = qqnorm(rel_err, plot.it = FALSE)$x) %>% 
  ungroup() %>% 
  ggplot(aes(x = theoretical, y = rel_err)) + 
  # geom_point(aes(text = node_id, color = day)) +
  geom_point() +
  facet_wrap(~variable, scales = "free_y") +
  geom_abline(slope = 1, intercept = 0)

# ggsave("../fig/area-error-simple.png")

val_composite %>% 
  dplyr::filter(variable %in% valvars) %>%
  group_by(variable) %>% 
  mutate(rel_err = pixc_err / sigma_est, 
         theoretical = qqnorm(rel_err, plot.it = FALSE)$x) %>% 
  ungroup() %>% 
  ggplot(aes(x = theoretical, y = rel_err)) + 
  # geom_point(aes(text = node_id, color = day)) +
  geom_point() +
  facet_wrap(~variable, scales = "free_y") +
  geom_abline(slope = 1, intercept = 0)

# ggsave("../fig/area-error-composite.png")

val_composite_fixed %>% 
  dplyr::filter(variable %in% valvars) %>%
  group_by(variable) %>% 
  mutate(rel_err = pixc_err / sigma_est, 
         theoretical = qqnorm(rel_err, plot.it = FALSE)$x) %>% 
  ungroup() %>% 
  ggplot(aes(x = theoretical, y = rel_err)) + 
  # geom_point(aes(text = node_id, color = day)) +
  geom_point() +
  facet_wrap(~variable, scales = "free_y") +
  geom_abline(slope = 1, intercept = 0)

val_composite_fixed %>% 
  rt_val_hist(scale = TRUE, curve = TRUE, vars = "area_total")
val_composite %>% 
  rt_val_hist(scale = TRUE, curve = TRUE, vars = "area_total")
```

Map the worst offenders.

```{r}
simple_pix <- join_pixc("../output/area-error/simple/", 
                        pixcname = "../pixel_cloud.nc")
simple_pix_gdem <- join_pixc("../output/area-error/simple",
                             pixcname = "../fake_pixc.nc", pcvname = "pcv_gdem.nc")

library(leaflet)

badnodes_simple <- badnodes(val_simple, n = 6)

pixdf1 <- simple_pix %>% 
  filter(node_index %in% badnodes_simple) %>% 
  transmute(azimuth_index, range_index, node_index, reach_index,
            lat_med = latitude, lon_med = longitude,
            lat_wd = latitude_vectorproc, lon_wd = longitude_vectorproc,
            water_frac, water_frac_uncert,
            classification, fdr = false_detection_rate, 
            mdr = missed_detection_rate, Pw = prior_water_prob,
            pixel_area)
pixdf2 <- simple_pix_gdem %>% 
  filter(node_index %in% badnodes_simple) %>% 
  transmute(azimuth_index, range_index, node_index, reach_index,
            lat_gdem = latitude, lon_gdem = longitude, pixel_area)

classpal <- colorFactor("Dark2", pixdf1$classification)

leaflet_unscaled <- leaflet() %>% 
  addTiles() %>% 
  addCircles(~lon_gdem, ~lat_gdem, 
             radius = ~sqrt(pixel_area / pi),
             fillColor = "red", fillOpacity = 0.8, stroke = FALSE, 
             data = pixdf2) %>% 
  addCircles(~lon_wd, ~lat_wd, radius = ~sqrt(pixel_area / pi),
             fillColor = ~classpal(classification), stroke = FALSE, 
             fillOpacity = 0.8, data = pixdf1)
htmlwidgets::saveWidget(leaflet_unscaled, "../fig/leaflet_unscaled.html")

leaflet_scaled <- leaflet() %>% 
  addTiles() %>% 
  addCircles(~lon_gdem, ~lat_gdem, 
             radius = ~sqrt(pixel_area / pi),
             fillColor = "red", fillOpacity = 0.8, stroke = FALSE, 
             data = pixdf2) %>% 
  addCircles(~lon_wd, ~lat_wd, radius = ~sqrt(pixel_area / pi * water_frac),
             fillColor = ~classpal(classification), stroke = FALSE, 
             fillOpacity = 0.8, data = pixdf1)
htmlwidgets::saveWidget(leaflet_scaled, "../fig/leaflet_scaled.html")


```

That is really illuminating! So why does the gdem show multichannel behavior but the pixel cloud doesn't? That will have to be a question for another day. 


What about straight-up comparison of raw errors between simple and composite?

```{r}
val_full <- list(composite = val_composite, simple = val_simple) %>% 
  bind_rows(.id = "area_agg")

val_full %>% 
  filter(variable %in% valvars) %>% 
  select(node_id, reach_id, variable, pixc_err, area_agg) %>%
  # glimpse()
  spread(key = area_agg, value = pixc_err) %>% 
  # glimpse()
  ggplot(aes(x = simple, y = composite)) +
  geom_point() +
  facet_wrap(~variable, scales = "free") + 
  geom_abline(aes(slope = 1, intercept = 0))
ggsave("../fig/area-error-compare.png")
```


