---
title: "notebook20190430"
author: "Mark Hagemann"
date: "4/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today: build on work from 0424 notebook prepping for validation writeup, manuscript. 

Need to come up with a list of runs for Rui to do. 

- Is it sufficient to run gdem at 10m resolution?


### gdem resoution investigation

Remember from yesterday: the bad runs are 57 and 58. 

```{r}
ro_manifest() %>% 
  filter(priordb == "$PRIORLOC4") %>% 
  filter(refdem_res == "5m") %>% 
  glimpse()
```


```{r}
romatch(60, vary = "refdem_res")
romatch(55, vary = "refdem_res")
```

```{r}
resvaldf1 <- c(60, romatch(60, vary = "refdem_res")) %>% 
  rt_valdata_multi() %>% 
  transmute(node_id, refdem_res, variable, pixc_err, relerr = pixc_err / sigma_est) %>% 
  group_by(node_id, variable) %>% 
  mutate(meanrelerr = mean(relerr),
         minabsrelerr = min(abs(relerr)),
         relerr_contrast = relerr - meanrelerr,
         relerr_adjust = abs(relerr) - minabsrelerr,
         err_adjust = abs(pixc_err) - min(abs(pixc_err))) %>% 
  ungroup()



resvaldf1 %>%
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  ggplot(aes(x = refdem_res, y = relerr_contrast)) + 
  geom_boxplot() +
  facet_wrap(~variable, scales = "free_y")


resvaldf1 %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  # filter(variable == "height") %>% 
  ggplot(aes(sample = relerr)) + 
  geom_qq() + 
  # geom_qq_line() + 
  facet_grid(variable ~ refdem_res, scales = "free_y")
  # geom_histogram()

resvaldf1 %>% 
  filter(variable == "height") %>% 
  ggplot(aes(x = refdem_res, y = relerr_adjust)) +
  geom_line(aes(group = node_id), alpha = 0.5, size = 0.3) +
  geom_violin(alpha = 0.5) +
  # geom_line(aes(group = node_id), alpha = 0.5, size = 0.3)
  geom_point(alpha = 0.5)

resvaldf1 %>% 
  filter(variable == "height") %>% 
  ggplot(aes(x = refdem_res, y = relerr)) +
  geom_line(aes(group = node_id), alpha = 0.5, size = 0.3) +
  geom_boxplot(alpha = 0.5) +
  # geom_line(aes(group = node_id), alpha = 0.5, size = 0.3)
  geom_point(alpha = 0.5)
```

Here's the one to show:

```{r}
resvaldf1 %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  # filter(variable == "height") %>% 
  ggplot(aes(sample = relerr)) + 
  geom_qq() + 
  # geom_qq_line() + 
  facet_grid(variable ~ refdem_res, scales = "free_y")
```

This one's harder to explain, but I like it: 


```{r}
resvaldf1 %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  ggplot(aes(x = refdem_res, y = err_adjust)) +
  geom_line(aes(group = node_id), alpha = 0.5, size = 0.3) +
  geom_violin(alpha = 0.5) +
  # geom_line(aes(group = node_id), alpha = 0.5, size = 0.3)
  geom_point(alpha = 0.5) +
  facet_wrap(~variable, scales = "free_y") + 
  scale_y_sqrt()

```

Safe to say that refdem resolution doesn't matter much. Absolute difference is very small in all but a few cases. Repeat now for higher flow case. 


```{r}
resvaldf2 <- c(55, romatch(55, vary = "refdem_res")) %>% 
  rt_valdata_multi() %>% 
  transmute(node_id, refdem_res, variable, pixc_err, relerr = pixc_err / sigma_est) %>% 
  group_by(node_id, variable) %>% 
  mutate(meanrelerr = mean(relerr),
         minabsrelerr = min(abs(relerr)),
         relerr_contrast = relerr - meanrelerr,
         relerr_adjust = abs(relerr) - minabsrelerr,
         err_adjust = abs(pixc_err) - min(abs(pixc_err))) %>% 
  ungroup()

resvaldf2 %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  # filter(variable == "height") %>% 
  ggplot(aes(sample = relerr)) + 
  geom_qq() + 
  # geom_qq_line() + 
  facet_grid(variable ~ refdem_res, scales = "free_y")
  # geom_histogram()

resvaldf2%>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  ggplot(aes(x = refdem_res, y = err_adjust)) +
  geom_line(aes(group = node_id), alpha = 0.5, size = 0.3) +
  geom_violin(alpha = 0.5) +
  # geom_line(aes(group = node_id), alpha = 0.5, size = 0.3)
  geom_point(alpha = 0.5) +
  facet_wrap(~variable, scales = "free_y") + 
  scale_y_sqrt()


```

Same gist. 


So to conclude: 10-m reference dem is fine. Finalized slc simulator runs should use that. 

Resume assembling plots and tables for manuscript. 


### Manuscript prep work

Now I can use romatch to get the runs I will use for validation.

- I should be able to quickly scope which runs are missing in order to get the full validation grid. 

```{r}
glimpse(ro_manifest())


varyvars <- c("pass", "day", "gdem_name")
romatch(54, vary = varyvars)

ro_manifest() %>% 
  filter(outno %in% 51:54)
```

```{r}

valdf_master <- rt_valdata_multi(51:54)
```


```{r}
xtgg0 <- valdf_master %>% 
  # filter(variable == "height") %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  mutate(relerr = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  ggplot(aes(x = xtrk_dist, color = pass)) +
  facet_wrap(~variable, scales = "free_y")
  
xtgg0 + geom_point(aes(y = pixc_err)) + ggtitle("Empirical height error")

xtgg0 + geom_point(aes(y = sigma_est)) + ggtitle("Estimated height uncertainty")

xtgg0 + geom_point(aes(y = relerr)) + ggtitle("Scaled height error")
```


```{r}
npixgg0 <- valdf_master %>% 
  # filter(variable == "height") %>% 
  filter(variable %in% c("height", "height2", "width", "area_total")) %>% 
  mutate(relerr = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  ggplot(aes(x = n_good_pix, color = pass)) +
  facet_wrap(~variable, scales = "free_y")
  
npixgg0 + geom_point(aes(y = pixc_err)) + ggtitle("Empirical height error")

npixgg0 + geom_point(aes(y = sigma_est)) + ggtitle("Estimated height uncertainty")

npixgg0 + geom_point(aes(y = relerr)) + ggtitle("Scaled height error")
```


