---
title: "notebook20190725"
author: "Mark Hagemann"
date: "7/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


A couple of tasks following Brent's phone call yesterday. 

- get *estimated* mu values from **intermediate_class_maps_0.nc** files. 
  - shoehorn these into uncertainty value updates, re-validate.
- get *true* mu values from **intermediate conditioned refloc new 0.nc** files, math in pdf

## Work with estimated mu values

Pick a simulation run to work with. Continue with number 65, as used in area-error/ 

```{r}
ro_manifest() %>% 
  filter(outno == 65) %>% 
  pull(indir)
  glimpse()
```

Put that (intermeidate class maps therein) into `rodir(65)` location.

```{r}
rodir(65) %>% path()
```

```
scp -v $HYDROslc-sac/output_sac_pixc_dir_0249_single_true-ref_10m/GDEM_DEM_ellip_130_0249/cycle_0001_pass_0249_001L_nlcd-100dB_water10dB_50m_CBE/intermediate_class_maps_0.nc \
 D:/data/riverobs-output/sacruns_latest/output/sac/65/

scp -v $HYDRO:slc-sac/output_sim_sac_0249_single_land-100dB/GDEM_DEM_ellip_130_0249/cycle_0001_pass_0249_001L_nlcd-100dB_water10dB_50m_CBE/intf_truth.LeftSwath.nc D:/data/riverobs-output/sacruns_latest/output/sac/65/
 
scp -v $HYDRO:slc-sac/output_sac_pixc_dir_0249_single_true-ref_10m/GDEM_DEM_ellip_130_0249/cycle_0001_pass_0249_001L_nlcd-100dB_water10dB_50m_CBE/intermediate_conditioned_refloc_new_0.nc D:/data/riverobs-output/sacruns_latest/output/sac/65/
```

Second one is 13 GB! Maybe wait on that one...


### mu values from class maps ncdf

```{r}
classncfile <- path(rodir(65), "intermediate_class_maps_0.nc")
classnc <- nc_open(classncfile)
pixcnc <- nc_open(path(rodir(65), "pixel_cloud.nc"))


names(classnc$dim)
classnc$dim$num_pixels$len
classnc$dim$num_lines$len
names(pixcnc$dim)
pixcnc$dim$`pixel_cloud/points`$len
pixcnc$dim$`noise/num_lines`$len


names(classnc$var) 



classnc$var$
classnc$var$water_power$ndims
nc_close(classnc)
nc_close(pixcnc)
```

Get the land_power, water_power.

```{r}
muwvec <- ncvar_get(classnc, "water_power")
mudimnames <- sapply(classnc$var$water_power$dim, function(x) x$name)
mudims <- setNames(dim(muwvec), mudimnames)
mudims


rangeinds <- ncvar_get(pixcnc, "pixel_cloud/range_index")
max(rangeinds)
aziminds <- ncvar_get(pixcnc, "pixel_cloud/azimuth_index")
max(aziminds)

```

It appears that `num_pixels` and `num_lines` correspond to `range_index` and `azimuth_index`, respectively. This makes it easy to get a subset, using subsetnc. It would really be great to have this optimized!

OK, that's updated. This is a good test case. 

```{r}
library(microbenchmark)
devtools::load_all("../../subsetnc")
testfile1 <- tempfile()
testfile2 <- tempfile()


mbm <- function(...) microbenchmark(..., times = 10L)
sapply(classnc$var, function(x) x$prec)
mbm1 <- mbm(classnc_ss1 <- nc_subset(classnc, num_pixels %in% rangeinds, num_lines %in% aziminds, optimize = FALSE, filename = testfile1))
mbm2 <- mbm(classnc_ss2 <- nc_subset(classnc, num_pixels %in% rangeinds, num_lines %in% aziminds, optimize = TRUE, filename = testfile2))

mbm1$time
mbm2$time
```

Yay, it shaved off about 1/3 of the time! I can certainly optimize it further, but ya know, premature optimization and all...

```{r}
file_size(classncfile)
file_size(testfile1)
file_size(testfile2)
```

And it's about 1/3 the size of the original. 

```{r}
unlink(testfile1)
```


Now comes the hard part. 

```{r}
muwvec <- ncvar_get(classnc_ss2, "water_power")
mulvec <- ncvar_get(classnc_ss2, "land_power")

dim(muwvec)
dim(mulvec)
```

This may be where I stop for today. 
