---
title: "notebook20190807"
author: "Mark Hagemann"
date: "8/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Still working in yesterday's notebook, but I want to use this notebook to delve into integration of the gamma-uniform posterior. With help of wolfram alpha. 


Likelihood funciton

```{r}
theta_dens <- function(theta, p, mu_w, mu_l, nlooks = 4) {
  numer <- theta^(-nlooks) * exp(-p / theta)
  
  thetavec <- seq(mu_l / nlooks, mu_w / nlooks, length.out = 1000)
  denom <- sum(thetavec^(-nlooks) * exp(-p / thetavec))
}

theta_mean <- function(p, mu_w, mu_l, nlooks = 4) {
  thetavec <- seq(mu_l / nlooks, mu_w / nlooks, length.out = 1000)
  numer <- sum(thetavec^(1-nlooks) * exp(-p / thetavec))
  denom <- sum(thetavec^(-nlooks) * exp(-p / thetavec))
  numer / denom
}

wfrac_mean <- function(p, mu_w, mu_l, nlooks = 4) {
  thetavec <- seq(mu_l / nlooks, mu_w / nlooks, length.out = 1000)
  wfracvec <- seq(0, 1, length.out = 1000)
  numer <- sum(wfracvec * thetavec^(-nlooks) * exp(-p / thetavec))
  denom <- sum(thetavec^(-nlooks) * exp(-p / thetavec))
  numer / denom
}

rownum <- 166764
t1 <- with(wfracdf[rownum, ], mu_l / 4)
t2 <- with(wfracdf[rownum, ], mu_w / 4)
p <- wfracdf$coherent_power[rownum]
numermean <- with(wfracdf[rownum, ], theta_mean(coherent_power, mu_w, mu_l, 4))
rhspiece <- with(wfracdf[rownum, ], numermean * coherent_power^(2))
gammainc(2, p / t1)
gammainc(2, p / t2)

gammainc(p / t2, 2) - gammainc(p / t1, 2)
incgam(p / t2, 2) - incgam(p / t1, 2)


# with(wfracdf[362, ], wfrac_mean(coherent_power, mu_w, mu_l, 4))
```

OK, I think I have this figured out. Outline the steps. 

- integration constant, c such that f(theta) = c L(theta) is a valid pdf
- mean: integrate c theta L(theta)
- 2nd moment: integrate c theta^2 L(theta)

```{r}
# integration constant
gu_constant <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  out <- p^(1 - nlooks) * (incgam(p / t2, nlooks - 1) - 
                             incgam(p / t1, nlooks - 1))
  out
}

with(wfracdf[1, ], gu_constant(coherent_power, mu_w, mu_l))

gu_mean <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  const <- 1 / gu_constant(p, mu_w, mu_l, nlooks)
  
  out <- const * p^(2 - nlooks) * (incgam(p / t2, nlooks - 2) - 
                             incgam(p / t1, nlooks - 2))
  out
}

with(wfracdf[1, ], gu_mean(coherent_power, mu_w, mu_l))

gu_var <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  const <- 1 / gu_constant(p, mu_w, mu_l, nlooks)
  mu <- gu_mean(p, mu_w, mu_l, nlooks)
  
  mom2 <- const * p^(3 - nlooks) * (incgam(p / t2, nlooks - 3) - 
                             incgam(p / t1, nlooks - 3))
  out <- mom2 - mu^2
  out
}

with(wfracdf[1, ], gu_var(coherent_power, mu_w, mu_l)) %>% sqrt()

```

Right on! I got the moments. 


Finally, I can run the pixel clouds through riverobs and validate the output. 

OK, ran riverobs. Now let's validate. 

(interjecting from the future to add a hybrid "orig-si" method, combining orig estimate, scale-invariant uncertainty)

```{r}
dir_copy("../output/area-error/orig/", "../output/area-error/orig_si")

file.copy("../output/area-error/pixel_cloud_orig.nc", 
          "../output/area-error/pixel_cloud_orig_si.nc")

si_nc <- nc_open("../output/area-error/pixel_cloud_scaleinv.nc")
newuncert <- ncvar_get(si_nc, "pixel_cloud/water_frac_uncert")
origsi_nc <- nc_open("../output/area-error/pixel_cloud_orig_si.nc", write = TRUE)

ncvar_put(origsi_nc, "pixel_cloud/water_frac_uncert", vals = newuncert)

nc_close(si_nc)
nc_close(origsi_nc)
```



```{r}

allmethods <- c("orig", "igapprox", "iguninf", "scaleinv", "gamma_unif", 
                "orig_si")
valdirs <- fs::path("../output/area-error/", allmethods)

valdfs <- valdirs %>% 
  purrr::map(~rt_valdata(., flag_out_nodes = TRUE)) %>% 
  setNames(allmethods)

allvaldf <- valdfs %>% 
  bind_rows(.id = "method")

rt_val_qq(allvaldf, vars = "area_total", groupvars = "method") +
  facet_wrap(~method, scales = "free_y") + 
  theme_bw() + 
  ylab("scaled node area error")
  
ggsave("../fig/uncmethods_qq.png", width = 8, height = 5, dpi = 300)


```

