---
title: "notebook20190806"
author: "Mark Hagemann"
date: "8/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


I'm still chugging along with results in the 0802 notebook, but I'm also trying out an integration of actual gamma_uniform distribution. Possible I can get density after all!

```{r}
library(pracma)
gammainc(3, 0)
incgam(3, 0)

## DON'T NEED TO APPROXIMATE! INTEGRAL IS BOUNDED AT WFRAC = [0,1]
# denom_gu_approx <- function(x, k, upper = 1e7) {
#   x^(1 - k) * gammainc(k - 1, x / upper)[1]
# }

denom_gu <- function(x, k, lower, upper) {
  # browser()
  f1 <- x^(1 - k) * gammainc(k - 1, x / upper)[2]
  print(f1)
  f0 <- x^(1 - k) * gammainc(k - 1, x / lower)[2]
  print(f0)
  f1 - f0
}

denom_gu_approx(1e-11, 4, 1e3)
denom_gu(1e-11, 4, 1e-12 / 4, 1e-10 / 4)




# approximate the density wrt wfrac
dgu_approx <- function(wfrac, mu_w, mu_l, power, nlooks, upper = 1e7) {
  
  x_theta <- (wfrac * (mu_w - mu_l) + mu_l) / nlooks
  
  # bounds on theta, based on water fraction bounds and mu's
  lwr_theta <- mu_l / nlooks
  upr_theta <- mu_w / nlooks
  keep <- x_theta > lwr_theta & x_theta < upr_theta
  
  out <- rep(0, length(x_theta))
  
  numer <- (x_theta[keep])^(-nlooks) * exp(-power / (x_theta[keep]))
  # print(numer)
  denom <- denom_gu(x = power, k = nlooks, 
                    lower = lwr_theta, upper = upr_theta)
  print(denom)
  out[keep] <- numer / denom
  out
  # numer
}

plot(0:100 / 50, dgu_approx(0:100 / 50, mu_w = 3, mu_l = 1, power = 2, nlooks = 4))

dgu_approx(0:100 / 50, mu_w = 1e-10, mu_l = 1e-12, power = 2e-11, nlooks = 4) *
      1 / 50

sum(dgu_approx(0:100 / 50, mu_w = 1e-10, mu_l = 1e-12, power = 2e-11, nlooks = 4) *
      1 / 50)

```

My guess is that the integral diverges. It definitely does! So the mean is undefined. Argh! But mine is bounded! 

I can't seem to figure out the incomplete gamma--scrap for now and just run with the likelihood. 

Try another tack: manually integrate to get moments

```{r}
wfrac_lik <- function(wfrac, )

# gu_moments <- function(p, nlooks, mu_w, mu_l, nn = 1000) {
#   wfracvec <- seq(0, 1, length.out = nn)
#   thetavec <- (wfracvec * (mu_w - mu_l) + mu_l) / nlooks
#   lik_theta <- thetavec^(-nlooks) * exp(-p / thetavec)
#   denom_theta <- sum(lik_theta)
#   
#   mean_wfrac <- sum(wfracvec * lik_theta / denom_theta)
#   mom2_wfrac <- sum(wfracvec^2 * lik_theta / denom_theta)
#   var_wfrac <- mom2_wfrac - mean_wfrac^2
#   
#   out <- c(mean = mean_wfrac, sd = sqrt(var_wfrac))
#   out
# }
# 
# gu_moments(6e-13, 4, 1e-10, 1e-12, nn = 1000)

```

Here's the actual moment funcitons (not approximated)

```{r}
# integration constant
gu_constant <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  out <- p^(1 - nlooks) * (incgam(p / t2, nlooks - 1) - 
                             incgam(p / t1, nlooks - 1))
  out
}

with(wfracdf[1, ], gu_constant(coherent_power, mu_w, mu_l))

gu_mean <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  const <- 1 / gu_constant(p, mu_w, mu_l, nlooks)
  
  out <- const * p^(2 - nlooks) * (incgam(p / t2, nlooks - 2) - 
                             incgam(p / t1, nlooks - 2))
  out
}

with(wfracdf[1, ], gu_mean(coherent_power, mu_w, mu_l))

gu_var <- function(p, mu_w, mu_l, nlooks = 4) {
  t1 <- mu_l / nlooks
  t2 <- mu_w / nlooks
  
  const <- 1 / gu_constant(p, mu_w, mu_l, nlooks)
  mu <- gu_mean(p, mu_w, mu_l, nlooks)
  
  mom2 <- const * p^(3 - nlooks) * (incgam(p / t2, nlooks - 3) - 
                             incgam(p / t1, nlooks - 3))
  out <- mom2 - mu^2
  out
}

gu_moments <- function(p, mu_w, mu_l, nlooks = 4) {
  meantheta <- gu_mean(p, mu_w, mu_l, nlooks)
  vartheta <- gu_var(p, mu_w, mu_l, nlooks)
  mean_wfrac <- (nlooks * meantheta - mu_l) / (mu_w - mu_l)
  var_wfrac <- (nlooks / (mu_w - mu_l))^2 * vartheta
  out <- c(mean = mean_wfrac, sd = sqrt(var_wfrac))
  out
}

gu_moments(6e-13, 1e-10, 1e-12, 4)

```



Deciding it's better to port the code beginning with moment estimation and pixel cloud creation into today's notebook. 

```{r}

wfrac_moments <- function(p, mu_w, mu_l, nlooks, 
                   method = c("orig", "igapprox", "iguninf", 
                              "scaleinv", "gamma_unif")) {
  method <- match.arg(method)
  
  if (method == "orig") {
    meanwfrac <- (p - mu_l) / (mu_w - mu_l)
    sdwfrac <- p / (mu_w - mu_l) / sqrt(nlooks)
  } else if (method == "igapprox") {
    # Uniform prior moments
    wfrachat_prior <- 0.5
    wfracvar_prior <- 1 / 12
    thetahat_prior <- (wfrachat_prior * (mu_w - mu_l) + mu_l) / nlooks
    thetavar_prior <- wfracvar_prior * (mu_w - mu_l)^2 / (nlooks^2)
    
    # prior inverse gamma parameters on theta (by moment matching to unif)
    alpha_prior <- thetahat_prior^2 / thetavar_prior + 2
    beta_prior <- thetahat_prior * (thetahat_prior^2 / thetavar_prior + 1)
    
    # posterior parameters on theta (inverse gamma)
    alpha_post <- alpha_prior + nlooks
    beta_post <- beta_prior + p
    
    # inverse gamma moments
    meanwfrac <- igmean_wfrac(alpha_post, beta_post, nlooks, mu_w, mu_l)
    sdwfrac <- sqrt(igvar_wfrac(alpha_post, beta_post, nlooks, mu_w, mu_l))

  } else if (method == "iguninf") {
    # Same, just boost the variance to make "uninformative"
    # Uniform prior moments
    wfrachat_prior <- 0.5
    wfracvar_prior <- 25
    thetahat_prior <- (wfrachat_prior * (mu_w - mu_l) + mu_l) / nlooks
    thetavar_prior <- wfracvar_prior * (mu_w - mu_l)^2 / (nlooks^2)
    
    # prior inverse gamma parameters on theta
    alpha_prior <- thetahat_prior^2 / thetavar_prior + 2
    beta_prior <- thetahat_prior * (thetahat_prior^2 / thetavar_prior + 1)
    
    # posterior parameters on theta (inverse gamma)
    alpha_post <- alpha_prior + nlooks
    beta_post <- beta_prior + p
    
    # inverse gamma moments
    meanwfrac <- igmean_wfrac(alpha_post, beta_post, nlooks, mu_w, mu_l)
    sdwfrac <- sqrt(igvar_wfrac(alpha_post, beta_post, nlooks, mu_w, mu_l))
    
  } else if (method == "scaleinv") {
    # scale-invariant prior
    # posterior is inverse gamma -- limit as alpha, beta priors go to zero. 
    meanwfrac <- (nlooks / (nlooks - 1) * p - mu_l) / (mu_w - mu_l)
    sdwfrac <- nlooks * p / (mu_w - mu_l) / (nlooks - 1) * (nlooks - 2)^(-1/2)
  } else if (method == "gamma_unif") {
    moms <- gu_moments(p, mu_w, mu_l, nlooks)
    meanwfrac <- moms["mean"]
    sdwfrac <- moms["sd"]
  } else {
    stop(sprintf("method %s not recognized.\n", method))
  }
  
  out <- list(mean = meanwfrac, sd = sdwfrac)
  out
}
```

### Compare moments. 

```{r}

allmomfun <- function(tosrow) {
  
  cohpow <- tosrow$coh_power
  muw <- tosrow$mu_w
  mul <- tosrow$mu_l
  nlook <- tosrow$nefflooks
  allmethods <- c("orig", "igapprox", "iguninf", "scaleinv", "gamma_unif")
  momveclist <- allmethods %>% 
    purrr::map(~wfrac_moments(p = cohpow, mu_w = muw, mu_l = mul, 
                             nlooks = nlook, method = .)) %>% 
    purrr::map(~as.data.frame(.))
  momdf <- dplyr::bind_rows(setNames(momveclist, allmethods),
                                .id = "method")
  momdf
}


allmomdf <- testobs_small %>% 
  split(f = 1:nrow(.)) %>% 
  purrr::map(~allmomfun(.)) %>% 
  bind_rows(.id = "pixel") %>% 
  mutate(pixel = as.factor(as.numeric(pixel)),
         lower = mean - 2 * sd, upper = mean + 2 * sd)

allmomdf %>% glimpse() %>% 
  ggplot(aes(x = method, ymin = lower, ymax = upper)) + 
  geom_linerange(aes(color = method), size = 0.8) + 
  facet_wrap(~pixel, scales = "free_y")

```



### Pixel clouds

Where did I last do this? Answer: 20190730 notebook. 


```{r}
pixcncfile <- path(rodir(65), "pixel_cloud.nc")
pixcdf <- pixc_read(pixcncfile)
# pixcnc <- nc_open(pixcncfile)
# pixcnc$dim$`pixel_cloud/points`$len
# nc_close(pixcnc)
rangeinds <- unique(pixcdf$range_index) + 1 # adjust zero-referenced indices
aziminds <- unique(pixcdf$azimuth_index) + 1


devtools::load_all("../../subsetnc")
classncfile <- path(rodir(65), "intermediate_class_maps_0.nc")
classnc <- nc_open(classncfile)
classnc_ss2 <- nc_subset(classnc, num_pixels %in% rangeinds, num_lines %in% aziminds)
nc_close(classnc)
  
wfracdf <- intermed2pixc(classnc_ss2, 
                         varids = c(mu_w = "water_power", mu_l = "land_power",
                                    cohpow_classnc = "coherent_power"),
                         pixcdf = pixcdf)

wfracdf %>% 
  sample_n(200) %>% 
  plot(coherent_power ~ cohpow_classnc, .)

# Make and fill the new netcdfs. 
allmethods <- c("orig", "igapprox", "iguninf", "scaleinv", "gamma_unif")
alphahatvecs <- lapply(allmethods, function(x) wfracdf$water_frac) %>% 
  setNames(allmethods) %>% as.data.frame()
sigalphavecs <- lapply(allmethods, function(x) wfracdf$water_frac_uncert) %>% 
  setNames(allmethods) %>% as.data.frame()


for (method in allmethods[-1:-2]) {
  print(method)
  newncfile <- sprintf("../output/area-error/pixel_cloud_%s.nc", method)
  file.copy(pixcncfile, newncfile)
  pixcnc <- nc_open(pixcncfile)
  newnc <- nc_open(newncfile, write = TRUE)
  
  fullnc_range <- ncvar_get(pixcnc, "pixel_cloud/range_index")
  fullnc_azim <- ncvar_get(pixcnc, "pixel_cloud/azimuth_index")
  fullnc_rangeazim <- fullnc_range * 1e5 + fullnc_azim
  
  df_rangeazim <- with(wfracdf, range_index * 1e5 + azimuth_index)
  
  rangeazim_match <- match(df_rangeazim, fullnc_rangeazim)
  
  newalphahat <- rep(NA_real_, nrow(wfracdf))
  newsigalpha <- rep(NA_real_, nrow(wfracdf))
  pbar <- progress::progress_bar$new(total = nrow(wfracdf))
  for (i in 1:length(newalphahat)) {
    # indi <- rangeazim_match[i]
    indi <- i
    rowi <- wfracdf[indi, ]
    momsi <- wfrac_moments(p = rowi$coherent_power, mu_w = rowi$mu_w,
                           mu_l = rowi$mu_l, nlooks = 4, method = method)
    
    newalphahat[indi] <- momsi$mean
    newsigalpha[indi] <- momsi$sd
    pbar$tick()
  }
  
  alphahatvecs[[method]] <- newalphahat
  sigalphavecs[[method]] <- newalphahat
  
  alphahat_toput <- ncvar_get(pixcnc, "pixel_cloud/water_frac")
  alphahat_toput[rangeazim_match] <- newalphahat
  
  sigalpha_toput <- ncvar_get(pixcnc, "pixel_cloud/water_frac_uncert")
  sigalpha_toput[rangeazim_match] <- newsigalpha

  # testinds <- sample(rangeazim_match, 200)
  # plot(alphahat_toput[testinds], 
  #      ncvar_get(pixcnc, "pixel_cloud/water_frac")[testinds]); abline(0, 1)
  
  ncvar_put(newnc, "pixel_cloud/water_frac", alphahat_toput)
  ncvar_put(newnc, "pixel_cloud/water_frac_uncert", sigalpha_toput)
  nc_close(newnc)
  nc_close(pixcnc)
  
}

alphahatvecs %>% 
  sample_n(400) %>% 
  pairs()

sigalphavecs %>% 
  sample_n(400) %>% 
  pairs()


```

Good. Next step is to run through riverobs. 