---
title: "notebook20190128"
author: "Mark Hagemann"
date: "January 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Working on getting some netcdfs plotted. I'm using [iris](https://scitools.org.uk/iris/docs/latest/). See also my daily work journal for today. 

Just added iris to my RiverObs conda environment.

```{r}
use_condaenv("RiverObs", required = TRUE)

conda_list()

list.files("../../river")
```


```{python}
# import iris
import os
import numpy as np

datadir = "../data/uncertainty_example/"
filename = datadir + "pixel_cloud.nc"

# os.listdir(datadir)
```

```{python}
cube1 = iris.load_cube(filename, "classification")
raw1 = iris.load_raw(filename)
raw1.extract(constraints= "classification")
# cube1.name()

```

"No cubes found". I wonder if the netcdfs I have aren't in the right format?


```{python}
cubes = iris._generate_cubes(filename, callback = None, constraints=None)
result = iris.cube._CubeFilterCollection.from_cubes(cubes, constraints=None)
result.cubes()
```

Well that's where I'll have to leave it for now. Come back to this later tonight. 


Punting on iris for now. Try just with netcdf4

```{python}
import netCDF4 as nc4

f = nc4.Dataset(filename)
f.enumtypes.keys()
f.variables.items()
# f.ncattrs()
f_dims = [dim for dim in f.dimensions]
f_dims
# f.close()
```

Maybe there's something wrong with the toy netcdf from Brent.

```{python}
fname2 = "D:/data/sac-simulator-output/tile-Sac-23Jan2019/tile-Sac-23Jan2019/pixel_cloud.nc"
f2 = nc4.Dataset(fname2)
f2.dimensions.keys()

foo = f2.groups["pixel_cloud"].variables["longitude"]
bar = f2.groups["pixel_cloud"].variables["latitude"]

np.nanmin(foo)
np.min(foo)
np.max(foo)
np.nanmax(foo)

np.min(bar)
np.max(bar)
# np.argwhere(np.isnan(bar))

# foo[12575:12585]
# bar[12575:12585]
foo.min()
```

No, it would seem that the updated pixc doesn't have those either. 

Looking through the RiverObs code, I see that I need to specify the group:

```{python}
f2.groups.keys()
f2pixc = f2.groups['pixel_cloud']
f2pixc.dimensions
```

OK--try again with iris?

```{python}
cube1 = iris.load_raw(filename)
# raw1 = iris.load_raw(filename)
```

Alright, not worth it. 

```{python}
f1pixc = f.groups["pixel_cloud"]
f1pixc.variables.keys()
f1pixc.dimensions.keys()
f1pixc.dimensions['points']
f1pixc.dimensions['depth']
f1pixc.variables["height"][0:99]

```

Alright, that's a start. Next try a random subset of heights. 

```{python}
import pandas

foo = range(10)
# np.random.choice(10, 10, replace = False)

randinds = np.random.choice(195152, 1000, replace = False)


h_sset = f1pixc.variables["height"][randinds]
lat_sset = f1pixc.variables["latitude"][randinds]
lon_sset = f1pixc.variables["longitude"][randinds]

h_array = np.column_stack((h_sset, lat_sset, lon_sset))
h_df = pandas.DataFrame([['latitude', lat_sset], ['longitude', lon_sset], 
    ['height', h_sset]])  
# h_array
```

I think best to plot this in R. Time to really put reticulate to use!

```{r}
foo <- py$h_array
bar <- py$h_df
class(foo)
class(bar)
head(foo)
head(bar)
```


Just work with the dumb numpy.

```{r}
h_df <- py$h_array %>% 
  as.data.frame() %>% 
  setNames(c("height", "lat", "lon")) %>% 
  glimpse()

```

Map it.

```{r}
library(leaflet)



leaflet(h_df) %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1)
```


Great. That's the workflow I'll go with for now. But the more pressing issue is to get RiverObs running and producing output on the new pixel cloud. 

Good news is that coffee is working (weird feeling coupled with total lack of sleep)

Get a handle on requisite file locations. 

```{r}
pixc <- "D:/data/sac-simulator-output/tile-Sac-23Jan2019/tile-Sac-23Jan2019/pixel_cloud.nc"
prior_reach <- "D:/data/SWOT-prior/PriorDistributionFolder/netcdfv2/NA07.nc"
```

Ugh, which prior netcdf is it? (Good opportunity to streamline visualizing workflow)

```{python}
ds1 = nc4.Dataset(r.prior_reach)
rchs1 = ds1.groups['reaches']
rchs1.variables.keys()

nodes1 = ds1.groups['nodes']
nnodes = nodes1.dimensions['numb_nodes'].size

randinds = np.random.choice(nnodes, min(nnodes, 1000))
lon1 = nodes1.variables['x'][randinds]
lat1 = nodes1.variables['y'][randinds]

arr1 = np.column_stack((lon1, lat1))
```


```{r}
py$arr1 %>% 
  as.data.frame() %>% 
  setNames(c("lon", "lat")) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1)
  
```

That looks like it. See if it matches the pixel cloud.


```{python}
ds2 = nc4.Dataset(r.pixc)
pixc2 = ds2.groups['pixel_cloud']
pixc2.variables.keys()

# pixc2.dimensions.keys()
npix = pixc2.dimensions['points'].size
# 
randinds2 = np.random.choice(npix, min(npix, 1000))
lon2 = pixc2.variables['longitude'][randinds2]
lat2 = pixc2.variables['latitude'][randinds2]

arr2 = np.column_stack((lon2, lat2))
```


```{r}
pixc_df <- py$arr2 %>% 
  as.data.frame() %>% 
  setNames(c("lon", "lat")) %>% 
  mutate(lon = lon - 360)

summary(pixc_df)


py$arr1 %>%
  as.data.frame() %>%
  setNames(c("lon", "lat")) %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(radius = 1) %>%
  addCircleMarkers(radius = 1, color = "red", data = pixc_df)
```

Finally got swot_pixc2rivertile to run, but it errors complaining about being unable to convert a fill value to uint32. I think it's in the node/node_id of the priordb. 

```{python}
priorfile = "D:/data/SWOT-prior/PriorDistributionFolder/netcdfv2/NA07.nc"
f = nc4.Dataset(priorfile)

np.max(f.groups['nodes'].variables['node_id'])

f.close()
```

OK, not there. (I'm looking for a `fill_value -9990000000.0`)

I see now, (shift+ctrl+F) FILL_VALUE is set as -9.99e9 in products/netcdf.py.

Fixed that. And now set up PYTHONPATH as a (user) environment variable so I no longer have to use the .bat file. Also made a script to set file location environment variables for use locally in swot-error project. Still getting warnings, and latest error is "Exception: number of good points: 0 smaller than required: 100". But that's a problem for another time. 
