---
title: "notebook20190211"
author: "Mark Hagemann"
date: "2/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Starting off: track down width errors between pixc and gdem. 

- Is the error the same at reach scale? Yes!

Now check out pixcvec comparison. First make a function for loading that data. DONE (over in lib/netcdf.R)

```{r}
sac_pcv <- pixcvec_read("../output/sac04/pcv.nc")
sac_gd_pcv <- pixcvec_read("../output/sac01/pcv_gdem.nc")
```


Leaflet map for a random node


```{r}
library(leaflet) 
randnode <- sample(unique(sac_pcv$node_index), 1)
randrch <- sample(unique(sac_pcv$reach_index), 1)

pcv_mapdata <- sac_pcv %>% 
  # filter(node_index == randnode) %>%
  filter(reach_index == randrch) %>%
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)

pcv_gd_mapdata <- sac_gd_pcv %>% 
  # filter(node_index == randnode) %>%
  filter(reach_index == randrch) %>%
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)


leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, data = pcv_mapdata) %>% 
  addCircleMarkers(radius = 1, color = "red", data = pcv_gd_mapdata)



```


Check the pixel classes.

```{r}
pcv_mapdata %>% 
  glimpse()
```


It would be really helpful if I could just plot a pixc file. Can I? Yes!

```{r}
sacdir <- "D:/data/sac-simulator-output/tile-Sac-23Jan2019/tile-Sac-23Jan2019/"
sacpixc <- pixc_read(paste0(sacdir, "pixel_cloud.nc"))
```

Plot a subset of each class. 

```{r}
sacpixc %>% 
  dplyr::filter(classification == 4) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1)
```

Here's a single node colored by class

```{r}

latmin <- min(pcv_mapdata$lat, na.rm = TRUE)
lonmin <- min(pcv_mapdata$lon, na.rm = TRUE)
latmax <- max(pcv_mapdata$lat, na.rm = TRUE)
lonmax <- max(pcv_mapdata$lon, na.rm = TRUE)

pal <- colorFactor("Set1", domain = sacpixc$classification)

sacpixc %>% 
  filter(latitude >= latmin, longitude >= lonmin, 
         latitude <= latmax, longitude <= lonmax) %>%
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, color = ~pal(classification))
```

Now trying with a database Rui sent. 

```{r}
testdb <- pixcvec_read("../output/sac04/pcv.nc")
```

OK, all of this doesn't matter--I've sorted it out. I'll need to come up with a new set of slides. Work on outlining that. Also some kind of methodology. Perhaps this belongs in a report. 




