---
title: "notebook20190823"
author: "Mark Hagemann"
date: "8/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm working today on manuscript figures.

Need to track down why area and width errors look so different at reach scale. 

```{r}
ro_manifest() %>% 
  filter(day == 131, notes == "manuscript") %>% glimpse() 

rodir(71, "composite") %>% 
  rt_valdata(group = "reaches") %>% 
  rt_val_scatter(variables = c("width", "area_total"), yvar = "relerr")

rodir(71, "composite") %>% 
  rt_valdata(group = "reaches") %>% 
  rt_val_scatter(variables = c("width", "area_total"), yvar = "err")


```

```{r}
rodir(71, "composite/rt.nc") %>% 
  # rt_valdata() %>%
  rt_read() %>% 
  glimpse() %>% 
  filter(reach_id == 6) %>% 
  mutate(radius = sqrt(area_total / pi)) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(radius = ~radius, popup = ~paste(node_id))
  
```

```{r}

pixc71 <- rodir(71, "composite", "pixel_cloud_new.nc") %>% 
  pixc_read()
pcv71 <- rodir(71, "composite", "pcv.nc") %>% pixcvec_read()

gdpixc71 <- rodir(71, "fake_pixc.nc") %>% 
  pixc_read()
gdpcv71 <- rodir(71, "composite", "pcv_gdem.nc") %>% pixcvec_read()

gdpix71 <- pixc_join(gdpixc71, gdpcv71)

nodeval71 <- rodir(71, "composite") %>% 
  rt_valdata()

pixc71 %>% 
  pixc_join(pcv71) %>% 
  map_node_pixc(nodes = 437, gdemdf = gdpix71)
```

How exactly does reach area relate to width? Right, it's a simple scaling by node length, which I don't have. But I can compute pretty easily. 

```{r}
rtnode71 <- rodir(71, "composite", "rt.nc") %>% 
  rt_read()

gdnode71 <- rodir(71, "composite", "rt_gdem.nc") %>% 
  rt_read()

rtnodelens <- rtnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  select(node_id, nodelen)

gdnodelens <- gdnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  select(node_id, nodelen)

inner_join(rtnodelens, gdnodelens, by = "node_id") %>% 
  filter(node_id > min(node_id), node_id < max(node_id)) %>% 
  mutate(len_diff = nodelen.x - nodelen.y) %>% 
  ggplot(aes(x = node_id, y = len_diff)) + 
  geom_point()

list(rt = rtnodelens, gdem = gdnodelens) %>% 
  bind_rows(.id = "source") %>% 
  filter(node_id > min(node_id), node_id < max(node_id)) %>% 
  ggplot(aes(x = node_id, y = nodelen, color = source)) +
  geom_point()

```

Areas now (the other component of width calculation)

```{r}
rtareas <- rtnode71 %>% 
  select(node_id, area_total)

gdareas <- gdnode71 %>% 
  select(node_id, area_total)

inner_join(rtareas, gdareas, by = "node_id") %>% 
  filter(node_id > min(node_id), node_id < max(node_id)) %>% 
  mutate(area_diff = area_total.x - area_total.y) %>% 
  ggplot(aes(x = node_id, y = area_diff)) + 
  geom_point()

list(rt = rtareas, gdem = gdareas) %>% 
  bind_rows(.id = "source") %>% 
  filter(node_id > min(node_id), node_id < max(node_id)) %>% 
  ggplot(aes(x = node_id, y = area_total, color = source)) +
  geom_point()
```




```{r}
rtreach0 <- rodir(71, "composite", "rt.nc") %>% 
  rt_read(group = "reaches")
gdreach0 <- rodir(71, "composite", "rt_gdem.nc") %>% 
  rt_read(group = "reaches")

rtreach <- rtnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  add_offset(rtreach0) %>% 
  reach_agg(weight = FALSE)

gdreach <- gdnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  add_offset(gdreach0) %>% 
  reach_agg(weight = FALSE)

rtreach %>% 
  ggplot(aes(x = reach_id, y = area_total)) + 
  geom_point() + 
  geom_point(data = gdreach, color = "red")

```



What happens when nodes are missing from the reach? 

- reach area = sum(node area) for nodes in reach
- reach width = sum(node area) / sum(node length) for nodes in reach


Plot my aggregated reach against read-in reach. Ditto for width. 

```{r}
reachdf_compare <- list(orig = rtreach0, redid = rtreach) %>% 
  bind_rows(.id = "method") %>% 
  select(method, reach_id, area_total, width, area_tot_u, width_u)

reachdf_compare %>% 
  ggplot(aes(x = reach_id, y = area_total, color = method)) + 
  geom_point()

reachdf_compare %>% 
  ggplot(aes(x = reach_id, y = width, color = method)) + 
  geom_point()

```

What's going on with reach 1?

```{r}
rtnode71 %>% 
  filter(reach_id == 1) %>% 
  # summary() %>% 
  add_nodelen(force = TRUE) %>% 
  summarize(area = sum(area_total), length = sum(nodelen), width = area / length)

rtreach0 %>% 
  filter(reach_id == 1) %>% 
  select(area_total, width)
```

OK, fixed a bug in add_nodelen()

Mabye if I do reach_agg and then rt_valdata_df()

```{r}
rt_valdata_df(rtreach, gdreach) %>% 
  rt_val_scatter(variables = c("width", "area_total"), yvar = "relerr")
```

No...

If area error is positive, width area should also be positive, unless reach length is different. 

```{r}
rtreachlens <- rtnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  select(node_id, reach_id, nodelen) %>% 
  group_by(reach_id) %>% 
  summarize(reachlen = sum(nodelen))

gdreachlens <- gdnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  select(node_id, reach_id, nodelen) %>% 
  group_by(reach_id) %>% 
  summarize(reachlen = sum(nodelen))

list(rt = rtreachlens, gdem = gdreachlens) %>% 
  bind_rows(.id = "source") %>% 
  # filter(node_id > min(node_id), node_id < max(node_id)) %>% 
  ggplot(aes(x = reach_id, y = reachlen, color = source)) +
  geom_point()
```

Conclusion: I should subset to intersection of node id's before doing reach_agg(). OK, I added a "usenodes" argument to reach_agg().

```{r}
rtreach <- rtnode71 %>% 
  add_nodelen(force = TRUE) %>% 
  add_offset(rtreach0) %>% 
  reach_agg(weight = FALSE)

gdreach <- gdnode71 %>% 
  filter(node_id %in% rtnode71$node_id) %>% 
  add_nodelen(force = TRUE) %>% 
  add_offset(gdreach0) %>% 
  reach_agg(weight = FALSE)


rt_valdata_df(rtreach, gdreach) %>% 
  rt_val_scatter(variables = c("width", "area_total"), yvar = "relerr")
```


Note: neither version of reach validation was previously correct! I'll likely have to manually edit the fake pixel clouds--or just exclude reach 7. Although--why is reach 6 so bad? Nodes missing here?

```{r}
list(rt = rtnode71, gd = gdnode71) %>% 
  bind_rows(.id = "source") %>% 
  filter(reach_id == 6) %>% 
  ggplot(aes(x = node_id, y = area_total)) +
  geom_point() + 
  facet_grid(rows = vars(source))
```

Yes, that appears to be the issue. Finally, I can move on to writing. 