---
title: "notebook20190504"
author: "Mark Hagemann"
date: "5/4/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
opts_knit$set(root.dir = "~/Documents/swot-error")
```

```{r}
library(ProjectTemplate)
load.project()
pixcdf <- join_pixc(rodir(18))
```


Today I'm making a function to do animations of pixel cloud netcdfs. Ideally this will farm out the rendering to a separate process so I don't have to wait for it. 

First see if I can use `ggforce::geom_circle()` to do pixel maps as I've previously done using leaflet. 

```{r, eval = FALSE}

pixcdf %>% 
  filter(node_index %in% 301:305) %>% 
  transmute(latitude, longitude, node_index, 
            classification = as.factor(classification), 
            radius_m = sqrt(pixel_area / pi),
            radx_deg = radius_m * 360 / 40075000,
            rady_deg = radx_deg * cos(latitude * pi / 180)) %>% 
  ggplot() +
  geom_point(aes(x = longitude, y = latitude, color = classification), size = 1)
  # geom_ellipse(aes(x0 = longitude, y0 = latitude, a = radx_deg, b = rady_deg,
  #                  angle = 0, fill = classification, color = classification))
```

How bad is it to animate in leaflet?

```{r}
library(leaflet)
library(crosstalk)

copal <- colorFactor("Set1", domain = as.factor(pixcdf$classification))


prepdf <- pixcdf %>% 
  filter(node_index %in% 301:305) %>% 
  transmute(latitude, longitude, node_index, pixc_index,
            height,
            time = illumination_time %% 10,
            time = round(time * 1000), 
            classification = as.factor(classification), 
            radius_m = sqrt(pixel_area / pi),
            radx_deg = radius_m * 360 / 40075000,
            rady_deg = radx_deg * cos(latitude * pi / 180))

pixcdf_shared <- prepdf  %>% 
  SharedData$new()


bscols(
  filter_slider("time", "Time", pixcdf_shared, column = ~time, width = 250,
              # value = ~c(min(time), min(time) + 0.01),
              animate = animation_options(loop = TRUE)),
  pixcdf_shared %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(radius = ~radius_m, fillColor = ~copal(classification), stroke = FALSE,
             fillOpacity = 0.8)

)


```

I guess I conclude that the animation doesn't work outside of a shiny app. And that's really all for today. Sheesh.

Let's try a different tack. Start with a plotly animation for height as a function of along-reach distance. 

```{r}
hgg <- prepdf %>% 
  ggplot(aes(x = time, y = height, text = node_index, frame = time, group = pixc_index)) +
  geom_point(aes(color = classification))
hgg

hggp <- ggplotly(hgg, tooltip = "text")

animation_slider(hggp, transition = 0)

```




```{r, eval=FALSE}

#' @param maptype Passed to \code{ggamp::get_map()}
pixc_animate <- function(ncfile, sattrack = FALSE, pixels = TRUE,
                         maptype = "terrain", ) {
  if (!(pixels || sattrack)) 
    stop("At least one of pixels or sattrack must be TRUE")
  
  
  
}
```


