---
title: "notebook20181119"
author: "Mark Hagemann"
date: "November 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
foo <- nc_open("../data/sac-pixc/109_ellip_off_heights_sac_cycle_0001_pass_0249_presum2.125.AzPTR.Presum.Noise.LeftSwath.Unflat.Multilook_L2PIXC.nc")

foo
if_real <- ncvar_get(foo, varid = "ifgram_real")
if_imag <- ncvar_get(nc = foo, varid = "ifgram_imag")
pwr1 <- ncvar_get(foo, varid = "power_left")
pwr2 <- ncvar_get(foo, varid = "power_right")

nlooks <- ncvar_get(foo, "num_looks")

nc_close(foo)
```

Per Brent's email: |complex ifgram| / sqrt(power1 * power2)


Some interferogram values are negative. Like 1/4 of them. Just omit for now.

```{r}

# if_real[if_real <= 0] <- NA
# if_imag[if_imag <= 0] <- NA

# coh_denom_log <- 1/2 * (log(if_real) + log(if_imag))
coh_denom_log <- 1/2 * (log(pwr1) + log(pwr2))

coh_denom <- exp(coh_denom_log)
if_norm <- sqrt(if_real^2 + if_imag^2)

coh_calc_log <- log(if_norm) - coh_denom_log

coh_calc <- if_norm / coh_denom

summary(if_real)
summary(if_imag)
summary(pwr1)
summary(pwr2)
summary(coh_calc)

```

This works somehow! Even though orders of magnitude are crazy wide-ranging!

Next compute variance

```{r}
var_approx <- 1 / (2 * nlooks) * (1 - coh_calc^2) / coh_calc^2
summary(var_approx)
```

To aggregate this, I'll need a node shapefile. Also a DEM.



```{r}
foo <- nc_open("../data/sac-pixc/109_ellip_off_heights_sac_cycle_0001_pass_0249_presum2.125.AzPTR.Presum.Noise.LeftSwath.Unflat.Multilook_L2PIXC.nc")

med_lat <- ncvar_get(foo, "latitude_medium")
med_lon <- ncvar_get(foo, "longitude_medium")
wd_lat <- ncvar_get(foo, "latitude_welldone")
wd_lon <- ncvar_get(foo, "longitude_welldone")

plot(wd_lat[1:1000 * 100], med_lat[1:1000 * 100])
length(unique(wd_lat))
length(unique(med_lat))

nc_close(foo)
```

Now about that shapefile.

```{r}


node_shp <- st_read("../data/sac-nodedb/Sacramento-NodeDatabase.shp")
reach_shp <- st_read("../data/sac-reachdb/Sacramento-ReachDatabase.shp")

plot(node_shp)
plot(reach_shp["Reach_ID"])

glimpse(node_shp)
glimpse(reach_shp)
```

Now make a spatial data.frame for the pixc data. Then I can assign to nodes.

```{r}
foo <- nc_open("../data/sac-pixc/109_ellip_off_heights_sac_cycle_0001_pass_0249_presum2.125.AzPTR.Presum.Noise.LeftSwath.Unflat.Multilook_L2PIXC.nc")

names(foo$var)

getvec <- function(...) {
  out0 <- ncvar_get(...)
  out <- as.vector(out0)
  out
}
pixc_df <- data.frame(
  lat = getvec(foo, "latitude_medium"),
  lon = getvec(foo, "longitude_medium"),
  height = getvec(foo, "height_medium"),
  class = getvec(foo, "classification"),
  xtrack = getvec(foo, "cross_track_medium"),
  nlooks = getvec(foo, "num_looks"),
  dhdphi = getvec(foo, "dheight_dphase_medium"), # meters per radian
  phase_var = as.vector(var_approx)
)

nc_close(foo)

pixc_sf <- pixc_df %>% 
  filter(lat > 0) %>% 
  st_as_sf(coords = c("lon", "lat"), crs = 4326) %>% 
  mutate(h_var_pix = phase_var * dhdphi^2)
glimpse(pixc_sf)
```


Aggregate by node.

I need (pretty sure) a different package for doing Thiessen analysis

Or not. Try `st_nearest_points` NOPE!

```{r}
library(dismo)

spts <- as(node_shp$geometry, "Spatial")
node_voroni <- voronoi(spts)

plot(node_voroni)
# points(sample_n(pixc_sf, 100), col = "red")
node_voroni_sf <- st_as_sf(node_voroni)

glimpse(node_voroni_sf)
```

Aggregate!

```{r}
pixc_agg <- st_within(sample_n(pixc_sf, 10000), node_voroni_sf, sparse = FALSE)

dim(pixc_agg)
anywhich <- function(x) ifelse(length(which(x)) < 1, NA, which(x))
elems <- apply(pixc_agg, 1, anywhich)

```

Not within! Time to plot more interactively.

```{r}
library(leaflet)

leaflet(node_voroni_sf) %>% 
  addTiles() %>% 
  addPolygons() %>% 
  addCircleMarkers(data = sample_n(pixc_sf, 1000), radius = 2, color = "red")

```

Getting to the limits of what I can do on the laptop. Finish workflow, then leave scaling-up for a more muscular machine.

- Attach nearest node info to pixc. 
- aggregate variance by node, paying attention to classification
- Get validation heights

...

Back and coockin' on the desktop now!

Map pixc to nodes.

```{r}
pixc_agnode <- pixc_sf %>% 
  st_within(node_voroni_sf, sparse = FALSE)

whichnode <- apply(pixc_agnode, 1, anywhich)

pixc_sf$nodeid <- whichnode

pixc_sf %>% 
  filter(nodeid == nodeid[1]) %>% 
  dplyr::select(class) %>% 
  plot()
```



```{r}
pal <- colorNumeric(
  palette = "Blues",
  domain = pixc_sf$nodeid)

pal2 <- colorNumeric(
  palette = "Blues",
  domain = pixc_sf$xtrack)

pal3 <- colorNumeric(
  palette = "Blues",
  domain = pixc_sf$dhdphi)

pal4 <- colorNumeric(
  palette = "Blues",
  domain = log(pixc_sf$phase_var))


pixc_sf %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 2, color = ~pal3(dhdphi))
  # addCircleMarkers(radius = 2, color = ~pal4(log(phase_var)))
```



Estimate height, aggregate variance.

```{r}
glimpse(pixc_sf)
pixc_ag_sf <- pixc_sf %>% 
  group_by(nodeid) %>% 
  summarize(height = mean(height), medheight = median(height),
            h_var_node = mean(h_var_pix))

```

Now get the truth

```{r}
sac_node_truth <- st_read("../data/sac-truth/SWOT_L2_HR_River_SP_001_249_Sac_20090109T000000_Node_Truth/SWOT_L2_HR_River_SP_001_249_Sac_20090109T000000_Node_Truth/SWOT_L2_HR_River_SP_001_249_Sac_20090109T000000_Node_Truth.shp") %>% 
  sf:::select.sf(reach_id, node_id, height, width)

nodemap <- st_within(sac_node_truth, node_voroni_sf, sparse = FALSE)

sac_node_truth$nodeid <- apply(nodemap, 1, anywhich)
```


```{r}
pixc_ag_df <- within(as.data.frame(pixc_ag_sf), {geometry = NULL})
sac_node_truth_df <- within(sac_node_truth, {geometry = NULL})
valdf <- pixc_ag_df %>% 
  rename(h_pixc = height) %>% 
  left_join(sac_node_truth_df, by = "nodeid", st_join = FALSE) %>% 
  mutate(h_offset = mean(h_pixc - height, na.rm = TRUE),
         h_adj = h_pixc - h_offset)
  

head(valdf)

plot(height ~ h_adj, valdf, xlim = c(0, 50)); abline(0, 1)
```


```{r}
valdf %>% 
  glimpse() %>% 
  mutate(sqrresid = (h_adj - height)^2) %>% 
  plot(sqrt(sqrresid) ~ sqrt(h_var_node), ., log = "xy")
```


No apparent signal there. Can I show variance changing with position in cross-track?

```{r}

valdf_full <- pixc_sf %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  sample_n(1000) %>% 
  rename(h_pixc = height) %>% 
  left_join(sac_node_truth_df, by = "nodeid", st_join = FALSE) %>% 
  mutate(h_offset = mean(h_pixc - height, na.rm = TRUE),
         h_adj = h_pixc - h_offset)
  
valdf_full %>% 
  glimpse() %>% 
  mutate(resid = h_adj - height) %>% 
  # ggplot(aes(x = h_var_pix, y = resid^2)) + 
  ggplot(aes(x = dhdphi^2, y = resid^2)) + 
  geom_point() +
  scale_x_log10() +
  scale_y_log10()

```

Time to put this into a script and do a proper set of analysis and presentation. 

- Math (from Brent's document, email correspondence)
- maps (static and interactive)
    - height
    - Node aggregation (couple of nodes, sample of pixels for all nodes)
    - 
- Pixel-scale residuals
    - with estimated variance
    - with cross-track position
    - with dh/dphi
- Node-scale residuals
