---
title: "notebook20190816"
author: "Mark Hagemann"
date: "8/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm still investigating node-level errors using pixel-level visualizations. 

I think it would be useful to have a function to generate plots as I've done the past coupld of days. Inputs: joined pixel cloud, nodes, buffer, scale or not, real area or not. 

```{r}

library(ggforce)
#' convert meters to lat/lon distance, approximately
to_latlon <- function(x, lat, lon) {
  lon_m <- cos(lat * pi / 180) * 110567
  lat_m <- 111000 # approximately
  out <- x * sqrt(1 / (lat_m * lon_m))
  out
}

#' @param ... passed to \code{geom_point()} or \code{geom_circle()}
map_node_pixc <- function(pixdf, 
                          nodes, 
                          gdemdf = NULL,
                          buffer = 5, scale = FALSE, 
                          real_area = FALSE, 
                          gdsize = 0.5, pixcsize = 5 * gdsize,
                          ...) {
    
  pixdf <- pixdf %>% 
    filter(node_index %in% (nodes + -buffer:buffer)) %>% 
    mutate(sizescale = 1,
           classification = as.factor(classification),
           innodes = node_index %in% nodes,
           alpha = ifelse(innodes, 0.75, 0.3),
           radius_m = sqrt(pixel_area / pi),
           radius_ll = to_latlon(radius_m, 
                                 latitude_vectorproc, 
                                 longitude_vectorproc))
  
  if (scale) {
    pixdf <- pixdf %>% 
      mutate(sizescale = water_frac,
             radius_ll = radius_ll * water_frac)
  }
  
  if (!is.null(gdemdf)) {
    gdemdf <- gdemdf %>% 
      filter(node_index %in% (nodes + -buffer:buffer)) %>% 
      mutate(innodes = node_index %in% nodes,
             alpha = ifelse(innodes, 1, 0.3),
             radius_m = sqrt(pixel_area / pi),
             radius_ll = to_latlon(radius_m, latitude, longitude))
  }
    
  # Calculate actual pixel sizes, if directed to.
  if (real_area) {
    # convert pixel area to radius in meters, then to lat/lon
    pixradius_m <- sqrt(pixdf$pixel_area / pi)
    gdradius_m <- sqrt(gdemdf$pixel_area / pi)
    
    pixdf <- pixdf %>% 
      mutate(radius_ll = to_latlon(pixradius_m, 
                                   latitude_vectorproc, 
                                   longitude_vectorproc))
    if (scale) pixdf$radius_ll <- pixdf$radius_ll * pixdf$water_frac
  } 
  

  # Construct ggplot object
  mapgg <- pixdf %>% 
    ggplot()
  
  # add truth, if supplied.
  if (!is.null(gdemdf)) {
    if (real_area) {
      

    } else {

    }
  }
  
  if (real_area) {
    if (!is.null(gdemdf)) {
      mapgg <- mapgg + 
        geom_circle(aes(x0 = longitude, y0 = latitude,
                        r = radius_ll,
                 alpha = alpha),
             fill = "black", n = 6,
             data = gdemdf, size = gdsize, linetype = 0)
    }
    
    
    mapgg <- mapgg + 
      geom_circle(aes(x0 = longitude_vectorproc, y0 = latitude_vectorproc,
                     alpha = alpha, 
                     fill = classification, 
                     r = radius_ll),
                  n = 8, linetype = 0)
  } else { # use points instead of circles
    if (!is.null(gdemdf)) {
      mapgg <- mapgg + 
        geom_point(aes(x = longitude, y = latitude,
             alpha = alpha),
             color = "black",
             data = gdemdf, size = gdsize)
    }
    
    
    mapgg <- mapgg + 
      geom_point(aes(x = longitude_vectorproc, y = latitude_vectorproc,
                     alpha = alpha, 
                     color = classification, 
                     size = pixcsize * sizescale),
                 shape = 20) + 
            scale_size_identity()
    
  }
  
  mapgg <- mapgg + 
    scale_alpha_identity() +
    coord_map()
    
  mapgg
}

pixdf <- join_pixc(rodir(80, "composite"), pixcname = "../pixel_cloud.nc")
gdemdf <- join_pixc(rodir(71, "composite"), pixcname = "../fake_pixc.nc", 
                    pcvname = "pcv_gdem.nc")



map_node_pixc(pixdf, 388, gdemdf, buffer = 2, real_area = TRUE, scale = TRUE) + 
  theme_bw()

```

I'm reasonably happy with that. What to do with it now? Fit into the general workflow--


```{r}
runno %>% 
  rodir() %>% 
  join_pixc() %>% 
  connect_updown %>% 
  run_riverobs()

connected <- us_ds(pixdf, "midstream", verbose = TRUE)

pixdf %>% 
  filter(connected$connected) %>% 
  map_node_pixc(388, buffer = 2, real_area = TRUE, scale = TRUE) + 
  theme_bw()
```

I think my update to `us_ds` works! See if it gives similar results for more interesting cases. 

```{r}
runno <- 82
agg <- "composite"
node <- 68

pixdf <- rodir(runno, agg) %>% 
  join_pixc(pixcname = "../pixel_cloud.nc")

connected1 <- us_ds(pixdf, "midstream", verbose = TRUE)
connected2 <- us_ds(pixdf, "ends", verbose = TRUE)


pixdf %>% 
  map_node_pixc(node, real_area = TRUE, scale = TRUE) + 
  theme_bw()

pixdf %>% 
  filter(connected1$connected) %>% 
  map_node_pixc(node, real_area = TRUE, scale = TRUE) + 
  theme_bw()

pixdf %>% 
  filter(connected2$connected) %>% 
  map_node_pixc(node, real_area = TRUE, scale = TRUE) + 
  theme_bw()
```

Cool! This way I can flag out weird geometry--and quickly. 