---
title: "notebook20190822"
author: "Mark Hagemann"
date: "8/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm taking a little time this morning to make some mapping functions. I want to easily:

- map pixel cloud
- map pixcvec (improved geolocation)
- plot slant plane
- color by classification
- over/underlay truth
- show a range of nodes
- show a box of range/azimuth


Here's a potential workflow.

```{r}
pixcdf %>% 
  grab_nodes(13:22, pcvdf) %>% #or..
  grab_nodebox(13:22, pcvdf, dilate = 10) %>% # slant-plane box, possibly dilated
  pixc_map(colorby = "classification", 
           geoloc = "best",
           real_area = TRUE, 
           water_frac = FALSE) %>%  # or...
  pixc_slantmap(colorby = "classification")
```

Start building these out.

```{r}

#' @param pcvdf a data.frame that includes node and range/azimuth information, 
#'  e.g. as returned by \code{pixcvec_read()}
grab_nodes <- function(pixdf, nodeids, pcvdf = pixdf) {
  radf <- pcvdf %>% 
    filter(node_index %in% nodeids)
  
  out <- pixdf %>% 
    filter((range_index * 1e5 + azimuth_index) %in% 
             (radf$range_index * 1e5 + radf$azimuth_index))
  out
}

grab_nodebox <- function(pixdf, nodeids, pcvdf = pixdf, dilate = 0) {
  radf <- pcvdf %>% 
    filter(node_index %in% nodeids)
  
  minrange <- min(radf$range_index, na.rm = TRUE) - dilate
  maxrange <- max(radf$range_index, na.rm = TRUE) + dilate
  minazimuth <- min(radf$azimuth_index, na.rm = TRUE) - dilate
  maxazimuth <- max(radf$azimuth_index, na.rm = TRUE) + dilate
  
  out <- pixdf %>% 
    filter(range_index >= minrange, range_index <= maxrange, 
           azimuth_index >= minazimuth, azimuth_index <= maxazimuth)
  out
}

pixc_map <- function(pixdf, 
                     colorby = "classification", 
                     geoloc = c("best", "orig", "improved"),
                     real_area = FALSE, 
                     water_frac = FALSE,
                     maxpoints = 2500, ...) {
  
  geoloc <- match.arg(geoloc)
  
  if (nrow(pixdf) > maxpoints) 
    stop(sprintf("Number of pixels (%s) is greater than maxpoints (%s).\n",
                 nrow(pixdf), maxpoints),
         "Please filter pixdf (e.g. grab_nodes()) or increase maxpoints")
  
  # geolocation:
  if (geoloc == "improved" || 
      (geoloc == "best" && !is.null(pixdf$latitude_vectorproc))) {
    pixdf$latitude <- pixdf$latitude_vectorproc
    pixdf$longitude <- pixdf$longitude_vectorproc
  }
  
  # sizing, coloring of points/circles
  pixdf$sizescale <- 1
  if (water_frac)  pixdf$sizescale <- pixdf$water_frac
  pixdf$colorvar <- pixdf[[colorby]]
  
  # Construct ggplot object
  mapgg <- pixdf %>% 
    ggplot()
  
  if (real_area) {
    
    # convert pixel area to radius in meters, then to lat/lon
    pixradius_m <- sqrt(pixdf$pixel_area * pixdf$sizescale / pi)
    gdradius_m <- sqrt(gdemdf$pixel_area / pi)
    
    pixdf$radius_ll <- to_latlon(pixradius_m, pixdf$latitude, pixdf$longitude)
    
    mapgg <- mapgg + 
      geom_circle(aes(x0 = longitude, y0 = latitude,
                    fill = colorvar, 
                    r = radius_ll),
                n = 8, linetype = 0, ...)
  } else { # use points instead of circles
    
    pixcsize = 2.5
    mapgg <- mapgg + 
      geom_point(aes(x = longitude, y = latitude,
                     color = colorvar, 
                     size = pixcsize * sqrt(sizescale)),
                 shape = 20, ...) + 
      scale_size_identity() +
      labs(color = colorby)
  }
    
  mapgg <- mapgg + 
    coord_map()
  mapgg
}


pixc_slantmap <- function(pixdf, 
                     colorby = "classification", 
                     maxpoints = 5000, ...) {
  # coloring of points/circles
  pixdf$colorvar <- pixdf[[colorby]]
  
  # Construct ggplot object
  mapgg <- pixdf %>% 
    ggplot()
  
  pixcsize = 2.5
  mapgg <- mapgg + 
    geom_raster(aes(x = range_index, y = azimuth_index,
                   fill = colorvar), ...) + 
    labs(fill = colorby)

  mapgg
}
```

Try it out!

```{r}
pixdf1 <- pixc_read(rodir(65, "pixel_cloud_new.nc"))
pcvdf1 <- pixcvec_read(rodir(65, "frac", "pcv.nc"))

pixdf1 %>% 
  # grab_nodes(350:360, pcvdf1) %>% 
  grab_nodebox(350:360, pcvdf1) %>% 
  # glimpse() %>%
  mutate(classification = as.factor(classification)) %>% 
  pixc_map(maxpoints = 4000)

pixdf1 %>% 
  # grab_nodes(350:500, pcvdf1) %>%
  grab_nodebox(350:360, pcvdf1) %>%
  # glimpse() %>%
  mutate(classification = as.factor(classification)) %>% 
  pixc_slantmap()

pixdf1 %>% 
  pixc_join(pcvdf1, "outer") %>% 
  grab_nodebox(350:360) %>% 
  pixc_slantmap()
  
```

That appears to work! Not bad for a little time spent. Put this into rivertile, along with a `pixc_pcv()` function that replaces the work of `join_pixc()`. Also, make `classification` a factor by default. 


Good. Now pick up where I left off yesterday.


```{r}
pixdf1 <- rodir(82, "pixel_cloud_new.nc") %>% pixc_read() %>% 
  pixc_join(pixcvec_read(rodir(82, "composite/pcv.nc")), type = "outer")

pixdf1_gdem <- rodir(82, "fake_pixc.nc") %>% pixc_read() %>% 
  pixc_join(pixcvec_read(rodir(82, "composite/pcv_gdem.nc")), type = "outer")
  
pixdf1_gdem2 <- rodir(82, "fake_pixc.nc") %>% pixc_read() %>% 
  pixc_join(pixcvec_read(rodir(82, "pcv_gdem_dil2.nc")), type = "outer")
  

pixdf1 %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-5:5)) %>%
  filter(classification != 1) %>% 
  pixc_map(maxpoints = 10000, geoloc = "orig", colorby = "node_index") +
  coord_map()

pixdf1 %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-2:2)) %>%
  filter(classification != 1) %>% 
  pixc_map(maxpoints = 10000, real_area = TRUE,
           water_frac = TRUE) +
  coord_map() +
  guides(fill = "none")
ggsave("../fig/spatial_reg_figs/node68_1.png", width = 3, height = 4)

pixdf1 %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-2:2)) %>%
  filter(classification != 1) %>% 
  pixc_map(maxpoints = 10000, water_frac = FALSE, 
           size = 2) +
  coord_map() +
  guides(color = "none")
ggsave("../fig/spatial_reg_figs/node68_2.png", width = 3, height = 4)


pixdf1_gdem %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-5:5)) %>%
  pixc_map(maxpoints = 100000, size = 0.1, 
           colorby = "node_index", geoloc = "orig") +
  coord_map()


pixdf1 %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-5:5)) %>%
  pixc_slantmap() +
  guides(fill ="none")
ggsave("../fig/spatial_reg_figs/node68_3.png", width = 3, height = 4)

pixdf1_gdem %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-5:5)) %>%
  pixc_slantmap(colorby = "node_index") +
  guides(fill ="none")
ggsave("../fig/spatial_reg_figs/node68_4.png", width = 3, height = 4)


pixdf1_gdem2 %>% 
  # grab_nodes(68 + (-5:5)) %>%
  grab_nodebox(68 + (-5:5)) %>%
  pixc_slantmap(colorby = "node_index")
```


See where this is. 

```{r}
library(leaflet)
pixdf1 %>% 
  grab_nodes(68) %>% 
  sample_n(10) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers()
  
```

