---
title: "notebook20190212"
author: "Mark Hagemann"
date: "2/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Looking at new dataset from Brent.

```{r}
sacdir <- "D:/data/sac-simulator-output/tile-Sac-11Feb2019/"
list.files(sacdir, recursive = TRUE)

```

Just pick one of these for now and look at how large the object is. 

```{r}
sacrt1 <- rt_read("../output/sac05/rt.nc")

glimpse(sacrt1)

leaflet(sacrt1) %>% 
  addTiles() %>% 
  addCircleMarkers()
```


Try using Renato's layover bias estimates.

```{r}
library(R.matlab)

lyvr1 <- R.matlab::readMat("../data/NA07_grwl_merged_dam_swot_obs.mat")

str(lyvr1[[1]])

lyvr <- setNames(lyvr1[[1]], dimnames(lyvr1[[1]])[[1]])[1:13]
str(lyvr)

head(lyvr$Orbs)
summary(lyvr$Orbs)
```



```{r}
lyvr[c("latitude", "longitude")] %>% 
  as.data.frame() %>% 
  sample_n(10000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, popup = ~paste(latitude, longitude))

bbox <- c(41, -123, 37, -121)

lyvr[c("latitude", "longitude")] %>% 
  as.data.frame() %>% 
  dplyr::filter(latitude < 41, longitude < -121, 
                latitude > 37, longitude > -123) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, popup = ~paste(latitude, longitude))


```


```{r}
lyvrdf <- lyvr %>% 
  as.data.frame() %>% 
  dplyr::filter(latitude < 41, longitude < -121, 
                latitude > 37, longitude > -123)


orbdf <- lyvrdf %>% 
  dplyr::select(latitude, longitude, Orbs.1:Orbs.7) %>% 
  gather(key = "key", value = "orb", -latitude, -longitude) %>% 
  dplyr::select(-key)

hbiasdf <- lyvrdf %>% 
  dplyr::select(latitude, longitude, layheightbias.1:layheightbias.7) %>% 
  gather(key = "key", value = "hbias", -latitude, -longitude) %>% 
  dplyr::select(-key) %>% 
  mutate(orb = orbdf$orb) %>% 
  dplyr::filter(!is.na(hbias))
```


Now I can filter based on the orbits I'm interested in.

- I don't know which one I was using, but it's one of 264, 249, or 527.

```{r}

laymapdf1 <- hbiasdf %>% 
  dplyr::filter(orb == 527, !is.na(hbias))

pal1 <- colorNumeric(palette = c("blue", "red"), domain = laymapdf1$hbias)

laymapdf1 %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(color = ~pal1(hbias))

```


Next item is to match up the lat/lon from my nodes to the layover df lat/lon. 

```{r}
valdata <- rt_valdata(dir = "../output/sac04")

lalo_valdata <- valdata %>% 
  dplyr::filter(variable %in% c("latitude", "longitude")) %>% 
  dplyr::select(node_id, variable, gdem_val) %>% 
  spread(key = variable, value = gdem_val)

herrdf <- valdata %>% 
  dplyr::select(node_id, variable, pixc_err) %>% 
  dplyr::filter(variable == "height") %>% 
  left_join(lalo_valdata, by = "node_id") %>% 
  mutate(longitude = ifelse(longitude > 180, longitude - 360, longitude))
```

I'll just do a nearest neighbor interpolation following [here](https://rspatial.org/analysis/4-interpolation.html)


```{r}
library(dismo)
v <- voronoi(laymapdf1[c("longitude", "latitude")])
plot(v)
v_sf <- st_as_sf(v)

herrgeom <- st_as_sf(herrdf, coords = c("longitude", "latitude"))

foo <- st_within(herrgeom$geometry, v_sf, sparse = FALSE)
apply(foo, 1, which)


```

That doesn't look right. Map it. 

```{r}
unqlocs <- apply(foo, 1, which) %>% unique()

laymapdf1[unqlocs, ] %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers() %>% 
  addCircleMarkers(data = herrdf, color = "red", radius = 3)
```


```{r}
passopts <- c(264, 249, 527)

hbiasdf %>% 
  dplyr::filter(orb == passopts[2]) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers() %>% 
  addCircleMarkers(data = herrdf, color = "red", radius = 3)
```

Conclusion: it must be pass 249

```{r}
library(dismo)

hbias249 <- hbiasdf %>% 
  dplyr::filter(orb == 249) %>% 
  rename(lat_lvr = latitude, lon_lvr = longitude)

v <- hbias249 %>% 
  dplyr::select(lon_lvr, lat_lvr) %>% 
  voronoi()
# plot(v)
v_sf <- st_as_sf(v)

herrgeom <- st_as_sf(herrdf, coords = c("longitude", "latitude"))

foo <- st_within(herrgeom$geometry, v_sf, sparse = FALSE)
joinrows <- apply(foo, 1, which)


herr_join <- cbind(herrdf, hbias249[joinrows, ])

plot(pixc_err ~ hbias, herr_join, xlab = "predicted layover height bias",
     ylab = "observed height error"); abline(0, 1)
summary(lm(pixc_err ~ 0 + hbias, herr_join))
```

Bin the hbias for a boxplot. 

```{r}
bins <- cut(herr_join$hbias, breaks = c(0, 0.1, 0.2, 0.31))

herr_join$hbias_bin <- bins

boxplot(pixc_err ~ hbias_bin, herr_join, 
        xlab = "binned layover bias estimate", 
        ylab = "observed height error"); abline(h = 0.13, lty = 2)

```


