---
title: "notebook20190206"
author: "Mark Hagemann"
date: "2/4/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(ncdf4)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)

opts_chunk$set(echo = TRUE)

splitPiece <- function (strvec, split, piece, ...) {
  spl <- strsplit(strvec, split = split, ...)
  out <- vapply(spl, `[`, character(1), piece)
  out
}


```


This is modified from a copy-paste of 20190204 notebook. The difference is that I've regenerated the output using fixed (?) uncertainty aggregation. 

```{r}
ncdir = "../output/sac01"
```


Fine. Next, do nodes. 

```{r}
sac_rt <- nc_open(sprintf("%s/rt.nc", ncdir)) # rivertile netcdf from Sac Pixc

# sac_rt$groups[[3]]
# sac_rt$dim$`reaches/reaches`

sacvars <- names(sac_rt$var)
# sacvars
nodevars <- sacvars[grepl("^nodes/", sacvars)]

nodevars_short <- splitPiece(nodevars, "/", 2, fixed = TRUE)

nodevals_list <- nodevars %>% 
  map(~as.vector(ncvar_get(nc = sac_rt, varid = .))) %>% 
  setNames(nodevars_short)


nacols <- map_lgl(nodevals_list, ~(sum(!is.na(.)) == 0))

nodevals_df <- as.data.frame(nodevals_list)[, !nacols]

nc_close(sac_rt)
```

Next get a truth for node level

```{r}
sac_rt <- nc_open(sprintf("%s/rt_gdem.nc", ncdir)) # rivertile netcdf from Sac gdem

sacvars <- names(sac_rt$var)
# sacvars
nodevars <- sacvars[grepl("^nodes/", sacvars)]

nodevars_short <- splitPiece(nodevars, "/", 2, fixed = TRUE)

nodetruth_list <- nodevars %>% 
  map(~as.vector(ncvar_get(nc = sac_rt, varid = .))) %>% 
  setNames(nodevars_short)


nacols <- map_lgl(nodetruth_list, ~(sum(!is.na(.)) == 0))

nodetruth_df <- as.data.frame(nodetruth_list)[, !nacols]

nc_close(sac_rt)
```


Next do that comparison. What variables do I want?

```{r}

keepvars <- c("node_id", "time", "latitude", "longitude", 
              "latitude_u", "longitud_u", "height", "height_u", 
              "width", "width_u", "area_detct", "area_det_u", 
              "area_total", "area_tot_u", "area_of_ht", "n_good_pix")

# This one just for truth comparison (i.e. vars to validate)
keepvars_tru <- c("node_id", "time", "latitude", "longitude", 
              "height", "width", "area_detct", "area_total", "area_of_ht")
```



```{r}
node_df <- nodevals_df[keepvars] %>% 
  mutate(time = round(time, digits = -3)) %>% 
  full_join(mutate(nodetruth_df[keepvars_tru], 
                   time = round(time, digits = -3)),
            by = c("node_id", "time"))
```


I'd love a plot of errors versus sensitivity, but I don't have sensitivity at feature scale. For now think about how to do error comparison more systematically. Start with a better data structure:

```{r}
errdf_node <- node_df %>% 
  transmute(node_id, time,
            h = (height.x - height.y),
            w = width.x - width.y,
            adet = area_detct.x - area_detct.y,
            atot = area_total.x - area_total.y,
            lat = latitude.x - latitude.y,
            lon = longitude.x - longitude.y)

uncdf_node <- node_df %>% 
  transmute(node_id, time,
            h = height_u,
            w = width_u,
            adet = area_det_u,
            atot = area_tot_u,
            lat = latitude_u,
            lon = longitud_u)

relerrdf_node <- (errdf_node / uncdf_node) %>% 
  mutate(node_id = errdf_node$node_id,
         time = errdf_node$time) %>% 
  gather(key = "variable", value = "value", -node_id, -time)

```


Now I can quickly plot:

```{r}
relerrdf_node %>% 
  filter(abs(value) < 100) %>% 
  ggplot(aes(x = value)) + 
  geom_histogram() + 
  facet_wrap(~variable, scales = "free")
```

I like that. I think it's a good first-level plot. I can think of things to parse out from this and compare, but leave that for now. Actually, real quick, add a non-rleative error plot. 

```{r}
errdf_node %>% 
  gather(key = "variable", value = "value", -node_id, -time) %>%
  # glimpse() %>% 
  ggplot(aes(x = value)) + 
  geom_histogram() + 
  facet_wrap(~variable, scales = "free")
  
```


Now I'll work on some standalone Rmd documents for different facets of error validation. Start with maps. 