---
title: "notebook20190109"
author: "Mark Hagemann"
date: "January 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Time to get R and Python to join forces. I'll try using `reticulate` for that. 

```{r}
library(reticulate)

use_condaenv("RiverObs", required = TRUE)
```

That appears to have worked. Now how do I use python commands?

```{r}
source_python("../src/imports.py")
pygdal <- import("osgeo")
```

Now that that works (after updating reticulate), see if I can flat-out run the script.

```{r}
source_python("../src/7SAC_264_l2_newfields.py")
```

It works!

Now back to the previous task: inspecting Brent's sample uncertainty file.

- Map the heights
- Map the estimated uncertainty
- Calculate empirical uncertainty

```{r}
ncfile <- "../../riverobs-data/uncertainty_example/pixel_cloud.nc"

ncobj <- nc_open(ncfile)
names(ncobj$var)

nc_close(ncobj)
```

How about a function to plot from an open pixc netcdf file?

```{r}


pixc_map <- function(ncobj, vars, subset = 500, 
                     prefix = "pixel_cloud/", plot = TRUE) {
  lats <- ncvar_get(ncobj, "pixel_cloud/latitude")
  len <- attr(lats, "dim")
  keepinds <- sort(sample(1:len, size = min(len, subset)))
  
  lats <- as.vector(lats[keepinds])
  lons <- as.vector(ncvar_get(ncobj, "pixel_cloud/longitude")[keepinds])
  vars <- as.vector(ncvar_get(ncobj, paste0(prefix, varname))[keepinds])
  
  plotdf <- setNames(data.frame(lat = lats, lon = lons, var = vars),
                     c("lat", "lon", varname))
  if (!plot) return(plotdf)
  
  pal <- colorNumeric(palette = "YlOrRd", domain = vars)
  out <- leaflet(plotdf) %>% 
    addTiles() %>% 
    addCircleMarkers(lng = ~lon, lat = ~lat, color = ~pal(plotdf[[varname]]))
  out
}
```


What about the river "rivers..." shapefile?

```{r}
rivers_sf <- st_read("../../riverobs-data/uncertainty_example/rivers-10x250-0-tiny-normal.shp")

glimpse(rivers_sf)

library(leaflet)

leaflet(rivers_sf) %>% 
  addTiles() %>% 
  addPolylines()
```

I wonder why he made them parallel...

Now let's get a look at that pixel cloud. 

```{r}
pixcnc <- nc_open("../../riverobs-data/uncertainty_example/pixel_cloud.nc")
pixcvars <- names(pixcnc$var)
pixcvars

getvars <- c("latitude", "longitude", "height")

pixclist <- getvars %>% 
  map(~paste0("pixel_cloud/", .)) %>% 
  map(~ncvar_get(nc = pixcnc, varid = .)) %>% 
  setNames(getvars)

pixcdf <- as.data.frame(pixclist) %>% 
  na.omit() %>% 
  mutate(longitude = longitude - 360) %>% 
  st_as_sf(coords = c("longitude", "latitude"))

nc_close(pixcnc)
```

Make it talk.

```{r}
glimpse(pixcdf)

pixcdf_sset <- pixcdf %>% 
  sample_n(500)

 
leaflet() %>% 
  addTiles() %>%
  addCircleMarkers(radius = 1, data = pixcdf_sset) %>%
  addPolylines(color = "red", data = rivers_sf)

map1 %>% 
  addCircleMarkers(radius = 1, data = pixcdf_sset)
```

Next I should play around with Brent's new files for aggregating. This is a good opportunity to use reticulate. 

```{r}
swat <- import("SWOTRiver")
py_help("simple")
```

