---
title: "notebook20190710"
author: "Mark Hagemann"
date: "7/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I discovered this morning a probable error in water fraction uncertainty calculation. It's easy to fix--I just need to multiply the 1-sigma uncertainty by $\sqrt{N_l^3 (N_l -1 )^{-2}(N_l - 1)^{-1}}$. For me ($N_l = 7$) that comes out to 1.3804. 

I'll bring this up with Brent, but first I'm going to try patching the pixel cloud and rerunning through riverobs. See how that affects the validation.

```{r}
file.copy("../output/area-error/pixel_cloud.nc", 
          "../output/area-error/pixel_cloud_fixed.nc")
new_pixc <- nc_open("../output/area-error/pixel_cloud_fixed.nc", write = TRUE)
wfrac_unc <- ncvar_get(new_pixc, "pixel_cloud/water_frac_uncert")
new_wfrac_unc <- wfrac_unc * 1.3804

ncvar_put(new_pixc, "pixel_cloud/water_frac_uncert", new_wfrac_unc)
nc_close(new_pixc)

pixc_old <- pixc_read("../output/area-error/pixel_cloud.nc")
pixc_new <- pixc_read("../output/area-error/pixel_cloud_fixed.nc")

toplot <- sample(1:nrow(pixc_old), 200)
plot(pixc_old$water_frac_uncert[toplot], pixc_new$water_frac_uncert[toplot]); abline(0, 1)

```

Good, now rerun riverobs.

Here are the results I get. Some improvement--I'll need to quantify this. 

```{r}
val_simple <- rt_valdata("../output/area-error/simple/", flag_out_nodes = FALSE)
val_composite <- rt_valdata("../output/area-error/composite/", flag_out_nodes = FALSE)

val_composite_fixed <- rt_valdata("../output/area-error/composite_fixed/", 
                                  flag_out_nodes = FALSE)

val_composite %>% 
  dplyr::filter(variable == "area_total") %>%
  mutate(scaled_error = pixc_err / sigma_est, 
         theoretical = qqnorm(scaled_error, plot.it = FALSE)$x) %>% 
  ggplot(aes(x = theoretical, y = scaled_error)) + 
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  xlim(-3.5, 3.5) + ylim(-10, 15)
  

# ggsave("../fig/area-error-composite.png")

val_composite_fixed %>% 
  dplyr::filter(variable == "area_total") %>%
  mutate(scaled_error = pixc_err / sigma_est, 
         theoretical = qqnorm(scaled_error, plot.it = FALSE)$x) %>% 
  ggplot(aes(x = theoretical, y = scaled_error)) + 
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  xlim(-3.5, 3.5) + ylim(-10, 15)

val_composite_fixed %>% 
  rt_val_hist(scale = TRUE, curve = TRUE, vars = "area_total") + 
  xlim(-13, 15) + ylim(0, 0.42)
val_composite %>% 
  rt_val_hist(scale = TRUE, curve = TRUE, vars = "area_total") +
  xlim(-13, 15) + ylim(0, 0.42)

```

Put this into a report and send to Brent.


