---
title: "notebook20190221"
author: "Mark Hagemann"
date: "2/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Look at dilation results, simultaneously improve stuff over in rivertile. 

- How about start with something that gets the worst nodes and plots them on a map
- Should also take an explicit subset of nodes. 
- OK, DONE. 

Next see about that dilation.

- Join non-dilation to dilation cases, see where largest disagreement occurs. 
    - old rt, old gdem rt
    - old rt, dilated gdem rt
    - dilated rt, dilated gdem rt
- plot histograms, worst-node maps

```{r}
dir15 <- "../output/sac15"

val1 <- rt_val_hist(dir15, vars = c("width", "height"))
val1
val2 <- rt_val_hist(dir15, vars = c("height", "width"), gdname = "rt_gdem_dil.nc")
val2

val3 <- rt_val_hist(dir15, vars = c("height", "width"), 
                    rtname = "rt_dil.nc", gdname = "rt_gdem_dil.nc")
val3
```

Look at the peskiest nodes. 

```{r}
plotnodes <- badnodes(rt_valdata(dir15))
```

```{r}
library(leaflet)
val_map_node(dir15, nodes = plotnodes[c(1, 3)])
val_map_node(dir15, nodes = plotnodes[c(1, 3)], pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil.nc")

```

So that didn't really do much. Try using a larger number of iterations. 


```{r}
val_map_node(dir15, nodes = plotnodes[c(1, 3)])
val_map_node(dir15, nodes = plotnodes[c(1, 3)], pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil1.nc")
val_map_node(dir15, nodes = plotnodes[c(1, 3)], pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil2.nc")

```


```{r}
val1 <- rt_val_hist(dir15, vars = c("width"))
val1

val2 <- rt_val_hist(dir15, vars = c("width"), gdname = "rt_gdem_dil1.nc")
val2

val3 <- rt_val_hist(dir15, vars = c("width"), gdname = "rt_gdem_dil2.nc")
val3
```



```{r}
valdata1 <- rt_valdata(dir15)
valdata2 <- rt_valdata(dir15, gdname = "rt_gdem_dil1.nc")
valdata3 <- rt_valdata(dir15, gdname = "rt_gdem_dil2.nc")
valdata4 <- rt_valdata(dir15, rtname = "rt_dil.nc", gdname = "rt_gdem_dil2.nc")


val_map_node(dir15, nodes = badnodes(valdata1))
val_map_node(dir15, nodes = badnodes(valdata2), 
             pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil1.nc")
val_map_node(dir15, nodes = badnodes(valdata3), 
             pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil2.nc")
val_map_node(dir15, nodes = badnodes(valdata4), 
             pcv1 = "pcv_dil.nc", pcv2 = "pcv_gdem_dil2.nc")
```

```{r}
val1 <- rt_val_hist(dir15, vars = c("width"))
val1

val2 <- rt_val_hist(dir15, vars = c("width"), gdname = "rt_gdem_dil1.nc")
val2

val3 <- rt_val_hist(dir15, vars = c("width"), gdname = "rt_gdem_dil2.nc")
val3

val4 <- rt_val_hist(dir15, vars = c("width"), 
                    rtname = "rt_dil.nc", gdname = "rt_gdem_dil1.nc")
val4

val4 <- rt_val_hist(dir15, vars = c("width"), 
                    rtname = "rt_dil.nc", gdname = "rt_gdem_dil2.nc")
val4
```


