---
title: "notebook20190429"
author: "Mark Hagemann"
date: "4/29/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

What's going on with height errors in near swath?

- I need a utility function for generating validation data from multiple runs, including metadata from manifest(s)

```{r}

rt_valdata_multi <- function(runnos, manifest = ro_manifest(),
                             basedir = getOption("ro_basedir")) {
  valdfs <- purrr::map(runnos, ~rt_valdata(rodir(., manifest = manifest)),
                       basedir = basedir) %>% 
    setNames(runnos)
  out <- bind_rows(valdfs, .id = "run") %>% 
    mutate(run = as.numeric(run)) %>% 
    left_join(manifest, by = c(run = "outno"))
  out
}
  
```


OK! That appears to work. Move it into lib/roruns.R. DONE. 


Now I can inspect near-swath height errors. 

First, are pixc locations being appropriately distributed in the case where gdem is split into left and right swaths? Answer: yes. The pixc's are split across left and right swaths as well. 

```{r}
mfest <- ro_manifest()
unique(mfest$pass)

mfest %>% 
  filter(pass == 264) %>%
  group_by(indir, gdem_name, priordb) %>% 
  summarize(n = n()) %>% 
  ungroup() #%>% 
  # select(-indir)
  glimpse()
  
mfest %>% 
  filter(indir == indir[1])

```

```{r}
mfest %>% 
  filter(pass == 264) %>% glimpse()

```

So the left swath is only there for the 10-m reference dem. OK.

Start with the 10-m ref dem case, improved prior loc. That means runs 52 and 53. 

```{r}

# valdf264 <- rt_valdata_multi(c(52, 53))
valdf264 <- rt_valdata_multi(c(57, 58))

valdf264 %>% 
  rt_val_scatter(variables = c("height", "height2"), 
                 xvar = "xtrk_dist", yvar = "relerr")
                 # xvar = "sigma_est", yvar = "relerr")
```

And the answer is... underwhelming! The 3m and 5m runs just don't hold up. Is that true in general? To answer that I'd need a massive validation data frame incorporating a lot of runs.

```{r}
ronums <- romatch(57, vary = c("day", "pass", "gdem_name", "refdem_res", "refdem")) %>% 
  c(57, .)

valdf_big <- rt_valdata_multi(ronums)

valdf_big %>% 
  filter(variable %in% c("height", "height2")) %>% 
  mutate(relerr = pixc_err / sigma_est) %>% 
  ggplot(aes(x = refdem_res, y = relerr, color = as.factor(pass))) +
  geom_boxplot() +
  facet_wrap(~variable)
```

The problem appears to be only with pass 264.

Good, question answered. 
