---
title: "notebook20190514"
author: "Mark Hagemann"
date: "5/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Yesterday I added shapefiles and improved geolocation to my riverobs run script. Today I'll try the more difficult task of putting the slough detector on-line. 


Some parameters will (eventually) need to be sorted out. 

- Search window size
    - Start with 2 pixels for now
- Where and how frequently to restart the upstream and downstream searches
    - Start with up/downstream-most nodes
- How to classify flagged pixels?
    - Give them a class number, 9 maybe? 
    
    
Best to do this in my own git branch of RiverObs. Make that now. 

Workflow will be pretty janky (again, for now). 

1. Run RiverObs as usual
2. Make copies of input pixel_cloud.nc, fake_pixc.nc
3. Run `us_ds` on pcv.nc, pcv_gdem.nc
4. Modify copied pixel clouds (`classification[usds$connected] = 9`)
5. Rerun RiverObs using new pixel clouds. 


```{r}
testpcv <- pixcvec_read("../output/sac18/pcv.nc")
testflag1 <- us_ds(testpcv, verbose = TRUE)
testflag2 <- us_ds(pixcvec_read("../output/sac18/pcv_gdem.nc"), verbose = TRUE)

str(testflag2, 1)

```

Since I've already done the regular riverobs runs (and have a decent script to do so), what if I have this flagging and rerunning work assuming regular runs have been done and are stored according to my folder structuring?

```{r}

dir <- "../output/sac18"

flagclass <- 9L

flag_sloughs <- function(dir, pixcflag = 9L,
                         gdemflag = 0L) {
  
  # create files to contain new classification
  file.copy(paste0(dir, "/pixel_cloud.nc"), 
            paste0(dir, "/pixel_cloud_flagged.nc"), overwrite = TRUE)
  file.copy(paste0(dir, "/fake_pixc.nc"), 
            paste0(dir, "/pixc_gdem_flagged.nc"), overwrite = TRUE)
  
  # connect pixels
  message("Connecting pixel cloud")
  pixccon <- us_ds(pixcvec_read(paste0(dir, "/pcv.nc")))
  message("Connecting gdem pixel cloud")
  gdemcon <- us_ds(pixcvec_read(paste0(dir, "/pcv_gdem.nc")))
  message("Connected.")
  
  # Match connections to pixel cloud by range, azimuth
  pixcnc <- nc_open(paste0(dir, "/pixel_cloud_flagged.nc"), write = TRUE)
  # on.exit(nc_close(pixcnc))
  
  pixcclass <- ncvar_get(pixcnc, "pixel_cloud/classification")
  pixcclass_out <- rep(pixcflag, length(pixcclass))
  pixcrange <- ncvar_get(pixcnc, "pixel_cloud/range_index")
  pixcazim <- ncvar_get(pixcnc, "pixel_cloud/azimuth_index")
  pixcrangeazim <- pixcrange * 1e6 + pixcazim
  
  flagrangeazim <- with(pixccon[pixccon$connected, ], 
                        range_index * 1e6 + azimuth_index)
  flaginds <- match(flagrangeazim, pixcrangeazim)
  
  # Assign to classification
  pixcclass_out[flaginds] <- pixcclass[flaginds]
  ncvar_put(pixcnc, varid = "pixel_cloud/classification", pixcclass_out)    
  nc_close(pixcnc)
  
  # Now gdem fake pixel cloud
  gdemnc <- nc_open(paste0(dir, "/pixc_gdem_flagged.nc"), write = TRUE)
  # on.exit(nc_close(gdemnc))
  
  gdemclass <- ncvar_get(gdemnc, "pixel_cloud/classification")
  gdemclass_out <- rep(gdemflag, length(gdemclass))
  gdemrange <- ncvar_get(gdemnc, "pixel_cloud/range_index")
  gdemazim <- ncvar_get(gdemnc, "pixel_cloud/azimuth_index")
  gdemrangeazim <- gdemrange * 1e6 + gdemazim
  
  flagrangeazim <- with(gdemcon[gdemcon$connected, ], 
                        range_index * 1e6 + azimuth_index)
  flaginds <- match(flagrangeazim, gdemrangeazim)

  # Assign to classification
  # browser()
  gdemclass_out[flaginds] <- gdemclass[flaginds]
  ncvar_put(gdemnc, varid = "pixel_cloud/classification", gdemclass_out)
  nc_close(gdemnc)

}


flag_sloughs("../output/sac18_improved")
flag_sloughs("../output/sac18")

```

```{r}
join_pixc("../output/sac18_improved", pcvname = "pcv.nc", 
          pixcname = "pixel_cloud_flagged.nc") %>% 
  filter(reach_index == 4) %>% 
  mutate(classification = as.factor(classification)) %>% 
  # glimpse() %>% 
  ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc)) + 
  geom_point(aes(color = classification), size = 0.2)
```




Now I need to make a flag_sloughs script. 


```{bash}

# copy files
cp pixel_cloud.nc pixel_cloud_flagged.nc
cp pixc_gdem.nc pixc_gdem_flagged.nc

# flag sloughs using R


# Recreate riverobs outputs
python $ROBIN/swot_pixc2rivertile.py pixel_cloud_flagged.nc rt_flagged.nc pcv_flagged.nc ../../config/config_newprior.rdf

python $ROBIN/swot_pixc2rivertile.py pixc_gdem_flagged.nc rt_gdem_flagged.nc pcv_gdem_flagged.nc ../../config/config_newprior_gdem.rdf

```

Do a quick validation. 

```{r}
valdf1 <- rt_valdata("../output/sac18", flag_out_nodes = FALSE)
valdf2 <- rt_valdata("../output/sac18", rtname = "rt_flagged.nc", 
                     gdname = "rt_gdem_flagged.nc", flag_out_nodes = FALSE)

rt_val_hist(valdf1, vars = c("area_total")) + xlim(-10000, 100000)
rt_val_hist(valdf2, vars = c("area_total")) + xlim(-10000, 100000)

rt_val_hist(valdf1, vars = c("area_total"), scale = TRUE) +
  xlim(-20, 20)
rt_val_hist(valdf2, vars = c("area_total"), scale = TRUE) +
  xlim(-20, 20)

valdf1 %>% 
  group_by(variable) %>% 
  summarize(mean = mean(pixc_err / sigma_est), 
            sd = sd(pixc_err / sigma_est))

valdf2 %>% 
  group_by(variable) %>% 
  summarize(mean = mean(pixc_err / sigma_est), 
            sd = sd(pixc_err / sigma_est))


```

```{r}
nodes18 <- badnodes(rt_valdata("../output/sac18", rtname = "rt_flagged.nc", 
                    gdname = "rt_gdem_flagged.nc", flag_out_nodes = FALSE))

joinpix_flagged <- join_pixc("../output/sac18", pcvname = "pcv_flagged.nc", 
                             pixcname = "pixel_cloud_flagged.nc")

nodearea_plot(joinpix_flagged, nodes = nodes18, 
              node_truth = rt_read("../output/sac18/rt_gdem_flagged.nc"))


val_map_node("../output/sac18", pcv1 = "pcv_flagged.nc", 
             nodes = 329,
             pcv2 = "pcv_gdem_flagged.nc", pixc1 = "pixel_cloud_flagged.nc", 
             pixc2 = "pixc_gdem_flagged.nc", maxpixels = 4000)
```

That doesn't look right. 

```{r}
gdempcv <- join_pixc("../output/sac18", pcvname = "pcv_gdem.nc", 
                     pixcname = "fake_pixc.nc")

foo <- us_ds(gdempcv, verbose = TRUE)

gdempcv$connected <- foo$connected

gdempcv %>% 
  filter(node_index == 329) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircles(radius = 5, stroke = FALSE, fillOpacity = 0.8)
```

```{r}
gdpix1 <- pixc_read("../output/sac18/pixc_gdem_flagged.nc")
gdpix2 <- pixcvec_read("../output/sac18/pcv_gdem_flagged.nc") %>% 
  # filter(node_index > 329)
  filter()

gdpix <- left_join(gdpix1, gdpix2, by = c("range_index", "azimuth_index"))

glimpse(gdpix)

gdpix %>% 
  ggplot(aes(x = longitude, y = latitude)) + 
  geom_point(aes(color = classification), size = 0.01)
ggsave(width = 12, height = 12, filename = "bigpix.png", dpi = 600)

gdpix1 %>% 
  filter(classification == 0) %>%
  # glimpse() %>% 
  ggplot(aes(x = longitude, y = latitude)) + 
  geom_point(aes(color = classification), size = 0.2)

```


```{r}
gdpixnc <- "../output/sac18/pixc_gdem_flagged.nc" %>% 
  nc_open()

lats <- ncvar_get(gdpixnc, "pixel_cloud/latitude")
latinds <- which(lats > 39.374 & lats < 39.380)

classes <- ncvar_get(gdpixnc, "pixel_cloud/classification")[latinds]

```


OK, I've got it fixed. (Remember, the pixcvec has fewer points than the pixel cloud so it matters how you join from one to the other.) Still doesn't lead to better overall validation, but it deals better with outliers, and bias is lower. Except when scaled. Put the flag function into lib/ and move on. 
