---
title: "notebook201905230"
author: "Mark Hagemann"
date: "5/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today I'm going to try to map the tiles given the very minimal information I have about them. 

First work with the 2 passes (one orbit) data.frame I have. Write a function to get coordinates for the corners of a tile given a single lat/lon and heading. Possibly 2 lat/lon points, if I include the adjacent tile.

Last time I worked on this was in 20190522.

```{r}
tiles <- readr::read_delim("../data/tiles/tile-database-2018.txt", 
                           delim = " ",
                           col_types = "iinnn") %>% 
  setNames(c("pass", "tile", "latitude", "longitude", "heading"))

nadir1mat <- as.matrix(tiles[c("longitude", "latitude")])
nadir2mat <- rbind(nadir1mat[-1, ], c(NA, NA))

tiles %>% 
  ggplot(aes(x = longitude, y = latitude)) +
  geom_point(aes(color = pass))

head(tiles)
```


```{r}
tilesrow <- c(22, 24)
nadir1 <- nadir1mat[tilesrow, ]
nadir2 <- nadir2mat[tilesrow, ]
heading <- with(tiles[tilesrow, ], heading)
xtstart <- 4000
xtend <- 64000
atend <- 64000
half <- "L"

getTileCorners <- function(nadir1, nadir2, heading, xtstart = 4000, 
                           xtend = 64000, half = c("L", "R")) {
  half <- match.arg(half)
  
  xtdir <- heading + ifelse(half == "L", 90, -90)
  xtdir <- ifelse(abs(xtdir) > 180, xtdir - 360, xtdir)
  
  
  points1 <- geosphere::destPoint(nadir1, b = xtdir, d = c(xtstart, xtend))
  points2 <- geosphere::destPoint(nadir2, b = xtdir, d = c(xtstart, xtend))
  
  out <- rbind(points1, points2[2:1, ], points1[1, ])
  out
}

corner2sf <- function(cornermat) {
  cornersf <- st_as_sf(cornermat[c(1, 2, 4, 3, 1), ], 
                       coords = c("lon", "lat"),
                       crs = "+proj=longlat +datum=WGS84")
  out <- st_polygon(cornersf)
  out
}

#' Get tiles as spatial frames POLYGON sfc
#' 
#' @param nadir1,nadir2 Either a length-2 vector or a 2-column matrix giving lon, lat
getTilePolygons <- function(nadir1, nadir2, heading, xtstart = 4000, 
                            xtend = 64000, half = c("L", "R")) {
  splitfun <- function(x) {
    if (is.numeric(x) && is.vector(x)) {
      stopifnot(length(x) == 2)
      x <- matrix(x, ncol = 2)
    }
    out <- split(x, f = 1:nrow(x))
  }
  nadir1 <- splitfun(nadir1)
  nadir2 <- splitfun(nadir2)
  stopifnot(length(nadir1) == length(nadir2))
  
  inputlist <- list(nadir1 = nadir1, nadir2 = nadir2, heading = heading)
  
  cornermats <- purrr::pmap(inputlist, getTileCorners, xtstart = xtstart, 
                         xtend = xtend, half = half)
  out <- st_polygon(cornermats)
  out
}


```

Not sure why it isn't working. Here's a stripped-down `sf:::plot.sfc_POLYGON:

```{r}
x <- tilesfc[[1]]

# Begin stripped-down function:
plot_sf(x)
lapply(seq_along(x), function(i) polypath(sf:::p_bind(x[[i]])))

plot_pgon <- function(x) {
  plot_sf(x)
  pbinds <- lapply(x, sf:::p_bind)
  lapply(seq_along(x), function(i) polypath(sf:::p_bind(x[[i]])))
  invisible(NULL)
}

plot_pgon(x)
plot_pgon(tilesfc)

```

Compare using nc data:

```{r}
nc = st_read(system.file("shape/nc.shp", package="sf"), quiet = TRUE)
plot_pgon(nc$geometry[[1]])
```

For some reason sf:::p_bind isn't doing its job.

```{r}
sf:::p_bind

sf:::p_bind(x)
```

Duh, I was using kilometers but should've used meters. Plots were too small!

```{r}
pgons <- getTilePolygons(nadir1mat[1:100, ], nadir2mat[1:100, ], tiles$heading[1:100])
pgons_sf <- tiles[1:100, ] %>% mutate(geometry = st_sfc(pgons)) %>% 
  st_sf(sf_column_name = "geometry", crs = "+proj=longlat +datum=WGS84")

pgons_sf[1:10, ] %>% 
  ggplot() + geom_sf()


leaflet(pgons_sf$geometry[99]) %>% 
  addTiles() %>% 
  addPolygons(color = "red", stroke = TRUE)

getTilePolygons(nadir1mat[270:280, ], nadir2mat[270:280, ], tiles$heading[270:280]) %>% 
  st_sfc(crs = "+proj=longlat +datum=WGS84") %>% 
  # as("spatial") %>% 
  as_Spatial() %>% 
  leaflet() %>% 
  addTiles() %>% 
  addPolygons(fillColor = "red")


```

Time to package this into a function to put in lib/. 


Does it work?

```{r}
with(tiles, getTilePolygons(nadir1 = c(longitude[1], latitude[1]), 
                            nadir2 = c(longitude[2], latitude[2]),
                            heading = heading[1], half = "L")) %>% 
  as_Spatial() %>% 
  leaflet() %>% 
  addTiles %>% 
  addPolygons()
```

```{r}

```

