---
title: "notebook20190423"
author: "Mark Hagemann"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Porting the recursive functions from yesterday into python. 

- Need to deal with different scoping rules for Python
- Start with enumerating the objects needed. 
    - `is_connected` logical vector, mutable 
    - `stream_neighbors` function
    - `rangeinds`, `aziminds`, `along`
    - arrays for `which(nodeinds == 225)`, `which(nodeinds == 210)`
        - adjust these by -1 for python indexing


```{python}
import numpy as np
import sys

sys.setrecursionlimit(100000) # allow for adequately deep recursion

rangeinds = np.array(r.rangeinds)
aziminds = np.array(r.aziminds)
along = np.array(r.along)
startinds_up = np.add(r.startinds_up, -1)
startinds_dn = np.add(r.startinds_dn, -1)

nn = len(rangeinds)
print(nn)
```

```{python}

connected_up = np.zeros(nn, dtype = bool)
connected_dn = np.zeros(nn, dtype = bool)

def connect_upstream(ind):
    if (connected_up[ind]):
        return
    # print("connecting: ", ind)
    connected_up[ind] = True
    for neighbor in stream_neighbors(ind, nnbr = 2, which = "up"):
        # print(neighbor)
        connect_upstream(neighbor)

def connect_downstream(ind):
    if (connected_dn[ind]):
        return
    connected_dn[ind] = True
    for neighbor in stream_neighbors(ind, nnbr = 2, which = "down"):
        connect_downstream(neighbor)



def stream_neighbors(index, nnbr = 2, which = "up"):
  this_range = np.add(rangeinds[index], np.arange(-nnbr, nnbr + 1))
  this_azimuth = np.add(aziminds[index], np.arange(-nnbr, nnbr + 1))
  this_along = along[index]
  neighbormask = np.isin(rangeinds, this_range) & \
                 np.isin(aziminds, this_azimuth)
  submask = along[np.where(neighbormask)[0]] <= this_along
  if which == "down":
    submask = ~submask
  neighbormask[np.where(neighbormask)[0]] = submask
  out = np.where(neighbormask)[0]
  return out
  

for index in startinds_up:
  # print(index)
  connect_upstream(index)
  
for index in startinds_dn:
  # print(index)
  connect_downstream(index)
```


First make sure I can show this for R case. Demonstrate on notorious sluice. DONE!

Now I've got the python recursion going. It takes on the order of a minute, I'd guess. Anyway, optimization is not for me to do. 


Now map it!

```{r}
library(leaflet)
pcvdf <- join_pixc(rodir(18)) %>% 
  # filter(pixc_index %in% pixcinds) %>% 
  arrange(pixc_index)
all_equal(pcvdf$pixc_index, pixcinds)

pcvdf$connected <- py$connected_dn + 2 * py$connected_up


fillpal <- colorFactor(palette = "Set1", domain = pcvdf$connected)
```


```{r}

for (reachind in unique(reachinds)) {
  llmap <- pcvdf %>% 
  mutate(index = pixcinds) %>% 
  # filter(pixc_index %in% pixcinds) %>% 
  filter(reach_index == reachind) %>%
  # filter(node_index %in% 210:225) %>% 
  # filter(is_connected == 1) %>% 
  # glimpse()
  leaflet() %>% 
  addTiles() %>% 
  addCircles(radius = ~sqrt(pixel_area / pi), 
             fillColor = ~fillpal(connected),
             stroke = FALSE, fillOpacity = 0.8, 
             popup = ~sprintf("connected: %s", connected))
             # popup = ~sprintf("reach: %s \nnode: %s", reach_index, node_index))
             # popup = ~sprintf("ind: %s, r: %s \na: %s \ns %02g",
             #                  index, range_index, azimuth_index, along_reach))
  htmlwidgets::saveWidget(llmap, file = sprintf("connected_map_reach%s.html", reachind))
}

```


Can I put this into a function that works on joined pixc? Of course, but no time for that just now. Best to just show:

- each reach of simulator pcv
- a single reach with gdem pcv overlaid

Saving the reach maps was easy. Now make the gdem version (could be tricky and time-consuming.) Here's copied/modified from yesterday:

```{r}
gdempath <- path(rodir(18), "pcv_gdem.nc")
gdemnc <- nc_open(gdempath)

getvar <- function(nc, varid) as.vector(ncvar_get(nc = nc, varid = varid))#, 
                                                  # start = 463, count = 3866))

# slant plane coordinates
rangeinds <- getvar(gdemnc, "range_index")
aziminds <- getvar(gdemnc, "azimuth_index")

# dominant segmentation label mask
seglabs <- getvar(gdemnc, "segmentation_label")
# segmask <- seglabs == Mode(seglabs)

# Along-reach coordinates
reachinds <- getvar(gdemnc, "reach_index")
nodeinds <- getvar(gdemnc, "node_index")
pixcinds <- getvar(gdemnc, "pixc_index")

adjust_along <- function(along, reachinds) {
  along_split <- split(along, reachinds)
  along_rezero <- map(along_split, function(x) x - min(x))
  
  nreaches <- length(along_split)
  shifts <- c(0, map_dbl(along_rezero, max))[1:nreaches] %>% 
    cumsum()
  out <- map2(along_rezero, shifts, function(x, y) x + y) %>% 
    unsplit(reachinds)
  out
}
along <- getvar(gdemnc, "along_reach") %>% 
  adjust_along(nodeinds)

startnode_up <- max(nodeinds) # 225
startnode_dn <- min(nodeinds) # 210
startinds_up <- which(nodeinds == startnode_up)
startinds_dn <- which(nodeinds == startnode_dn)
```

Getting really messy here...




```{python}
import numpy as np
import sys

sys.setrecursionlimit(230000) # allow for adequately deep recursion

rangeinds = np.array(r.rangeinds)
aziminds = np.array(r.aziminds)
along = np.array(r.along)
startinds_up = np.add(r.startinds_up, -1)
startinds_dn = np.add(r.startinds_dn, -1)

nn = len(rangeinds)
print(nn)
```


```{python}
connected_up = np.zeros(nn, dtype = bool)
connected_dn = np.zeros(nn, dtype = bool)

def connect_upstream(ind):
    if (connected_up[ind]):
        return
    # print("connecting: ", ind)
    connected_up[ind] = True
    for neighbor in stream_neighbors(ind, nnbr = 2, which = "up"):
        # print(neighbor)
        connect_upstream(neighbor)

def connect_downstream(ind):
    if (connected_dn[ind]):
        return
    connected_dn[ind] = True
    for neighbor in stream_neighbors(ind, nnbr = 2, which = "down"):
        connect_downstream(neighbor)


def stream_neighbors(index, nnbr = 2, which = "up"):
  this_range = np.add(rangeinds[index], np.arange(-nnbr, nnbr + 1))
  this_azimuth = np.add(aziminds[index], np.arange(-nnbr, nnbr + 1))
  this_along = along[index]
  neighbormask = np.isin(rangeinds, this_range) & \
                 np.isin(aziminds, this_azimuth)
  submask = along[np.where(neighbormask)[0]] <= this_along
  if which == "down":
    submask = ~submask
  neighbormask[np.where(neighbormask)[0]] = submask
  out = np.where(neighbormask)[0]
  return out
  

for index in startinds_up:
  # print(index)
  connect_upstream(index)
  
for index in startinds_dn:
  # print(index)
  connect_downstream(index)
```

Mapping

```{r}
library(leaflet)
gdemdf <- join_pixc(rodir(18), pcvname = "pcv_gdem.nc", pixcname = "fake_pixc.nc") %>% 
  # filter(pixc_index %in% pixcinds) %>% 
  arrange(pixc_index)
all_equal(gdemdf$pixc_index, pixcinds)

gdemdf$connected <- py$connected_dn + 2 * py$connected_up


fillpal <- colorFactor(palette = "Set1", domain = gdemdf$connected)
```


```{r}

for (reachind in 4) {
  llmap <- gdemdf %>% 
  mutate(index = pixcinds) %>% 
  # filter(pixc_index %in% pixcinds) %>% 
  filter(reach_index == reachind) %>%
  # filter(node_index %in% 210:225) %>% 
  # filter(is_connected == 1) %>% 
  # glimpse()
  leaflet() %>% 
  addTiles() %>% 
  addCircles(radius = ~sqrt(pixel_area / pi), 
             fillColor = ~fillpal(connected),
             stroke = FALSE, fillOpacity = 0.8, 
             popup = ~sprintf("connected: %s", connected))
             # popup = ~sprintf("reach: %s \nnode: %s", reach_index, node_index))
             # popup = ~sprintf("ind: %s, r: %s \na: %s \ns %02g",
             #                  index, range_index, azimuth_index, along_reach))
  htmlwidgets::saveWidget(llmap, file = sprintf("connected_map_gdem_reach%s.html", reachind))
}

```
