---
title: "notebook20190802"
author: "Mark Hagemann"
date: "8/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal for today is to compare different approximations of water fraction uncertainty. Here are the candidates.

1. Original: MLE, frequentist uncertainty
2. My update: Gamma with scale-invariant prior on theta
3. Stan model using Uniform(0,1) prior on water fraction
4. Conjugate prior (inverse gamma) approximation of uniform(0, 1)
5. Conjugate prior (inverse gamma) approximation of uniform(0, Inf)
6. (Possibly) MLE with Hessian-derived standard error

Validation can only take place at the node level, and MCMC is out of the question for an entire node (right?), so purpose of stan-modeled estimates is solely to compare the shape of the posterior for alpha with the approximations, at the pixel level. This is not validation, but comparison to a validated model. I could, for instance, see whether water fraction uncertainty at the pixel level is consistently larger or smaller using Stan vs. approximation. 

## Desired result

I want the following:

- Plot overlaying density curves (and MCMC histograms) for a small sample of pixels
- Plot comparing 1-sigma or 95%CI coverage for a larger sample of pixels
- Simulated pixel clouds -> rivertiles -> validation for a subset of above results
  - Whichever best approximates Gamma-uniform(0, 1) case
  

## Preambulary work 

First, get the validation dataset, stan models, and functions to estimate in each case. 

- Function to get relevant observations from pixel cloud, intermediate files
  - random sample of pixels (range, azimuth index)
  - mu_w, mu_l, nefflooks, coh_power
- Function to create `stanfit` object given observations. 
- Function to generate density (a la `dgamma()`) given observations
- Function to generate random sample (a la `rgamma()`) given observations.
- Function to generate a new pixel cloud with updated water_frac and water_frac_uncert fields


Much of this can be ported from existing work: reports/gamma-uniform-bayes.Rmd, 


### Extract relevant data

Function to get specified variables for given range/azimuth index, similar to `intermed2pixc()` function. Actually, that function does just fine. Just tidying up the code here. Also making it take vector arguments. 

```{r}
intermed2pixc <- function(nc_inter, varids, pixcdf) {

  
  varraylist <- lapply(varids, ncvar_get, nc = nc_inter, collapse_degen = FALSE)
  names(varraylist) <- if(is.null(names(varids))) varids else names(varids)
  
  # Check if nc_inter is already subset along range ("num_pixels__") 
  # and/or azimuth ("num_lines__"). If so, revalue the dimnames 
  # of the returned array before melting. 
  rowids <- if (is.null(nc_inter$var[["num_pixels__"]]))
    1:nrow(varraylist[[1]]) else as.vector(ncvar_get(nc_inter, "num_pixels__"))
  colids <- if (is.null(nc_inter$var[["num_lines__"]]))
    1:ncol(varraylist[[1]]) else as.vector(ncvar_get(nc_inter, "num_lines__"))
  
  # Make a joinable data.frame from 1st element in varraylist
  rownames(varraylist[[1]]) <- rowids - 1 # Adjust to match python-based indexing in pixc
  colnames(varraylist[[1]]) <- colids - 1
  
  
  
  vardflist0 <- setNames(reshape2::melt(varraylist[[1]]), 
                         c("range_index", "azimuth_index", 
                           names(varraylist)[1])) %>% 
    mutate(range_index = as.numeric(range_index), 
           azimuth_index = as.numeric(azimuth_index))
  vardf <- vardflist0
  # melt the remaining varraylist elements, cbind to 1st
  if (length(varraylist) > 1) {
    vardflist1 <- lapply(varraylist[-1], function(x) reshape2::melt(x)[[3]])
    vardf <- cbind(vardflist0, 
                       setNames(as.data.frame(vardflist1), 
                                names(varraylist)[-1]))
  }
  
  # join to pixc df and return
  outdf <- inner_join(x = pixcdf, y = vardf, by = c("range_index", "azimuth_index"))
  outdf
}

testdf1 <- intermed2pixc(classnc_ss2, c(cohpow = "coherent_power"), pixcdf)
# testdf1 <- outdf

testdf1 %>% 
  sample_n(100) %>% 
  ggplot(aes(x = coherent_power, y= cohpow)) + geom_point()


```

~~Now a higher-level function to get only mu_w, mu_l, nefflooks, coh_power for a specified, or random, set of pixels.~~ I think I'll just do some simple processing of the output from `intermed2pixc()`--no need to put into a function. 

```{r}
testdir <- rodir(65)

list.files(testdir)
pixcdf <- pixc_read(path(testdir, "pixel_cloud.nc")) %>% 
  sample_n(100)

rangeinds <- pixcdf$range_index + 1
aziminds <- pixcdf$azimuth_index + 1

intermednc <- nc_open(path(testdir, "intermediate_class_maps_0.nc"))
intermed_sset <- nc_subset(intermednc, num_lines %in% rangeinds, 
                           num_pixels %in% aziminds)

testobs_full <- intermed2pixc(intermed_sset, 
                         c(mu_w = "water_power", mu_l = "land_power"),
                         pixcdf = pixcdf)
testobs <- testobs_full %>% 
  transmute(range = range_index, azimuth = azimuth_index,
            coh_power = coherent_power, nefflooks = 4, mu_w, mu_l)

```

### Density and random sample generating functions

```{r}
#' @param x vector of water fractions. 


dwfrac <- function(x, p, mu_w, mu_l, nlooks, 
                   method = c("orig", "igapprox", "iguninf", 
                              "scaleinv", "gamma-unif")) {
  method <- match.arg(method)
  
  x_theta <- (x * (mu_w - mu_l) + mu_l) / nlooks # convert water frac to theta
  
  if (method == "orig") {
    meanwfrac <- (p - mu_l) / (mu_w - mu_l)
    sdwfrac <- p / (mu_w - mu_l) / sqrt(nlooks)
    out <- dnorm(x, mean = meanwfrac, sd = sdwfrac)
  } else if (method == "igapprox") {
    # Uniform prior moments
    wfrachat_prior <- 0.5
    wfracvar_prior <- 1 / 12
    thetahat_prior <- (wfrachat_prior * (mu_w - mu_l) + mu_l) / nlooks
    thetavar_prior <- wfracvar_prior * (mu_w - mu_l)^2 / (nlooks^2)
    
    # prior inverse gamma parameters on theta (by moment matching to unif)
    alpha_prior <- thetahat_prior^2 / thetavar_prior + 2
    beta_prior <- thetahat_prior * (thetahat_prior^2 / thetavar_prior + 1)
    
    # posterior parameters on theta (inverse gamma)
    alpha_post <- alpha_prior + nlooks
    beta_post <- beta_prior + p
    
    # inverse gamma density
    out <- dgamma(1 / x_theta, shape = alpha_post, rate = beta_post)
  } else if (method == "iguninf") {
    # Same, just boost the variance to make "uninformative"
    # Uniform prior moments
    wfrachat_prior <- 0.5
    wfracvar_prior <- 25
    thetahat_prior <- (wfrachat_prior * (mu_w - mu_l) + mu_l) / nlooks
    thetavar_prior <- wfracvar_prior * (mu_w - mu_l)^2 / (nlooks^2)
    
    # prior inverse gamma parameters on theta
    alpha_prior <- thetahat_prior^2 / thetavar_prior + 2
    beta_prior <- thetahat_prior * (thetahat_prior^2 / thetavar_prior + 1)
    
    # posterior parameters on theta (inverse gamma)
    alpha_post <- alpha_prior + nlooks
    beta_post <- beta_prior + p
    
    # inverse gamma density
    out <- dgamma(1 / x_theta, shape = alpha_post, rate = beta_post)
  } else if (method == "scaleinv") {
    # scale-invariant prior
    # posterior is inverse gamma -- limit as alpha, beta priors go to zero. 
    out <- dgamma(1 / x_theta, shape = nlooks, scale = 1 / p)
  } else if (method == "gamma-unif") {
    # browser()
    out <- rep(0, length(x_theta))
    keep <- x >= 0 & x <= 1
    out[keep] <- (x_theta[keep])^(-nlooks) * exp(-p / x_theta[keep])

  } else {
    stop(sprintf("method %s not recognized.\n", method))
  }
  
  out
}

# helper funcitons for posterior mean, variance of water frac
igmean_wfrac <- function(alpha, beta, nlooks, mu_w, mu_l) {
  igmean_theta <- beta / (alpha - 1)
  out <- (nlooks * igmean_theta - mu_l) / (mu_w - mu_l)
  out
}

igvar_wfrac <- function(alpha, beta, nlooks, mu_w, mu_l) {
  igvar_theta <- beta^2 * (alpha - 1)^(-2) * (alpha - 2)^(-1)
  out <- nlooks^2 * igvar_theta * (mu_w - mu_l)^(-2)
  out
}


```

### Stan sampler for true gamma-uniform case

```{r}
gamunifmod1 <- stan_model("../src/gamma-unif.stan")
gamunifmod2 <- stan_model("../src/gamma-unif2.stan")

gamunifsampler <- function(p, mu_w, mu_l, nlooks, 
                           ...,
                           stanmodel = gamunifmod1) {
  sampdata <- list(N = 1, y = structure(p, .Dim = 1L), 
                   mu_l = mu_l, mu_w = mu_w, nlooks = nlooks)
  samps <- sampling(stanmodel, data = sampdata, pars = "wfrac", 
                  ...)
  samps
  out <- extract(samps, pars = "wfrac", inc_warmup = FALSE)
  out
}

glimpse(testobs)

foo <- with(testobs[1,], gamunifsampler(coh_power, mu_w, mu_l, nefflooks, 
                                        cores = 2, chains = 2))

bar <- with(testobs[2,], gamunifsampler(coh_power, mu_w, mu_l, nefflooks, 
                                        stanmodel = gamunifmod2,
                                        cores = 2, chains = 2))

hist(foo$wfrac)
hist(bar$wfrac)
```


### Pixel-level density plots (n = 12)

```{r}

## The following in case I need to recreate my original plot (before I set a seed)
# orig_range <- c(2063, 2139, 1611, 1813, 1597, 2528, 
#                 1725, 1344, 1745, 1420, 1619, 2612)
# orig_azim <- c(3646, 4006, 2873, 3543, 3160, 477, 
#                3280, 2704, 3328, 2352, 3124, 175)

small_inds <- sample(1:nrow(testobs), 12)
testobs_small <- testobs[small_inds, ]

glimpse(testobs_small)
# dwfrac vectors
xvec <- 1:600 / 200

# all curve values as data.frame for a given row of testobs_small

allcurvefun <- function(tosrow, xvec) {
  
  cohpow <- tosrow$coh_power
  muw <- tosrow$mu_w
  mul <- tosrow$mu_l
  nlook <- tosrow$nefflooks
  allmethods <- c("orig", "igapprox", "iguninf", "scaleinv", "gamma-unif")
  densveclist <- allmethods %>% 
    purrr::map(~data.frame(x = xvec,
                   density = dwfrac(xvec, p = cohpow, mu_w = muw, 
                             mu_l = mul, nlooks = nlook, method = .))) %>% 
    purrr::map(function(df) {df$density = df$density / max(df$density); df})
  densvecdf <- dplyr::bind_rows(setNames(densveclist, allmethods),
                                .id = "method")
  densvecdf
}

allcurvedf <- testobs_small %>% 
  split(f = 1:nrow(.)) %>% 
  purrr::map(~allcurvefun(., -100:200 / 100)) %>% 
  bind_rows(.id = "pixel") %>% 
  mutate(wfrac = x,
         pixel = as.factor(as.numeric(pixel)))

allcurvedf %>% 
  ggplot(aes(x = wfrac, y = density)) + 
  geom_line(aes(color = method)) +
  facet_wrap(~pixel)

```

### Pixel-level histograms. 

```{r}
standatas <- testobs_small %>% 
  # glimpse() %>% 
  split(f = 1:nrow(.)) %>% 
  purrr::map(~gamunifsampler(.$coh_power, .$mu_w, .$mu_l, .$nefflooks, 
                            cores = 2))

standatas %>% 
  purrr::map(~data.frame(wfrac = as.vector(.$wfrac))) %>% 
  bind_rows(.id = "pixel") %>%
  mutate(pixel = as.factor(as.numeric(pixel))) %>% 
  ggplot(aes(x = wfrac)) + 
  geom_histogram(aes(y = ..ncount..), breaks = 0:20 / 20) + 
  geom_line(aes(y = density, color = method), data = allcurvedf, size = 1) +
  facet_wrap(~pixel, ncol = 4) + 
  theme_minimal() + 
  theme(legend.position = "bottom", axis.title.y = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank())

ggsave("../fig/wfrac_methods_dens.png", height = 6, width = 8)
```

### Check-in

- How close am I to results? 
  - Dataset prepped? Check! (`testobs`)
  - Density functions rerady? Check! (`dwfrac()`)
  - Samplers ready? Check!
  - Pixel-level plots, n = 12? Check!
  - Pixel clouds using approximated gamma? 
  


  
  
  