---
title: "notebook20190701"
author: "Mark Hagemann"
date: "7/1/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```


Getting back into things after France and Florida. Manuscript time, big time. Working with validation-objects script. Also, manuscript project. I've gotten some new results since last time I worked on the manuscript, so I'll need to sort things out first. Do I have an outline somewhere? Yes! Simplenote. 

What did we end up varying? I'll need to set up the axes of validation. See Rui's email with Brent.

Looks like there are 18 total runs (plus possibly 6 more due to passes being split over multiple runs). I need now to figure out which run numbers these correspond to. Variables:

- pass
- day
- tile
- refdem
- land_sig0

constant:

- water_sig0 == "10db"
- refdem_res == "10m"

See if I can pull this info from the manifest. 

```{r}
ro_manifest() %>% 
  mutate(sig0_ref = paste0(refdem, land_sig0)) %>% 
  filter(water_sig0 == "10dB",
         refdem_res == "10m",
         sig0_ref %in% c("GDEM-100dB", "SRTM-5dB")) %>% 
  group_by(pass, day, tile, refdem, land_sig0) %>% 
  summarize(n = n()) %>%  
  # ungroup() %>%
  # summarize(n = n())
  kable()

ro_manifest() %>% 
  mutate(sig0_ref = paste0(refdem, land_sig0)) %>% 
  filter(water_sig0 == "10dB",
         refdem_res == "10m",
         sig0_ref %in% c("GDEM-100dB", "SRTM-5dB"),
         pass == 264, day == 221, 
         refdem == "GDEM", land_sig0 == "-100dB")


duplicated(ro_manifest()$indir)

length(unique(ro_manifest()$indir))

ro_manifest()$outno
```

Aha! It's all there--at least to the point that my latest csv is entirely redundant. But do I have all the requisite runs? Count is short.

```{r}
ro_manifest() %>% 
  mutate(sig0_ref = paste0(refdem, land_sig0)) %>% 
  filter(water_sig0 == "10dB",
         refdem_res == "10m",
         sig0_ref %in% c("GDEM-100dB", "SRTM-5dB")) %>% 
  group_by(pass, day) %>% 
  summarize(n = n()) %>% 
  kable()
```

Missing: pass 527, day 119; pass 264, day 110; pass 249, day??

```{r}
ro_manifest() %>% 
  filter(day == 119, pass == 527, refdem == "GDEM") %>% 
  glimpse()

ro_manifest() %>% 
  filter(day == 110, pass == 264, refdem == "GDEM") %>%
  glimpse()

ro_manifest() %>% 
  filter(pass == 249, day == 109, priordb == "$PRIORLOC2", land_sig0 == "-100dB",
         water_sig0 == "10dB") %>% 
  glimpse()
  # group_by(day) %>% 
  # summarize(n = n())
```

Ask Rui about:

- 527-119, GDEM, -100dB land
- 264-110, GDEM, -100dB land
- 249-109, SRTM

After emailing with Rui and Mike, I'll start with cycles 2 and 3--that's:

- 249: 130 and 220
- 264: 131 and 221
- 527: 209, 302

I've got everything re-read in the validation script. That's a good stopping place for today. Tomorrow I'll work on how to present the new axes of validation. Also writing. 

