---
title: "notebook20190513"
author: "Mark Hagemann"
date: "5/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Today I'm redoing some riverobs runs with different things toggled on that I hadn't done before. I think I've successfully used the improved geolocation, but I don't notice any difference on the map. See what it's done different. 


```{r}
library(rivertile)

joindf <- join_pixc("../output/sac18") %>% 
  mutate(classification = as.factor(classification))

glimpse(joindf)
all.equal(joindf$longitude, joindf$longitude_vectorproc)

diff_gg <- joindf %>% 
  mutate(londif = abs(longitude - longitude_vectorproc),
         latdif = abs(latitude - latitude_vectorproc)) %>% 
  arrange(desc(londif)) %>% 
  `[`(1:100, ) %>% 
  ggplot(aes(x = latdif, y = londif, 
             text = node_index)) +
  geom_point()

diff_gg
ggplotly(diff_gg, tooltip = "text")

```

Look at a single node that has a big-difference pixel.

```{r}
theseinds <- 471:490

joindf %>% 
  filter(node_index %in% theseinds) %>% 
  ggplot(aes(x = longitude, y = latitude, color = classification))+
  geom_point()

joindf %>% 
  filter(node_index %in% theseinds) %>% 
  ggplot(aes(x = longitude_vectorproc, y = latitude_vectorproc, 
             color = classification))+
  geom_point()


```

Cool, it must be a simple issue with my shiny app. 

See how it affects validation. 

```{r}
nodeval1 <- rt_valdata("../output/sac18_improved")
nodeval2 <- rt_valdata("../output/sac18")

commonnodes <- intersect(nodeval1$node_id, nodeval2$node_id)
nodeval1 <- filter(nodeval1, node_id %in% commonnodes)
nodeval2 <- filter(nodeval2, node_id %in% commonnodes)
```

```{r}
valvars <- c("height", "height2", "width", "area_total")
# valvars <- c("latitude", "longitude")
rt_val_hist(nodeval1, vars = valvars, scale = TRUE) + ggtitle("Improved geolocation")
rt_val_hist(nodeval2, vars = valvars, scale = TRUE) + ggtitle("No Improved geolocation")

rt_val_hist(nodeval1, vars = valvars, scale = FALSE) + ggtitle("Improved geolocation")
rt_val_hist(nodeval2, vars = valvars, scale = FALSE) + ggtitle("No Improved geolocation")


```

Improved geolocation makes errors and especially scaled errors much worse. Why?

- Find a node with large discrepancy 
- plot uncorrected pixels with centroid, corrected centroid overlain
- plot corrected pixels with centroid, uncorrected centroid overlain.

```{r}
unique(nodeval1$variable)
plotvar <- "gdem_val"
lalodf1 <- nodeval1 %>% 
  filter(variable %in% c("latitude", "longitude")) %>% 
  select(node_id, variable, !!plotvar) %>% 
  spread(key = "variable", value = plotvar) %>% 
  transmute(node_id, lat1 = latitude, lon1 = longitude) 

lalodf2 <- nodeval2 %>% 
  filter(variable %in% c("latitude", "longitude")) %>% 
  select(node_id, variable, !!plotvar) %>% 
  spread(key = "variable", value = plotvar) %>% 
  transmute(node_id, lat2 = latitude, lon2 = longitude)

lalodf <- inner_join(lalodf1, lalodf2, by = "node_id") %>% 
  mutate(londif = lon1 - lon2, latdif = lat1 - lat2, 
         eucdist = sqrt(londif^2 + latdif^2),
         logeuc = log(eucdist))

lalodf %>% 
  arrange(desc(eucdist))

glimpse(lalodf)
summary(lalodf)

```

Hmm, geolocation is the same except for 4 nodes (update: zero nodes). The difference is with the gdem truth! Why is that different? 

Node latitude and longitue may just be reflecting the prior. But why is gdem not doing the same? 

Time to compare unimproved to improved directly. 

```{r}
nodedf1 <- rt_read("../output/sac18_improved/rt.nc")
nodedf2 <- rt_read("../output/sac18/rt.nc")
nodedf <- inner_join(nodedf1, nodedf2, by = c("node_id", "reach_id"))

glimpse(nodedf)

plot(height.y - height.x ~ height.x, nodedf)


gdemdf1 <- rt_read("../output/sac18_improved/rt_gdem.nc")
gdemdf2 <- rt_read("../output/sac18/rt_gdem.nc")
gdemdf <- inner_join(gdemdf1, gdemdf2, by = c("node_id", "reach_id"))

glimpse(gdemdf)

plot(height.y - height.x ~ height.x, gdemdf)




```



Try doing it all in 1 go, using nodeval's

```{r}
nodeval <- inner_join(nodeval1, nodeval2, 
                      by = c("reach_id", "node_id", "variable"))
glimpse(nodeval)

nodeval %>% 
  ggplot(aes(x = gdem_val.x, y = gdem_val.y)) +
  geom_point(aes(color = variable)) +
  scale_x_log10() + 
  scale_y_log10() + annotation_logticks()

nodeval %>% 
  filter(variable == "height") %>% 
  ggplot(aes(x = gdem_val.x, y = gdem_val.y)) +
  geom_point(aes(color = variable))

list(improved = nodeval1, unimproved = nodeval2) %>% 
  bind_rows(.id = "geoloc") %>% 
  filter(variable == "height") %>% 
  ggplot(aes(x = node_id, y = gdem_val)) +
  geom_point(aes(color = geoloc))

list(improved = nodeval1, unimproved = nodeval2) %>% 
  bind_rows(.id = "geoloc") %>% 
  filter(variable == "area_total") %>% 
  ggplot(aes(x = node_id, y = gdem_val)) +
  geom_point(aes(color = geoloc))


```

Track back to pixel level. 


```{r}
pixdf <- list(
  improved = join_pixc("../output/sac18_improved/"), 
                       # pixcname = "fake_pixc.nc", pcvname = "pcv_gdem.nc"),
  unimproved = join_pixc("../output/sac18")#, 
                       # pixcname = "fake_pixc.nc", pcvname = "pcv_gdem.nc")
) %>% 
  bind_rows(.id = "geoloc")

pixdf %>% 
  filter(geoloc == "improved") %>% 
  glimpse()
pixdf %>% 
  filter(geoloc == "unimproved") %>% 
  glimpse()

pixdf %>% 
  sample_n(2000) %>% 
  ggplot(aes(x = node_index, y = height, color = geoloc)) + 
  geom_point()

pixdf %>% 
  sample_n(2000) %>% 
  ggplot(aes(x = longitude_vectorproc, 
             y = height, color = geoloc)) + 
  geom_point()

pixdf %>% 
  select(pixc_index, node_index, height, geoloc) %>% 
  group_by(node_index, geoloc) %>% 
  summarize(mean = mean(height)) %>% #, min = min(height), max = max(height)) %>% 
  spread(key = geoloc, value = mean) %>% 
  na.omit() %>% glimpse() %>% 
  # sample_n(1000) %>% glimpse()
  ggplot(aes(x = unimproved, y = improved)) + 
  geom_point() + geom_abline(slope = 1, intercept = 0)

pixdf %>% 
  select(range_index, azimuth_index, node_index, height, geoloc) %>% 
  spread(key = geoloc, value = height) %>% 
  na.omit() %>% glimpse() %>% 
  sample_n(1000) %>% glimpse() %>% 
  ggplot(aes(x = unimproved, y = improved)) + 
  geom_point() + geom_abline(slope = 1, intercept = 0)


```

So the gdem is rotten at the pixc level. These are two runs that use the same pixc as input. 

Crazy, rerunning those simulations fixed it. Arrgh! Must have been a stray fake pixel cloud in the project folder. Repeat for a high-flow case. Done (via ctrl+F). Looks identical as well. 