---
title: "notebook20190318"
author: "Mark Hagemann"
date: "3/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Working on getting pixc read in, implementing this for validation app. 

I may want to use reticulate package and python netcdf. 

```{r}
library(fs)
datadir <- "/media/removable/USB Drive/swot-error-data/cycle_0001_pass_0249_001L_nlcd-5dB_water10dB_50m_CBE/"

ncpath <- path(datadir, "pixel_cloud.nc")

pixcnc <- nc_open(ncpath)

foo <- pixc_read(ncpath)

```



```{r}
library(leaflet)
classpal <- colorNumeric("viridis", domain = 1:4)

foo %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(color = ~classpal(classification))

```

Before I resort to reticulating with python, do what I can in R. 

- I thought pixcvec had 1:1 correspondence with pixc, but there are many more points in pixc. Maybe pixcvec stores an index? Looks like!

```{r}
bar2 <- foo %>% 
  dplyr::select(azimuth_index, range_index, classification,
                latitude, longitude) %>% 
  right_join(bar)
```

OK, so that's actually pretty straightforward. What's next?

- I'll have to figure out how to reference (or change) file location for pixc. 
    - Store in an R-readable (txt? md?) within each output folder?
    - copy pixc into each output folder?
    - symbolic link in output folder?
        - Won't work on Windows
- Exactly what functionality do I want?
    - For a set of selected nodes...
    - Plot pixc with classification
        - Based on proximity
        - Based on node assignment (differentiate from proximity using outline color?)
    - Plot pixcvec with classification
        - proximity-based
        - node assignment based
- Under the hood
    - Read in pixc and fake pixc when folder data gets read in
        - lat, lon, classification, others?
    - Join to pixcvec on the fly?

Try fixing `pixc_read_gdem`

```{r}
gdpath <- path(datadir, "gdem_preproc.nc")

```

- It may be worth defining my own funciton for reading in subsets serially. 
    - Be sure to include status indicator so I can interrupt if it's prohibitively slow. 
    - 
    
    
```{r}
nc <- nc_open(gdpath)
varid <- "latitude"
inds <- head(waterpix, 100)

ncvar_ss <- function(nc, varid=NA, inds) {
  if (length(dim(inds)) > 2) stop("dimensionality > 2 not supported.")
  
  indlist <- split(inds[, 1], f = inds[, 2])

  pb <- progress::progress_bar$new(total = length(indlist))
  pb$tick(0)
  
  vals <- list()
  for (i in 1:length(indlist)) {
    pb$tick()
    vals[[i]] <- ncvar_ss_1d(nc, varid = varid, indvec = indlist[[i]], 
                         inds2 = as.numeric(names(indlist)[i]))
  }
  out <- unlist(vals)
  out
}

# Check for inefficiencies of this method. Result should be close to 1. 
check_ineff <- function(indmat) {
  num1 <- nrow(indmat)
  num2 <- as.data.frame(indmat) %>% 
    group_by(col) %>% 
    summarize(nret = max(row) - min(row) + 1) %>% 
    summarize(sum = sum(nret)) %>% 
    `[[`("sum")
  out <- num2 / num1
  out
}

indvec <- indlist[[1]]
inds2 <- as.numeric(names(indlist)[1])


ncvar_ss_1d <- function(nc, varid=NA, indvec, inds2 = NULL) {
  stopifnot(is.numeric(indvec) && is.vector(indvec))
  
  minind <- min(indvec)
  maxind <- max(indvec)
  indcnt <- maxind - minind + 1
  newinds <- indvec - minind + 1
  
  if (!is.null(inds2)) {
    minind <- cbind(minind, inds2)
    indcnt <- cbind(indcnt, 1)
  }
  
  out <- ncvar_get(nc, varid = varid, start = minind, count = indcnt)
  
  out <- as.vector(out[newinds])
  out
}


```


test it!

```{r}
nc <- nc_open(gdpath)
varid <- "latitude"
inds <- head(waterpix, 100)

latvec <- ncvar_ss(nc, "latitude", waterpix)
ltypevec <- ncvar_ss(nc, "landtype", inds = waterpix)
```

Appears to work. Now I can modify pixc_read_gdem, etc. 


```{r}
gdempixc <- path("../output/sac15/fake_pixc.nc")

foo <- pixc_read(gdempixc)

foo <- pixcvec_read("../output/sac15/pcv_gdem.nc")
```

So apparently my regular functions worked all along. Why did I ever want to read in the raw gdem? Anyway, time to go back and see where to go with shiny app. 


