---
title: "notebook20190327"
author: "Mark Hagemann"
date: "3/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Why are reach-level relative errors different for width and area?

```{r}
dir <- "~/Documents/swot-error/output/sac18"

reach_val <- rt_valdata(dir, group = "reaches")

rt_val_scatter(reach_val, variables = c("width", "area_total"), 
               yvar = "relerr")
rt_val_scatter(reach_val, variables = c("width", "area_total"), 
               yvar = "err")

```

How are these calculated? 

```{r}
path(dir, "rt.nc") %>% 
  rt_read(group = "reaches") %>% 
  glimpse()
```

I think the answer might be that reach lengths are different between the gdem and real pixc, since the former has nodes the latter doesn't. That would make sense!

So TODO: ensure gdem has same nodes as pixc. Prune partial node obs from pixc. 

I think I can forge ahead now. 

### Cumulative relative error plot

Put this into a function. 

```{r}


cumerr_plot <- function(valdf, reach_ids = "all", 
                        variables = c("width", "area_total"),
                        desc = FALSE) {
  
  if (length(reach_ids) == 1 && reach_ids == "all")
    reach_ids <- unique(valdf$reach_id)
  if (length(variables) == 1 && variables == "all")
    variables <- unique(valdf$variable)
  
  rankfun <- function(x) if (desc) -x else x

  plotdf <- valdf %>%
    dplyr::filter(reach_id %in% reach_ids,
                  variable %in% variables) %>% 
    mutate(reach_id = as.factor(reach_id)) %>% 
    group_by(variable, reach_id) %>% 
    mutate(relerr = pixc_err / sigma_est) %>% 
    arrange(rankfun(relerr)) %>% 
    mutate(cum_err = cumsum(pixc_err),
       cum_sigma = sqrt(cumsum(sigma_est^2)),
       cum_relerr = cum_err / cum_sigma, 
       relerr_rank = rank(rankfun(relerr))) %>% 
    ungroup()

  ggplot(plotdf, aes(x = relerr_rank)) +
    geom_line(aes(y = cum_relerr, color = reach_id, group = reach_id)) +
    facet_wrap(~variable, scales = "free")
}


cumerr_plot(valdf_n, variables = c("height", "width", "area_total"))
cumerr_plot(valdf_n, variables = c("height", "width", "area_total"), desc = TRUE)
```


I think that looks good. Now do one for leave-one-out. 


```{r}

looerr_plot <- function(valdf, reach_ids = "all", 
                        variables = c("width", "area_total"),
                        desc = FALSE) {
  
  if (length(reach_ids) == 1 && reach_ids == "all")
    reach_ids <- unique(valdf$reach_id)
  if (length(variables) == 1 && variables == "all")
    variables <- unique(valdf$variable)
  
  rankfun <- function(x) if (desc) -x else x
  
  loosum <- function(x, na.rm = FALSE) sum(x, na.rm = na.rm) - x
  
  plotdf <- valdf %>%
    dplyr::filter(reach_id %in% reach_ids,
                  variable %in% variables) %>% 
    mutate(reach_id = as.factor(reach_id)) %>% 
    group_by(variable, reach_id) %>% 
    mutate(relerr = pixc_err / sigma_est) %>% 
    arrange(rankfun(relerr)) %>% 
    mutate(cum_err = loosum(pixc_err),
       cum_sigma = sqrt(loosum(sigma_est^2)),
       cum_relerr = cum_err / cum_sigma, 
       relerr_rank = rank(rankfun(relerr)),
       node_ind = node_id - min(node_id)) %>% 
    ungroup()

  ggplot(plotdf, aes(x = node_ind)) +
    geom_line(aes(y = cum_relerr, color = reach_id, group = reach_id)) +
    facet_wrap(~variable, scales = "free")
}

looerr_plot(valdf_n, variables = c("height", "width", "area_total"))
cumerr_plot(valdf_n,reach_ids = 7, variables = c("height", "width", "area_total"))
```


I think that looks good. Later I'll put it into rivertile and into the shiny app. 

Next I want to make sure I can replicate the riverobs reach aggregation. This will be useful for recomputing reach values after filtering or adjusting node values. 

```{r}

nodedata <- rt_read(path(dir, "rt.nc"), keep_na_vars = TRUE)
reachdata <- rt_read(path(dir, "rt.nc"), group = "reaches", keep_na_vars = TRUE)

intersect(names(nodedata), names(reachdata))
setdiff(names(reachdata), names(nodedata))

calc_len <- function(area, width) {
  out <- area / width
  out
}

reach_height_lm <- function(node_h, node_h_u, node_x, loc_offset, 
                         weight = TRUE) {
  weights <- 1 / (node_h_u^2)
  if (!weight) weights <- NULL
  
  hxdf <- data.frame(x = node_x - mean(node_x) + loc_offset, h = node_h)
  hxmod <- lm(h ~ x, hxdf, weights = weights)
  
  hxmod
}

reachadjdf <- reachdata %>% 
  dplyr::select(reach_id, loc_offset)

foo <- nodedata %>% 
  left_join(reachadjdf) %>% 
  filter(reach_id == 3) %>% 
  arrange(node_id) %>% 
  mutate(nodelen = calc_len(.$area_total, .$width),
         cumlen = cumsum(nodelen))

bar <- with(foo, reach_height_lm(node_h = height2, node_h_u = height2_u, 
           node_x = cumlen, loc_offset = loc_offset, weight = TRUE))



est_height <- function(node_h, node_h_u, node_x, loc_offset, weight = TRUE) 

reach_agg <- function(nodedata) {
  
  if (is.null(nodedata$cumlen) || is.null(nodedata$nodelen)) {
    stop("nodedata must have the following precomputed: nodelen, cumlen, loc_offset")
  }
  
  # Make linear models for height, slope
  hxmods <- split(nodedata, f = nodedata$reach_id) %>% 
    purrr::map(~reach_height_lm(node_h = .$height, node_h_u = .$height2_u, 
           node_x = .$cumlen, loc_offset = .$loc_offset, weight = TRUE))
  hxcoef <- map(hxmods, ~as.data.frame(summary(.)$coefficients, row.names = FALSE)) %>% 
    map(~setNames(.[, 1:2], c("est", "std"))) %>% 
    map(~mutate(., param = c("intercept", "slope"))) %>% 
    bind_rows(.id = "reach_id")
  
  reach_heights <- filter(hxcoef, param == "intercept")$est
  reach_heights_u <- filter(hxcoef, param == "intercept")$std
  reach_slopes <- filter(hxcoef, param == "slope")$est * 1e6
  reach_slopes_u <- filter(hxcoef, param == "slope")$std * 1e6
  
  nd_agg <- nodedata %>% 
    group_by(reach_id) %>% 
    summarize(time = median(time), time_tai = median(time_tai), 
              area = sum(area_total),
              area_u = sqrt(sum(area_tot_u^2)),
              width = area / sum(nodelen),
              width_u = area_u / sum(nodelen)) %>% 
    mutate(height = reach_heights,
           height_u = reach_heights_u,
           slope = reach_slopes, 
           slope_u = reach_slopes_u) %>% 
    rename(area_total = area, area_tot_u = area_u)
  
  nd_agg
}


#' Check whether all node IDs are sequential --i.e. none are missing. 
all_sequential <- function(node_ids) {
  ids_adj <- node_ids - min(node_ids) + 1
  isTRUE(all.equal(ids_adj, 1:length(ids_adj)))
}

add_nodelen <- function(nodedata, reachdata) {
  
  nodeids <- nodedata$node_id
  if (!all_sequential(nodeids)) stop ("Gaps exist in node data")

  # join to loc_offset from reachdata
  reachadjdf <- reachdata %>% 
    dplyr::select(reach_id, loc_offset)
  
  out <- nodedata %>% 
    arrange(node_id) %>% 
    left_join(reachadjdf, by = "reach_id") %>% 
    mutate(nodelen = calc_len(area_total, width),
           cumlen = cumsum(nodelen))
    
  out
}

```

Bah, first I need to find out why reachdata has duplicate rows. Fix that immediately. OK, done. 


Now that I have that coded up, think through how I might fix mismatches between gdem and pixc data. Starting with area. 

Since the gdem has nodes that the pixc does not, I want to filter these out and recompute gdem area. That would be a simple `filter()` followed by `reach_agg()`. But `add_nodelen()` has to be called beforehand, and cannot be touched by the filter operation. 


Everything appears to be working as intended. Time to add to rivertile, document, test more fully. 