---
title: "notebook20190820"
author: "Mark Hagemann"
date: "8/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm becoming convinced that I need to do a separate set of RiverObs runs after using my upstream-downstream algo on the pixel clouds. Take a similar approach as I did with fixing the water fraction uncertainty. 

And I can use my nc_subset() function!

```{r}
library(subsetnc)
# modified from update_pixc()
usds_pixc <- function(pixcfile, pcvfile, newfile = "pixel_cloud_usds.nc",
                      is_gdem = FALSE) {
  stopifnot(file.exists(pixcfile))
  putdir <- normalizePath(paste0(pixcfile, "/.."))
  putfile <- file.path(putdir, newfile)
  file.copy(pixcfile, putfile, overwrite = TRUE)
  outnc <- nc_open(putfile, write = TRUE)
  on.exit(nc_close(outnc))
  
  origpixcnc <- nc_open(pixcfile)
  on.exit(nc_close(origpixcnc))
  origpixcdf <- pixc_read(pixcfile) %>% 
    mutate(rangeazim = range_index * 1e5 + azimuth_index)
  origpcvdf <- pixcvec_read(pcvfile)
  
  subsetdf <- us_ds(origpcvdf) %>% filter(connected) %>% 
    select(range_index, azimuth_index) %>% 
    mutate(rangeazim = range_index * 1e5 + azimuth_index)
  # browser()
  
  ncrange <- ncvar_get(outnc, "pixel_cloud/range_index")
  ncazim <- ncvar_get(outnc, "pixel_cloud/azimuth_index")
  ncrangeazim <- ncrange * 1e5 + ncazim
  
  keepdim <- match(subsetdf$rangeazim, ncrangeazim)
  
  outclass <- ncvar_get(outnc, "pixel_cloud/classification")
  
  if (is_gdem) {
    outclass[-keepdim] <- 0
  } else {
    outclass[-keepdim] <- 1
  }
  
  if (is_gdem) {
    outclass[-keepdim] <- 0
  } else {
    outclass[-keepdim] <- 1
  }
  ncvar_put(outnc, "pixel_cloud/classification", outclass, 
            start = 1, count = length(outclass))      

}


```


Now make the new pixc netcdfs. 

```{r}
dirs_to_run <- c(valdirs_simple, valdirs_composite, valdirs_frac) # from validation objects

dir <- dirs_to_run[11]
for (dir in dirs_to_run) {
  print(dir)
  pixcfile <- fs::path(dir, "pixel_cloud_new.nc")
  pcvfile <- fs::path(dir, "pcv.nc")
  usds_pixc(pixcfile = pixcfile, pcvfile = pcvfile, newfile = "pixel_cloud_new_usds.nc")
}
```

Now gdem. I really hope this works. 

```{r}
gdemdirs <- rodir(valnums)

for (dir in gdemdirs) {
  print(dir)
  pixcfile <- fs::path(dir, "fake_pixc.nc")
  pcvfile <- fs::path(dir, "pcv_gdem.nc")
  
  usds_pixc(pixcfile = pixcfile, pcvfile = pcvfile, 
            newfile = "fake_pixc_usds.nc", is_gdem = TRUE)
}


```


Why is netcdf giving me zero-length variables?

```{r}
pixcfile1 <- fs::path(dir, "pixel_cloud.nc")
pixcfile2 <- fs::path(dir, "fake_pixc.nc")

testnc1 <- nc_open(pixcfile1)
testnc2 <- nc_open(pixcfile2)

keepinds <- 1:10

nc_subset(testnc1, `tvp/num_tvps` %in% keepinds, keepinds = keepinds)
nc_subset(testnc2, `tvp/nr_tvps` < 10)
```

Tracing the call stack. 

- `ncss_create_fill`
- `ncvar_put`
- `ncvar_size`
- `.C("R_nc4_varsize", ...)`
- `nc_inq_dimlen` Code is here: https://www.unidata.ucar.edu/software/netcdf/docs/ddim_8c_source.html
- 


I figured out where the problem is, but not why it's happening. I did figure out a workaround. I think. Can I use dots argument cleverly?

```{r}
testfun <- function(...) {
  browser()
  argexprs <- enexprs(...)
  
  print("hello")
}

c = 1:4
testfun(a = 3, d < 23, c = c)
```


This is really puzzling scoping behavior. 

```{r}
fun1 <- function(x, ...) {
  exprs <- enexprs(...)
  # browser()
  
  for (expr in exprs) print(eval_tidy(expr, env = parent.frame()))
  print("done")
}

fun2 <- function(y) {
  z <- 3
  x <- "abc"
  fun1(x, z < 5)
}

fun2(5)
```

Right. Need to use `parent.frame()` to get dynamic scoping behavior. 

Still running into problems. I think I'm better off changing the classification to land rather than subsetting the pixc. This will result in larger files, but will be faster. 

Alright, that's done. Make a new notebook to check out the results.
