---
title: "notebook20190522"
author: "Mark Hagemann"
date: "5/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Yesterday I got the passes read in; today work on tiles. 

Format is a little hard to understand. They only have 2 passes?

```{r}
tiles <- readr::read_delim("../data/tiles/tile-database-2018.txt", 
                           delim = " ",
                           col_types = "iinnn") %>% 
  setNames(c("pass", "tiles", "latitude", "longitude", "heading"))

tiles %>% 
  ggplot(aes(x = longitude, y = latitude)) +
  geom_point(aes(color = pass))
  
```

Seems like a lot of work there. I don't doubt the information is in there, but now is not the time to do that. 


First get the .RData files for the passes. 


```{r}
ro_manifest()$pass %>% unique()

passes <- c(249, 264, 527)

list.files("../data/orbits")
passes_files <- sprintf("%s/SWOT_ephemeris2015_science_full_%04d.nc",
                        "~/Documents/swot-error/data/orbits",
                        passes)

passes_sf <- map(passes_files, ~orbit_read(.)) %>% 
  setNames(passes)


allpasses_df <- passes_sf %>% 
  map(~data.frame(.)) %>% 
  bind_rows(.id = "pass")


allgeoms <- Reduce(f = c, x = map(passes_sf, ~pull(., geometry)))
allpasses_sf <- mutate(allpasses_df, geometry = allgeoms) %>% 
  st_as_sf()
  
ggplot(allpasses_sf) +
  geom_sf(aes(color = pass))

```

I should start a munge/ script for riverproducts app objects. DONE.

Next, make a table for pass, tile, date. I suppose this would be a good time to select the simulations to show. These can be changed, of course. 

```{r}
ro_manifest() %>% 
  filter(refdem == "GDEM", refdem_res == "10m", priordb == "$PRIORLOC4")
  select(outno, pass, tile, day)
```

Good. Next, get the prior db. 

```{r}
ncfile <- "D:/data/SWOT-prior/PriorDistributionFolder/netcdfV4/NA07.nc"

nodedf <- priornode_read(ncfile)

reachpal <- colorNumeric("viridis", nodedf$reach_id)

nodedf %>% 
  filter(reach_id %in% 41352:41477) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(fillColor = ~reachpal(reach_id), fillOpacity = 0.8, 
             stroke = FALSE, radius = 5,
             popup = ~paste(reach_id)) %>% 
  addLegend(pal = reachpal, values = ~reach_id)

cldf <- priorcl_read(ncfile, reachids = (41352:41477))


cldf %>% 
  leaflet() %>% 
  addTiles() %>% 
  addPolylines(color = ~reachpal(reach_id), opacity = 0.8, 
             stroke = FALSE, weight = 2,
             popup = ~paste(reach_id)) %>% 
  addLegend(pal = reachpal, values = ~reach_id)



cldf[2, ] %>% 
  ggplot() +
  geom_sf()
```

This is taking a really long time. Is it faster if I do it all in one shot instead of a group_by/summarize?

```{r}
cldf <- priorcl_read(ncfile, reachids = (41352:41477), as_sf = FALSE) %>% 
  filter(node_id != 0)

clsf <- st_as_sf(cldf, coords = c("longitude", "latitude"))
clsp <- st_cast(clsf$geometry, to = "LINESTRING", ids = clsf$node_id)

cldf_smry <- data.frame(clsf) %>% 
  group_by(node_id, reach_id) %>% 
  summarize(n = n()) %>% 
  ungroup()

clsf_smry <- cldf_smry %>% 
  arrange(node_id) %>% 
  mutate(geometry = clsp) %>% 
  st_as_sf()

ggplot(clsf_smry) + 
  geom_sf(aes(color = reach_id)) +
  theme_minimal()

```

I think it will be easier to just focus on Sacramento reaches. Do one version for updated prior and one for original. 


```{r}
reaches1 <- path(rodir(40), "rt.nc") %>% 
  rt_read(group = "reaches") %>% 
  pull(reach_id)
reaches2 <- path(rodir(52), "rt.nc") %>% 
  rt_read(group = "reaches") %>% 
  pull(reach_id)

priorncfile1 <- "D:/data/SWOT-prior/PriorDistributionFolder/netcdfV4/NA07.nc"
priorncfile2 <- path("~/Documents/swot-error/data/priordb-update/Sac_sample_db15.nc")


clsf1 <- priorcl_read(priorncfile1, reachids = reaches1, as_sf = TRUE) 
clsf2 <- priorcl_read(priorncfile2, reachids = reaches2, as_sf = TRUE) 

ggplot(clsf1) + geom_sf(aes(color = reach_id))
ggplot(clsf2) + geom_sf(aes(color = reach_id))
```

