---
title: "notebook20190809"
author: "Mark Hagemann"
date: "8/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


For today's show-and-tell meeting, present a single qq plot showing composite + simple + water fraction methods validation at node level, both for "orig" and "orig-si" methods. 

### orig-si

```{r}
sival_simple <- rt_valdata("../output/area-error/orig_si/simple/")
sival_composite <- rt_valdata("../output/area-error/orig_si/composite/")
sival_frac <- rt_valdata("../output/area-error/orig_si/frac/")

bind_rows(composite = sival_composite, 
          frac = sival_frac, 
          simple = sival_simple, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method)

```

### orig

```{r}
origval_simple <- rt_valdata("../output/area-error/orig/simple/")
origval_composite <- rt_valdata("../output/area-error/orig/composite/")
origval_frac <- rt_valdata("../output/area-error/orig/frac/")

bind_rows(composite = origval_composite, 
          frac = origval_frac, 
          simple = origval_simple, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method)

```

Why is "simple" method different betwen orig and orig_si?


```{r}
simparea_o <- origval_simple %>% 
  filter(variable == "area_total")

simparea_s <- sival_simple %>% 
  filter(variable == "area_total")

list(orig = simparea_o, orig_si = simparea_s) %>% 
  bind_rows(.id = "method") %>% 
  ggplot(aes(x = node_id, y = pixc_err)) +
  geom_point(aes(color = method))

list(orig = simparea_o, orig_si = simparea_s) %>% 
  bind_rows(.id = "method") %>% 
  ggplot(aes(x = node_id, y = sigma_est)) +
  geom_point(aes(color = method))

```


Right, the estimates are the same, but area_tot_u is different, hence different scaled errors. But why would water_frac_uncert come into play for simple method? 

- Re-run simple versions, see if anything changes. 
- Play with use_fractional_inundation?

This is some wild stuff. Finding bugs in the code

- method coerced to "composite" when calculating uncertainty
- std_composite has wrong indent
- std_wd should be std_dw. 

Here's using different uncert methods (not all composite)


```{r}
origval_simple_new <- rt_valdata("../output/area-error/orig_new/simple/")
origval_composite_new <- rt_valdata("../output/area-error/orig_new/composite/")
origval_frac_new <- rt_valdata("../output/area-error/orig_new/frac/")

bind_rows(composite = origval_composite_new, 
          frac = origval_frac_new, 
          simple = origval_simple_new, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method)
```


```{r}
sival_simple_new <- rt_valdata("../output/area-error/orig_si_new/simple/")
sival_composite_new <- rt_valdata("../output/area-error/orig_si_new/composite/")
sival_frac_new <- rt_valdata("../output/area-error/orig_si_new/frac/")

bind_rows(composite = sival_composite_new, 
          frac = sival_frac_new, 
          simple = sival_simple_new, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method)
```


Reach-level results now. 

```{r}
basedir_new <- "../output/area-error/orig_si_new/frac/"
rtncfile_new <- path(basedir_new, "rt.nc")
rtncfile_truth_new <- path(basedir_new, "rt_gdem.nc")

reachdf_new <- rt_read(rtncfile_new, group = "reaches", keep_na_vars = TRUE)
truthdf_new <- rt_read(rtncfile_truth_new, group = "reaches", keep_na_vars = TRUE)

valmap <- c(wse = "wse_r_u", area_total = "area_tot_u", 
            slope = "slope_r_u", width = "width_u")

uncdf_new <- reachdf_new %>% 
  # glimpse() %>% 
  select(reach_id, wse_r_u, area_tot_u, slope_r_u, width_u) %>% 
  gather(key = "variable", value = "sigma_est", -reach_id) %>% 
  mutate(variable = plyr::mapvalues(variable, from = valmap, 
                                    to = names(valmap)))

estdf_new <- reachdf_new %>% 
  # glimpse() %>% 
  select(reach_id, wse, area_total, slope, width) %>% 
  gather(key = "variable", value = "est", -reach_id) %>% 
  left_join(uncdf_new, by = c("reach_id", "variable"))

reachvaldf_new <- truthdf_new %>% 
  select(reach_id, wse, area_total, slope, width) %>% 
  gather(key = "variable", value = "truth", -reach_id) %>% 
  left_join(estdf_new, by = c("reach_id", "variable")) %>% 
  mutate(pixc_err = est - truth, 
         relerr = (est - truth) / sigma_est)


rt_val_scatter(reachvaldf_new, 
               variables = c("width", "area_total", "wse", "slope"), 
               yvar = "relerr")
```


Leaflet maps now.

```{r}
simple_pix <- join_pixc("../output/area-error/orig_si_new/frac/", 
                        pixcname = "../../pixel_cloud_orig_si.nc")
simple_pix_gdem <- join_pixc("../output/area-error/orig_si_new/frac/", 
                             pcvname = "pcv_gdem.nc",
                        pixcname = "../../fake_pixc.nc")

library(leaflet)

badnodes_new <- badnodes(sival_frac_new, n = 4, which = "min")

pixdf1 <- simple_pix %>% 
  filter(node_index %in% badnodes_new) %>% 
  transmute(azimuth_index, range_index, node_index, reach_index,
            lat_med = latitude, lon_med = longitude,
            lat_wd = latitude_vectorproc, lon_wd = longitude_vectorproc,
            water_frac, water_frac_uncert,
            classification, fdr = false_detection_rate, 
            mdr = missed_detection_rate, Pw = prior_water_prob,
            pixel_area)
pixdf2 <- simple_pix_gdem %>% 
  filter(node_index %in% badnodes_new) %>% 
  transmute(azimuth_index, range_index, node_index, reach_index,
            lat_gdem = latitude, lon_gdem = longitude, pixel_area)

classpal <- colorFactor("Dark2", pixdf1$classification)

leaflet_scaled <- leaflet() %>% 
  addTiles() %>% 
  addCircles(~lon_gdem, ~lat_gdem, 
             radius = ~sqrt(pixel_area / pi),
             fillColor = "black", fillOpacity = 1, stroke = FALSE, 
             data = pixdf2) %>% 
  addCircles(~lon_wd, ~lat_wd, radius = ~sqrt(pixel_area / pi * water_frac),
             fillColor = ~classpal(classification), stroke = FALSE, 
             fillOpacity = 0.6, data = pixdf1, 
             popup = ~paste("node: ", node_index))

leaflet_scaled
```

Add an "allfrac" (all classes use water fraction) and rerun. 

```{r}
sival_simple_new <- rt_valdata("../output/area-error/orig_si_new/simple/")
sival_composite_new <- rt_valdata("../output/area-error/orig_si_new/composite/")
sival_frac_new <- rt_valdata("../output/area-error/orig_si_new/frac/")
sival_allfrac_new <- rt_valdata("../output/area-error/orig_si_new/allfrac/")


bind_rows(composite = sival_composite_new, 
          frac = sival_frac_new, 
          allfrac = sival_allfrac_new,
          simple = sival_simple_new, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method, scales = "free_y")
```

I think this is good for now. Next challenge: quickly apply the same analysis to multiple runs. 