---
title: "notebook20190204"
author: "Mark Hagemann"
date: "2/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Working with netcdf output from running RiverObs scripts. 

I brainstormed some validations to do in today's work journal. Start with reach scale. 

```{r}
sac_rt <- nc_open("../output/out_rt.nc") # rivertile netcdf from Sac Pixc

# sac_rt$groups[[3]]
# sac_rt$dim$`reaches/reaches`
sac_rt$var$`nodes/time`$units

sacvars <- names(sac_rt$var)
# sacvars
reachvars <- sacvars[grepl("^reaches/", sacvars)]
reachvars <- reachvars[!grepl("rch_id_", reachvars, fixed = TRUE)] # matrices/I don't need these
reachvars_short <- splitPiece(reachvars, "/", 2, fixed = TRUE)

reachvals_list <- reachvars %>% 
  map(~as.vector(ncvar_get(nc = sac_rt, varid = .))) %>% 
  setNames(reachvars_short)

nacols <- map_lgl(reachvals_list, ~(sum(!is.na(.)) == 0))

reachvals_df <- as.data.frame(reachvals_list)[, !nacols]

nc_close(sac_rt)
```


```{r}
glimpse(reachvals_df)
```

```{r}
library(leaflet)

leaflet(reachvals_df) %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~p_longitud, lat = ~p_latitud, radius = 2)
```

Fine. Next, do nodes. 

```{r}
sac_rt <- nc_open("../output/out_rt.nc") # rivertile netcdf from Sac Pixc

# sac_rt$groups[[3]]
# sac_rt$dim$`reaches/reaches`

sacvars <- names(sac_rt$var)
# sacvars
nodevars <- sacvars[grepl("^nodes/", sacvars)]

nodevars_short <- splitPiece(nodevars, "/", 2, fixed = TRUE)

nodevals_list <- nodevars %>% 
  map(~as.vector(ncvar_get(nc = sac_rt, varid = .))) %>% 
  setNames(nodevars_short)

# map_int(nodevals_list, ~length(.)) %>% sort()

nacols <- map_lgl(nodevals_list, ~(sum(!is.na(.)) == 0))

nodevals_df <- as.data.frame(nodevals_list)[, !nacols]

nc_close(sac_rt)
```

```{r}
glimpse(nodevals_df)
```

```{r}
leaflet(nodevals_df) %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, radius = 2)
```


Next get a truth for node level

```{r}
sac_rt <- nc_open("../output/gdemrt.nc") # rivertile netcdf from Sac Pixc

# sac_rt$groups[[3]]
# sac_rt$dim$`reaches/reaches`

sacvars <- names(sac_rt$var)
# sacvars
nodevars <- sacvars[grepl("^nodes/", sacvars)]

nodevars_short <- splitPiece(nodevars, "/", 2, fixed = TRUE)

nodetruth_list <- nodevars %>% 
  map(~as.vector(ncvar_get(nc = sac_rt, varid = .))) %>% 
  setNames(nodevars_short)

# map_int(nodetruth_list, ~length(.)) %>% sort()

nacols <- map_lgl(nodetruth_list, ~(sum(!is.na(.)) == 0))

nodetruth_df <- as.data.frame(nodetruth_list)[, !nacols]

nc_close(sac_rt)
```


Compare vals to truth

```{r}
dim(nodetruth_df)
dim(nodevals_df)

glimpse(nodevals_df)


```

See which node_id's are missing from the different outputs.

```{r}

valmisslocs <- setdiff(nodetruth_df$node_id, nodevals_df$node_id)
trumisslocs <- setdiff(nodevals_df$node_id, nodetruth_df$node_id)

leaflet(nodevals_df) %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude, radius = 2, color = "blue") %>% 
  addCircleMarkers(data = filter(nodevals_df, node_id %in% trumisslocs), 
                   color = "blue") %>% 
  addCircleMarkers(data = filter(nodetruth_df, node_id %in% valmisslocs),
                   color = "red")
  
```


OK, pixc is just missing nodes at the end. 

Next do that comparison. What variables do I want?

```{r}
glimpse(nodevals_df)
keepvars <- c("node_id", "time", "latitude", "longitude", 
              "latitude_u", "longitud_u", "height", "height_u", 
              "width", "width_u", "area_detct", "area_det_u", 
              "area_total", "area_tot_u", "area_of_ht", "n_good_pix")

# This one just for truth comparison (i.e. vars to validate)
glimpse(nodetruth_df)
keepvars_tru <- c("node_id", "time", "latitude", "longitude", 
              "height", "width", "area_detct", "area_total", "area_of_ht")
```



```{r}
node_df <- nodevals_df[keepvars] %>% 
  mutate(time = round(time, digits = -3)) %>% 
  full_join(mutate(nodetruth_df[keepvars_tru], 
                   time = round(time, digits = -3)),
            by = c("node_id", "time"))

glimpse(node_df)

node_df %>% 
  filter(!(node_id %in% valmisslocs), 
         !(node_id %in% trumisslocs)) %>% 
  glimpse()
```


Make some plots.

```{r}
valdf_node %>% 
  ggplot(aes(x = h_err_scale)) + 
  geom_histogram()

valdf_node %>% 
  ggplot(aes(x = lat_err_scale)) + 
  geom_histogram() +
  xlim(-500, 500)

valdf_node %>% 
  ggplot(aes(x = lon_err_scale)) + 
  # xlim(-50, 50) +
  coord_cartesian(
    # xlim = c(-20, 20)
    xlim = c(-50, 50)
  ) +
  geom_histogram(
    # binwidth = 2.5
    binwidth = 5
  )
```

I'd love a plot of errors versus sensitivity, but I don't have sensitivity at feature scale. For now think about how to do error comparison more systematically. Start with a better data structure:

```{r}
errdf_node <- node_df %>% 
  transmute(node_id, time,
            h = (height.x - height.y),
            w = width.x - width.y,
            adet = area_detct.x - area_detct.y,
            atot = area_total.x - area_total.y,
            lat = latitude.x - latitude.y,
            lon = longitude.x - longitude.y)

uncdf_node <- node_df %>% 
  transmute(node_id, time,
            h = height_u,
            w = width_u,
            adet = area_det_u,
            atot = area_tot_u,
            lat = latitude_u,
            lon = longitud_u)

relerrdf_node <- (errdf_node / uncdf_node) %>% 
  mutate(node_id = errdf_node$node_id,
         time = errdf_node$time) %>% 
  gather(key = "variable", value = "value", -node_id, -time) %>%
  glimpse()
  

```


Now I can quickly plot:

```{r}
relerrdf_node %>% 
  filter(abs(value) < 100) %>% 
  ggplot(aes(x = value)) + 
  geom_histogram() + 
  facet_wrap(~variable, scales = "free")
```

I like that. I think it's a good first-level plot. I can think of things to parse out from this and compare, but leave that for now. Actually, real quick, add a non-rleative error plot. 

```{r}
errdf_node %>% 
  gather(key = "variable", value = "value", -node_id, -time) %>%
  # glimpse() %>% 
  ggplot(aes(x = value)) + 
  geom_histogram() + 
  facet_wrap(~variable, scales = "free")
  
```

Next I want to see if I can get error bars to show up in a leaflet plot. This would mean using polylines. How to specify those in a data.frame?

- I may need to use sf package and have a geometry column. Try it out!

```{r}
library(sf)

linegeom <- nodevals_df %>% 
  dplyr::select(reach_id:height_u) %>% 
  mutate(lat_min = latitude - 2 *latitude_u,
         lat_max = latitude + 2 *latitude_u,
         lon_min = longitude - 2 * longitud_u,
         lon_max = longitude + 2 *longitud_u) %>% 
  split(f = 1:nrow(.)) %>% 
  map(~st_multilinestring(
    list(matrix(c(.$longitude, .$lon_max, .$longitude, .$lon_min, 
             .$longitude, .$lat_max, .$latitude, .$lat_min, 
             .$latitude, .$lat_max
             ), ncol = 2, byrow = FALSE)))) %>% 
  st_sfc()

nodevals_sf <- nodevals_df %>% 
  mutate(geometry = linegeom) %>% 
  st_as_sf()
  
```

Not clear how to do this. And anyway it's almost time for my telecon for uncertainty stuff. Leave as a todo. 

Next plot: scatterplot showing squared error vs. squared uncertainty. Mean shold follow a 1:1 line.

```{r}
bounddf_node <- list(err = errdf_node, unc = uncdf_node) %>% 
  bind_rows(.id = "qty") %>% 
  gather(key = "variable", value = "value", -node_id, -time, -qty) %>% 
  spread(key = "qty", value = "value") %>% 
  na.omit()

bounddf_node %>% 
  ggplot(aes(x = unc^2, y = err^2)) + 
  geom_point() + 
  facet_wrap(~variable, scales = "free") + 
  scale_x_log10() + scale_y_log10() + 
  geom_abline(slope = 1, intercept = 0)
```

Looks like lat and lon are not being treated right. The others are too good--we should be looking at a random quantity; these look deterministic. Could that just be the impact of log space? I think not. 

- What's up with the low outlier in height? Both uncertainty and error are super low. 


Now more practice with sf.Editing the chunk above. Here's from the st_as_sf help page. 

```{r}
pt1 = st_point(c(0,1))
pt2 = st_point(c(1,1))
st_sfc(pt1, pt2)
d = data.frame(a = 1:2)
d$geom = st_sfc(pt1, pt2)
df = st_as_sf(d)
d$geom = c("POINT(0 0)", "POINT(0 1)")
df = st_as_sf(d, wkt = "geom")
d$geom2 = st_sfc(pt1, pt2)
st_as_sf(d) # should warn
data(meuse, package = "sp")
meuse_sf = st_as_sf(meuse, coords = c("x", "y"), crs = 28992, agr = "constant")
```


OK, I've got something working (I think). See if leaflet can handle it.

```{r}
leaflet() %>% 
  addTiles() %>% 
  # addCircleMarkers(radius = 3, data = nodevals_df) %>%
  addPolylines(stroke = 1, data = nodevals_sf[1:2, ], color = "red")



sf::as_Spatial(linegeom[1:2]) %>%  #plot()
  leaflet() %>% 
# leaflet(linegeom) %>% 
  addPolylines(weight = 0.1)
```


Not clear why that's not plotting. Anyway, it's time to switch gears. 

