---
title: "notebook20190404"
author: "Mark Hagemann"
date: "4/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Beginning a prototype for uncertainty validation across characteristics of node, reach data. Copying from simplenote:

- viewing geometry* 
	- cross-track distance
	- npix_cross, npix_along (node width/area only)
	- flow angle / median of flow angle--width/area height via layover
- layover condition (noise background for land and water)
- hydraulic condition--e.g. variability in inundated area (HOW TO QUANTIFY?)
	- percentile of flow
	- flow/(mean flow), or log(flow) - mean(log(flow)) 
- magnitude of slope*, width*, area*
	- ditto for magnitude of uncertainty (will be correlated with magnitude of variable)
- number of pixels/nodes*
- Uncertainty estimation method (height, height2, width/area, slope)
- Data product--reach or node

- Starting with scatterplots. 
    - y-axis: relative error
    - x-axis: different variables above
        - x-track distance
        - n pixels
        - log(flow) - mean(log(flow)) (use high, low flow condition for now)
    - Color: other variables
        - land-water contrast (dB)
        - hydrologic condition (high flow, low flow)
    - angle: node orientation relative to track
    - One set per variable (height, height2, area)
    - repeat for reaches, but they'll be less interesting. 

```{r}
devtools::load_all("../../rivertile")
diri <- "~/Documents/swot-error/output/sac18"

valdf1 <- rt_valdata(diri, flag_out_nodes = TRUE) %>% 
  mutate(rel_sigma = sigma_est / pixc_val, rel_val = pixc_val / sigma_est)

xvars <- c("xtrk_dist", "n_good_pix", "pixc_val", "sigma_est", "rel_sigma", "rel_val")

plotdf1 <- xvars %>% 
  map(~rt_val_scatter(valdf1, 
                      variables = c("width", "area_total",
                                    "height", "height2"),
                      xvar = ., yvar = "relerr", 
                      plot = FALSE)) %>% 
  setNames(xvars) %>% 
  bind_rows(.id = "xvar")


var1 <- "area_total"
plotdf1 %>% 
  filter(variable == var1) %>% 
  ggplot(aes(x = xval, y = yval)) + 
  geom_point() +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var1)

var2 <- "height"
plotdf1 %>% 
  filter(variable == var2) %>% 
  ggplot(aes(x = xval, y = yval)) + 
  geom_point() +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var2)

var3 <- "height2"
plotdf1 %>% 
  filter(variable == var3) %>% 
  ggplot(aes(x = xval, y = yval)) + 
  geom_point() +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var3)
```

Next I need to add in inter-run variables: hydrologic condition, noise contrast. These I can only get from the roruns.csv file. Find a way to elegantly incorporate that!

```{r}
roruns <- read.csv("../src/roruns.csv", stringsAsFactors = FALSE)

glimpse(roruns)
```

Start with hydro condition--easiest to incorporate. Rather than overthinking how to select runs automatically, just manually specify the run number and fish out the results using the roruns object. 

```{r}
roruns[18, ] %>% glimpse()

romatch <- function(rorow, vary) {
  relcols <- c("priordb", "case", "pass", "bndry_cond", "smearing",
               "land_sig0", "water_sig0", "gdem_name")
  keepcols <- setdiff(relcols, vary)
  rowstrings <- apply(roruns[, keepcols], 1, paste0, collapse = "")
  matchrow <- paste0(roruns[rorow, keepcols], collapse = "")
  out <- setdiff(which(matchrow == rowstrings), rorow)
  out
}

romatch(18, c("bndry_cond"))
romatch(18, c("land_sig0", "water_sig0"))
romatch(18, c("bndry_cond", "land_sig0", "water_sig0"))
```

That's a handy, albeit not super elegant, function. With it I can provide a row number and axis to vary and get the row numbers of runs that only vary along the specified axis/es. 

Now a directory retrieval function. 

```{r}
rodir <- function(rorow) {
  basedir <- "~/Documents/swot-error/"
  out <- normalizePath(fs::path(basedir, roruns$outdir[rorow]))
  names(out) <- roruns$outno[rorow]
  out
}
rodir(18)
romatch(18, c("land_sig0", "water_sig0")) %>% rodir()
```

Nice! Now I can combine these to fill out my scatterplots. 

```{r}
valdf2 <- c(18, romatch(18, "bndry_cond")) %>% 
  setNames(., nm = .) %>% 
  rodir() %>% 
  map(~rt_valdata(dir = ., group = "nodes", flag_out_nodes = TRUE)) %>% 
  bind_rows(.id = "outno") %>% 
  mutate(outno = as.numeric(outno)) %>% 
  left_join(roruns, by = "outno") %>% 
  mutate(rel_sigma = sigma_est / pixc_val, rel_val = pixc_val / sigma_est)

xvars <- c("xtrk_dist", "n_good_pix", "pixc_val", "sigma_est", "rel_sigma", "rel_val")

plotdf2 <- xvars %>% 
  map(~rt_val_scatter(valdf2, 
                      variables = c("width", "area_total",
                                    "height", "height2"),
                      xvar = ., yvar = "relerr", 
                      plot = FALSE)) %>% 
  setNames(xvars) %>% 
  bind_rows(.id = "xvar")


var1 <- "area_total"
plotdf2 %>% 
  filter(variable == var1) %>% 
  ggplot(aes(x = xval, y = yval, color = bndry_cond)) + 
  geom_point(alpha = 0.3) +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var1)
```

Nice! Shall I attempt a sigma0 comparison?

```{r}
valdf3 <- c(18, romatch(18, c("water_sig0", "land_sig0"))) %>% 
  setNames(., nm = .) %>% 
  rodir() %>% 
  map(~rt_valdata(dir = ., group = "nodes", flag_out_nodes = TRUE)) %>% 
  bind_rows(.id = "outno") %>% 
  mutate(outno = as.numeric(outno)) %>% 
  left_join(roruns, by = "outno") %>% 
  mutate(rel_sigma = sigma_est / pixc_val, rel_val = pixc_val / sigma_est)

xvars <- c("xtrk_dist", "n_good_pix", "pixc_val", "sigma_est", "rel_sigma", "rel_val")

plotdf3 <- xvars %>% 
  map(~rt_val_scatter(valdf3, 
                      variables = c("width", "area_total",
                                    "height", "height2"),
                      xvar = ., yvar = "relerr", 
                      plot = FALSE)) %>% 
  setNames(xvars) %>% 
  bind_rows(.id = "xvar")


var1 <- "area_total"
plotdf3 %>% 
  filter(variable == var1) %>% 
  mutate(sig0 = paste(water_sig0, land_sig0, sep = ",")) %>% 
  ggplot(aes(x = xval, y = yval, color = sig0)) + 
  geom_point(alpha = 0.3) +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var1)

var2 <- "height"
plotdf3 %>% 
  filter(variable == var2) %>% 
  mutate(sig0 = paste(water_sig0, land_sig0, sep = ",")) %>% 
  ggplot(aes(x = xval, y = yval, color = sig0)) + 
  geom_point(alpha = 0.3) +
  facet_wrap(~xvar, scales = "free_x") +
  ylab("relative error") + xlab("") +
  ggtitle(var2)
```

Based on the above plots, try a simple adjustment using a linear fit of relerr ~ sigma_est.

```{r}

var1 <- "area_total"
plotdf2 %>% 
  filter(variable == var1, bndry_cond == 220,
         node_id != 573) %>% 
  dplyr::select(node_id, yval, xvar, xval, bndry_cond) %>%
  spread(key = xvar, value = xval) %>% #pairs()
  lm(yval ~ sigma_est + n_good_pix, .) %>% 
  summary()

```

