---
title: "node validation writeup"
author: "Mark Hagemann"
date: "2/11/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(leaflet)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
opts_knit$set(root.dir = "~/Documents/swot-error/")
```

```{r}
library(ProjectTemplate)
load.project()
valdata <- rt_valdata("output/sac04", group = "nodes")

# valdata <- valdata %>% dplyr::filter(node_id != 3249122) %>% 
#   dplyr::select(reach_id:sigma_est)

```

## Motivation

SWOT data products containing estimates of error uncertainty will need to make thes estimates *a priori*, at least at first. This requires some knowledge of the phenomena that lead to imprecision, and a suitable quantificaiton of this imprecision. 

While the true performance of SWOT uncertainty models will be unresolved until actual observations are made from the satellite, we can get some sense of their performance in a controlled range of conditions using simulated pixel cloud data. This report presents a first-cut validation of uncertainty model performance for a single siumulated pixel cloud on the Sacramento River model. 

## Methods

Two rivertile netcdfs were generated using the Sacramento pixel_cloud from the SWOT instrument simulator

## Results



### Summary statistics

Table #### shows bias, variance, relative bias, and relative standard deviation for all 264 nodes in the rivertile produced by RiverObs.

```{r}
valdata %>% 
  # glimpse() %>% 
  mutate(pixc_relerr = pixc_err / sigma_est) %>% 
  group_by(variable) %>% 
  summarize(bias = mean(pixc_err),
            sd = sd(pixc_err),
            rel_bias = mean(pixc_relerr),
            rel_sd = sd(pixc_relerr)) %>% 
  mutate(rmse = sqrt(bias^2 + sd^2), 
         rel_rmse = sqrt(rel_bias^2 + rel_sd^2)) %>% 
  kable(digits = 2)
  
```


### Coverage rates

```{r}

covfun <- function(x, sigma, pctl) {
  pctl <- pctl / 100
  bnd <- -qnorm((1 - pctl) / 2, mean = 0, sd = 1)
  numin <- sum(abs(x / sigma) <= bnd)
  out <- numin / length(x) * 100
  out
}

valdata %>% 
  # glimpse() %>% 
  group_by(variable) %>% 
  summarize(
    `50` = covfun(pixc_err, sigma_est, 50),
    `75` = covfun(pixc_err, sigma_est, 75),
    `90` = covfun(pixc_err, sigma_est, 90),
    `95` = covfun(pixc_err, sigma_est, 95),
    `99` = covfun(pixc_err, sigma_est, 99)
    ) %>% 
  kable(digits = 2)

# Now with bias removed
valdata %>% 
  # glimpse() %>% 
  group_by(variable) %>% 
  mutate(pixc_err = pixc_err - mean(pixc_err, na.rm = TRUE)) %>% 
  summarize(
    `50` = covfun(pixc_err, sigma_est, 50),
    `75` = covfun(pixc_err, sigma_est, 75),
    `90` = covfun(pixc_err, sigma_est, 90),
    `95` = covfun(pixc_err, sigma_est, 95),
    `99` = covfun(pixc_err, sigma_est, 99)
    ) %>% 
  kable(digits = 2)

```

### Scatterplots

```{r}
gg_scatter1 <- valdata %>% 
  ggplot(aes(x = sigma_est^2, y = pixc_err^2)) + 
  geom_point() + 
  scale_x_log10() + scale_y_log10() +
  geom_abline(slope = 1, intercept = 0) +
  facet_wrap(~variable, scales = "free")

gg_scatter1
```

### Spatial trends (downstream)

```{r}
valdata %>% 
  ggplot(aes(x = node_id, y = pixc_err)) + 
  geom_point() + 
  facet_wrap(~variable, scales = "free") + 
  stat_smooth()
```


### Normal quantil-quantile plots

```{r}
valdata %>% 
  ggplot(aes(sample = pixc_err / sigma_est)) + 
  geom_qq() +
  geom_qq_line() +
  facet_wrap(~variable, scales = "free")
```

