---
title: "Sac width, area bias comparison"
author: "Mark Hagemann"
date: "2/20/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

opts_knit$set(root.dir = "../")
```

```{r}
library(ProjectTemplate)
library(leaflet)
load.project()
```


This document compares width and area bias using 2 different Sacramento simulated cases:

- Old one, sent 1/25/2019
- New one, -5dB land, 10 dB water, 220 flow condition

Both were run using Rui's updated prior db, and using the same RiverObs version.

Errors are relative to gdem fake pixel cloud. 


## Error statistics

The new version has a more centered mode and less bias, but larger outliers. 

```{r}
list(old_sacfile = rt_val_hist("output/sac02", scale = FALSE, vars = "width")$data,
  new_sacfile = rt_val_hist("output/sac15", scale = FALSE, vars = "width")$data) %>% 
  bind_rows(.id = "version") %>% 
  group_by(version) %>% 
  summarize(bias = mean(pixc_err), median = median(pixc_err)) %>% 
  kable()
```


## Error histograms

These are raw errors (not centered or scaled at all). 

```{r}
rt_val_hist("output/sac02", scale = FALSE, vars = c("width", "area_total")) + 
  ggtitle("Old Sac file")

rt_val_hist("output/sac15", scale = FALSE, vars = c("width", "area_total")) +
  ggtitle("New Sac file")
```


### Zoomed to same x-axis limits

Note that some outliers in the new Sac errors are removed from this plot:

```{r}

rt_val_hist("output/sac02", scale = FALSE, vars = "width") + xlim(-100, 200) +
    ggtitle("Old Sac file")

rt_val_hist("output/sac15", scale = FALSE, vars = "width") + xlim(-100, 200) +
    ggtitle("New Sac file")

```

## Maps showing 4 nodes with the worst absolute width errors

Locations of pixcvec pixels associated with the worst-width-error nodes. Blue is from the pixel_cloud, red is from the fake gdem pixel_cloud

### Old Sac file

Note that all these errors are overpredictions (high outliers)

```{r}
valdata <- rt_valdata("output/sac02", group = "nodes") %>% 
  dplyr::filter(variable != "area_detct") 

badnodes <- valdata %>% 
  dplyr::filter(variable == "width") %>% 
  arrange(desc(abs(pixc_err))) %>% 
  `[[`("node_id") %>% 
  `[`(1:4)

pcvdata <- pixcvec_read("output/sac02/pcv.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)

pcvdata_gdem <- pixcvec_read("output/sac02/pcv_gdem.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)


pcvdata  %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, popup = ~format(node_index)) %>% 
  addCircleMarkers(radius = 1, color = "red", data =pcvdata_gdem)

```


### New Sac file

One of these errors is a low-outlier. 3 out of 4 of these are not even in the old Sac file's spatial coverage. 

```{r}
valdata <- rt_valdata("output/sac15", group = "nodes") %>% 
  dplyr::filter(variable != "area_detct") 

badnodes <- valdata %>% 
  dplyr::filter(variable == "width") %>% 
  arrange(desc(abs(pixc_err))) %>% 
  `[[`("node_id") %>% 
  `[`(1:4)

pcvdata <- pixcvec_read("output/sac15/pcv.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)

pcvdata_gdem <- pixcvec_read("output/sac15/pcv_gdem.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)


pcvdata  %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, popup = ~format(node_index)) %>% 
  addCircleMarkers(radius = 1, color = "red", data =pcvdata_gdem)

```
