---
title: 'Sac width compare v2: dilation'
author: "Mark Hagemann"
date: "2/21/2019"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

opts_knit$set(root.dir = "../")
```

```{r, cache = FALSE}
library(ProjectTemplate)
library(leaflet)
load.project()
devtools::load_all("../rivertile")
```

Recall the following issue, where large outliers occurred in the node-level width errors. 


```{r}
ridnode <- function(gg) {
  gg$data <- dplyr::filter(gg$data, node_id != 573)
  gg
}

dir15 <- "output/sac15"
# rt_valdata(dir15) %>% dplyr::filter(variable == "width") %>% arrange(pixc_err)
rt_val_hist(dir15, vars = c("width")) %>% 
  ridnode()
```

These are due to locations where the finer-resolution gdem pixc water search stops before it should, as in the following plot of underlying pixcvec pixels for 2 nodes (gdem-derived red, pixc-derived blue):


```{r}
plotnodes <- c(290, 303)
val_map_node(dir15, nodes = plotnodes)
```

Brent implemented a fix wherein RiverObs has an option giving the number of iterations for a binary dilation before segmentation. Or something. Here's the result for these nodes after setting this option to 1:

```{r}
val_map_node(dir15, nodes = plotnodes, pcv2 = "pcv_gdem_dil1.nc")
```

The southern node gdem expanded slightly, but it's still a much smaller width--especially in the northern node. 

What if we set the dilation option to 2?

```{r}
val_map_node(dir15, nodes = plotnodes, pcv2 = "pcv_gdem_dil2.nc")
```

That's certainly closer! How does that make the overall histogram of node-level height errors look?

```{r}
rt_val_hist(dir15, vars = c("width"), gdname = "rt_gdem_dil2.nc") %>% 
  ridnode()

```

It's fixed some high outliers, but added some pretty gnarly low outliers. Observe:

```{r}
valdata1 <- rt_valdata(dir15)
valdata2 <- rt_valdata(dir15, gdname = "rt_gdem_dil1.nc")
valdata3 <- rt_valdata(dir15, gdname = "rt_gdem_dil2.nc")
valdata4 <- rt_valdata(dir15, rtname = "rt_dil.nc", gdname = "rt_gdem_dil2.nc")


# val_map_node(dir15, nodes = badnodes(valdata1))
# val_map_node(dir15, nodes = badnodes(valdata2), 
#              pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil1.nc")
val_map_node(dir15, nodes = badnodes(valdata3, which = "min", n = 2), 
             pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil2.nc")
# val_map_node(dir15, nodes = badnodes(valdata4), 
#              pcv1 = "pcv_dil.nc", pcv2 = "pcv_gdem_dil2.nc")
```

That's actually both nodes--they're adjacent. 

Maybe adding a dilation option (of 1) to the original pixel cloud will help. 

```{r}
val_map_node(dir15, nodes = badnodes(valdata3, which = "min", n = 2),
             pcv1 = "pcv_dil.nc", pcv2 = "pcv_gdem_dil2.nc")
```

Sure enough. Here is the nodel-level width error histogram using a dilation option of 1 for the pixel_cloud and 2 for the gdem truth pixel_cloud. 


```{r}
val4 <- rt_val_hist(dir15, vars = c("width"), 
                    rtname = "rt_dil.nc", gdname = "rt_gdem_dil2.nc") %>% 
  ridnode()
val4
```

Now high outliers agian! Here are the 4 worst high-oulier nodes:

```{r}
val_map_node(dir15, nodes = badnodes(valdata4, which = "max", n = 4),
             pcv1 = "pcv_dil.nc", pcv2 = "pcv_gdem_dil2.nc")
```


## Conclusion

The pre-segmentation dilation option does what it's supposed to, but it is a coarse adjustment with often adverse consequences. It's hard for me to see how to tune this a priori to get the best results. 
