---
title: "Validation Objects"
author: "Mark Hagemann"
date: "5/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document creates datasets, figures, tables, and other objects to be used in the validation manuscript project. 


Function to put objects into manuscript project subdirectory.

```{r}
push2manuscript <- function(object) {
  objstring <- rlang::as_string(enexpr(object))
  save(list = objstring, 
       file = sprintf("~/Documents/manuscript-uncval/robjs/%s.RData",
                      objstring))
  if (inherits(object, "gg")) print(object)
}
foo <- "abc"
push2manuscript(foo)

```

Function to save ggplots using a methodical naming convention.

```{r}
save_plot <- function(plot,
                      type, scale = c("node", "reach"), agg = c("composite", "frac", "simple"),
                      noise = c("low", "high"), ...) {
  scale <- match.arg(scale)
  agg <- match.arg(agg)
  noise <- match.arg(noise)
  outname <- sprintf("~/Documents/manuscript-uncval/fig/%s-%s-%s-%s.png", type, scale, agg, noise)
  
  ggsave(filename = outname, plot = plot, ...)
  knitr::include_graphics(outname, dpi = 300)
  # message(outname)
}
```



## Setup

### Location of validation data, including which directories to use

```{r}
# varyvars <- c("pass", "day", "gdem_name")
# romatch(54, vary = varyvars)

valnums <- ro_manifest() %>% 
  filter(notes == "manuscript") %>% 
  filter(outno != 74, outno != 87) %>% # Remove this if/when the run is fixed.
  pull(outno)
valdirs_simple <- rodir(valnums, "simple")
valdirs_composite <- rodir(valnums, "composite")
valdirs_frac <- rodir(valnums, "frac")

ro_manifest() %>% 
  filter(outno %in% valnums)
``` 

### Node valdation data.frames

```{r}

keepvars <- c("run", "day", "pass", "reach_id", "node_id", 
              "variable", "pixc_val", "gdem_val", "pixc_err", "sigma_est", 
              "xtrk_dist", "n_good_pix", "land_sig0", "refdem")

valdf_simple <- rt_valdata_multi(runnos = valnums, group = "nodes", "simple") %>% 
  mutate(xtrk_dist = abs(xtrk_dist)) %>% 
  select(!!keepvars)
valdf_composite <- rt_valdata_multi(runnos = valnums, group = "nodes", "composite") %>% 
  mutate(xtrk_dist = abs(xtrk_dist)) %>% 
  select(!!keepvars)
valdf_frac <- rt_valdata_multi(runnos = valnums, group = "nodes", "frac") %>% 
  mutate(xtrk_dist = abs(xtrk_dist)) %>% 
  select(!!keepvars)

valdf_master <- list(simple = valdf_simple,
                     composite = valdf_composite,
                     frac = valdf_frac) %>% 
  bind_rows(.id = "agg")

valdf_gdem <- valdf_master %>% filter(refdem == "GDEM")
valdf_srtm <- valdf_master %>% filter(refdem == "SRTM")


# spread by variable for estimate, truth, sigma_est
pixcvaldf <- valdf_master %>% 
  select(run, agg, reach_id, node_id, pixc_val, variable) %>% 
  spread(key = "variable", value = "pixc_val")
gdemvaldf <- valdf_master %>% 
  select(run, agg, reach_id, node_id, gdem_val, variable) %>% 
  spread(key = "variable", value = "gdem_val")
sigmaestdf <- valdf_master %>% 
  select(run, agg, reach_id, node_id, sigma_est, variable) %>% 
  spread(key = "variable", value = "sigma_est")

push2manuscript(pixcvaldf)

push2manuscript(valdf_master)

push2manuscript(gdemvaldf)
push2manuscript(sigmaestdf)

```


### Reach validation

```{r}

reachvaldf_simple <- rt_valdata_multi(valnums, group = "reaches", "simple")
reachvaldf_composite <- rt_valdata_multi(valnums, group = "reaches", "composite")
reachvaldf_frac <- rt_valdata_multi(valnums, group = "reaches", "frac")
```


### Flow info

```{r}
library(lubridate)
flowdf <- read.csv("../data/sac_flow.csv", stringsAsFactors = FALSE) %>% 
  transmute(date = lubridate::ymd_hm(DATE.TIME, tz = "America/Los_Angeles"),
            date = as.Date(date),
            flow = as.numeric(VALUE),
            logdev = log(flow) - mean(log(flow), na.rm = TRUE))
cdffun <- ecdf(na.omit(flowdf$flow))
flowdf$qtl <- cdffun(flowdf$flow)

runinfo <- ro_manifest() %>% 
  filter(outno %in% valnums)

cdfdf <- data.frame(
  flow = exp(seq(log(1000), log(max(flowdf$flow, na.rm = TRUE)), 
                 length.out = 200))
) %>% 
  mutate(cdf = cdffun(flow))

flowdf$cdf <- cdffun(flowdf$flow)
```


## Tables

### Validation data summary

```{r}
# Number of nodes per run
rundates <- ymd(sprintf("2009%04d", runinfo$day))
rundatedf <- data.frame(pass = runinfo$pass, 
                        date = rundates, day = as.factor(runinfo$day)) %>% 
  unique() %>% 
  mutate(flow = flowdf$flow[match(date, flowdf$date)],
         flow_pctile = cdffun(flow) * 100)
run_tbl <- pixcvaldf %>% 
  left_join(runinfo, by = c(run = "outno")) %>% 
  group_by(pass) %>% 
  summarize(n_nodes = n()) %>% 
  left_join(rundatedf)
kable(run_tbl)
push2manuscript(run_tbl)

```

### Validation results, part 1

```{r}
# valvars <- c("height", "height2", "slope", "width", "area_total")
valvars <- c("wse", "slope", "width") #, "area_total")
```

Summary stats

```{r}
sumstatdf <- valdf_master %>% 
  mutate(relerr = pixc_err / sigma_est) %>% 
  dplyr::filter(variable %in% valvars) %>% 
  group_by(variable) %>% 
  summarize(bias = mean(relerr), sd = sd(relerr)) %>% 
  mutate(rmse = sqrt(bias^2 + sd^2))
push2manuscript(sumstatdf)
kable(sumstatdf, digits = 2)
```


Coverage stats

```{r}
covdf <- valdf_gdem %>% 
  dplyr::filter(variable %in% valvars) %>% 
  val_coverage()

push2manuscript(covdf)
```


Hypothesis tests

```{r}
node_ht <- valdf_gdem %>% 
  dplyr::filter(variable %in% valvars) %>% 
  rt_hyptest(sides = 2)

node_ht_db <- valdf_gdem %>% 
  dplyr::filter(variable %in% valvars) %>% 
  rt_hyptest(debias = TRUE)

node_ht$pval_debias <- node_ht_db$pval

push2manuscript(node_ht)

```

Hypothesis test--subset

```{r}
node_htsset <- valdf_gdem %>% 
  dplyr::filter(day != 220, variable %in% valvars) %>% 
  rt_hyptest(sides = 2)

node_htsset_db <- valdf_gdem %>% 
  dplyr::filter(day != 220, variable %in% valvars) %>% 
  rt_hyptest(debias = TRUE)

node_htsset$pval_debias <- node_ht109_db$pval

push2manuscript(node_htsset)

kable(node_htsset, format.args = list(scientific = -2))
```


## Figures

### Map of passes, locations

Data

```{r}
pass_mapdf <- function(pixcnc, outlen = 100) {
  dfin <- pixc_read(pixcnc, group = "tvp")
  nrin <- nrow(dfin)
  sampint <- floor(nrin / outlen)
  sampinds <- seq(1, nrin, by = sampint)
  out <- dfin[c("time", "latitude", "longitude")][sampinds, ]
  out
}

passmapdf <- paste0(valdirs_simple, "/pixel_cloud.nc") %>% 
  map(pass_mapdf) %>% 
  setNames(valnums) %>% 
  bind_rows(.id = "run") %>% 
  mutate(outno = as.numeric(run)) %>% 
  left_join(ro_manifest(), by = "outno")

# # Number of times each node is observed across validation data.
# nodecov <- valdf_gdem %>% 
#   mutate(reach_id = as.factor(reach_id)) %>% 
#   filter(variable == "latitude") %>% 
#   group_by(node_id, reach_id) %>% 
#   summarize(n = as.factor(n())) %>% 
#   ungroup()
```

Prior db data

```{r}
# ncloc <- path("D:/data/SWOT-prior/PriorDistributionFolder/netcdfV4/", "NA07.nc")
ncloc <- "~/Documents/swot-error/data/priordb-update/Sac_sample_db15.nc"

nodemapdf <- priornode_read(ncloc, seq(min(valdf_master$node_id), 
                                       max(valdf_master$node_id)), 
                            as_sf = FALSE) %>% 
  mutate(reach_id = as.factor(reach_id)) # %>% 
  # left_join(nodecov, by = c("node_id", "reach_id"))
```


Map object

```{r}
library(ggmap)
allat <- c(passmapdf$latitude, nodemapdf$latitude)
allon <- c(passmapdf$longitude, nodemapdf$longitude)
pad <- 0.1
bbox <- c(min(allon, na.rm = TRUE) - pad, min(allat, na.rm = TRUE) - pad,
          max(allon, na.rm = TRUE) + pad, max(allat, na.rm = TRUE) + pad)
bbox_zoomin <- c(-122.02, 39.475, -121.98, 39.5)

bgmap <- get_map(location = bbox, maptype = "terrain-background",
                 crop = TRUE)
satmap <- get_map(location = bbox, maptype = "satellite")
satmap_zoomin <- get_map(location = bbox_zoomin, maptype = "satellite")

nodemapdf %>% 
  filter(reach_id == 10)

maplims <- list(xmin = -122.63, xmax = -121.2, ymin = 38.78, ymax = 39.9)
linedf <- with(maplims, data.frame(lon = c(xmin, xmin, xmax, xmax, xmin), 
                                   lat = c(ymin, ymax, ymax, ymin, ymin)))

map_gg <- ggmap(bgmap, darken = c(0.4, "white")) +
  geom_line(aes(x = longitude, y = latitude,
                group = as.factor(pass),
                linetype = pass),
            data = mutate(passmapdf, pass = as.factor(pass)),
            size = 1) + 
  geom_point(aes(x = longitude, y = latitude, color = reach_id), 
             data = nodemapdf) +
  # scale_color_hue(l = 70)
  # scale_color_viridis_d(begin = .2, end = 0.7)
  scale_color_brewer(palette = "Paired")+ 
  xlim(maplims$xmin, maplims$xmax) + 
  ylim(maplims$ymin, maplims$ymax)
push2manuscript(map_gg)

library(legendMap)

map_zoomin <- ggmap(satmap_zoomin, darken = c(0.1, "white")) + 
    geom_point(aes(x = longitude, y = latitude, fill = reach_id), 
             data = dplyr::filter(nodemapdf, reach_id %in% c(4, 5)),
             # data = dplyr::filter(nodemapdf, node_id %in% 258:261),
                          color = "black", shape = 21, size = 3) +
  # scale bar from 3wen/legendMap
  scale_bar(lon = -122.011, lat = 39.479, 
                       distance_lon = 0.5, distance_lat = 0.05, distance_legend = 0.12,
                       dist_unit = "km", legend_colour = "white",
                       legend_size = 5)
push2manuscript(map_zoomin)
```

### Distributions of validation axes variables

```{r}
ggnpxhist <- valdf_gdem %>% 
  filter(agg == "composite") %>%
  filter(variable == "wse") %>%
  mutate(pass = as.factor(pass)) %>% 
  ggplot(aes(x = n_good_pix)) +
  # geom_density(aes(color = pass))
  geom_histogram(aes(fill = pass), color = "gray30")
ggnpxhist

ggnpxviol <- valdf_gdem %>% 
  filter(agg == "composite") %>% 
  filter(variable == "wse") %>% 
  mutate(pass = as.factor(pass)) %>% 
  ggplot(aes(x = pass, y = n_good_pix)) +
  geom_violin()

ggnpxviol
ggnpxhist
push2manuscript(ggnpxhist)
```

```{r}
ggxtkhist <- valdf_gdem %>% 
  filter(variable == "latitude") %>% 
  mutate(pass = as.factor(pass)) %>% 
  ggplot(aes(x = xtrk_dist, fill = pass)) +
  geom_histogram(color = "gray40")

ggxtkhist

```

```{r}

npx_xtk_gg <- valdf_gdem %>% 
  filter(variable == "wse", agg == "composite") %>% 
  mutate(pass = as.factor(pass), 
         shape = as.numeric(pass) + 20) %>% 
  ggplot(aes(x = xtrk_dist, y = n_good_pix, fill = pass,
             shape = pass)) +
  geom_point(alpha = 0.4) + 
  # scale_shape(limits = 21:23) +
  scale_shape_manual(values = 21:23) +
  scale_y_log10() +
  annotation_logticks(sides = "l") + 
  xlab("cross-track distance (m)") +
  ylab("number of pixels")

push2manuscript(npx_xtk_gg)
```

### Hydrologic conditions

```{r}
flowdf_plot <- flowdf %>% 
  filter(date %in% rundates) %>% 
  left_join(rundatedf, by = c("date", "flow")) %>% 
  mutate(pass = as.factor(pass))

flowdf %>% 
  filter(date >= "2009-01-15", date < "2009-04-01") %>% 
  ggplot(aes(x = date, y = flow)) + 
  geom_line() + 
  geom_vline(aes(xintercept = date, color = pass), 
             data = flowdf_plot, linetype = 1)

ecdf_gg <- cdfdf %>% 
  ggplot(aes(x = flow, y = cdf)) + 
  geom_line() + 
  geom_point(aes(color = day), data = flowdf_plot, size = 3) +
  geom_text(aes(label = day), data = flowdf_plot, nudge_x = 0) + 
  scale_x_log10() +
  annotation_logticks(sides = "l") + 
  theme(legend.position = "none")
  # coord_flip()
ecdf_gg
push2manuscript(ecdf_gg)
```

### Validation results, part 1

#### Histograms

```{r}
# ambiguous_nodes(rodir(51))
histgg1 <- valdf_gdem %>% 
  filter(agg == "composite") %>% 
  rt_val_hist(scale = TRUE, plot = TRUE, 
                       curve = TRUE,
                       vars = valvars) + 
  xlim(-8, 8)

histgg1
histgg2 <- valdf_srtm %>% 
  rt_val_hist(scale = TRUE, plot = TRUE, 
                       curve = TRUE,
                       vars = valvars) +
  xlim(-8, 8)
# histdf <- rt_val_hist(valdf_master, scale = TRUE, plot = FALSE)
# 
# histgg1 <- histdf %>%     
#   dplyr::filter(variable %in% valvars) %>% 
#   ggplot(aes(x = err)) +
#   geom_density(aes(color = as.factor(day))) +
#   # geom_histogram(aes(y = ..density.., fill = as.factor(day), 
#   #                    group = day), position = "dodge",
#   #                bins = 15) +
#   facet_wrap(~variable, scales = "free") +
#   stat_function(fun = dnorm, args = list(mean = 0, sd = 1), color = "blue") +
#   scale_fill_brewer(palette = "Set1")
histgg1
histgg2
push2manuscript(histgg1)
push2manuscript(histgg2)

# ggplotly(histgg1)
```


```{r violin-plots}
valdf_gdem %>% 
  # glimpse() %>%
  filter(variable %in% valvars) %>% 
  transmute(reach_id, node_id, variable = as.factor(variable),
            pass = as.factor(pass), day, 
            scaled_error = pixc_err / sigma_est) %>% 
  ggplot(aes(x = variable, fill = pass, y = scaled_error)) + 
  geom_violin(position = position_dodge(0.5))
```


Node-area plots for bad nodes

```{r}
badnodes <- c(286, 360, 301)
# val_map_node(rodir(51), nodes = badnodes, maxpixels = 5000, 
#              pcv2 = "pcv_gdem_dil2.nc")

nodearea_plot(pixc_joined = join_pixc(rodir(18)), nodes = badnodes, 
              node_truth = rt_read(fs::path(rodir(18), "rt_gdem.nc")))
```

#### QQ plots

```{r}

qqgg_nodes_composite_low <- valdf_gdem %>% 
  filter(agg == "composite") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

save_plot(qqgg_nodes_composite_low, type = "qq", scale = "node", 
          agg = "composite", noise = "low", height = 4, width = 5.5)

qqgg_nodes_frac_low <- valdf_gdem %>% 
  filter(agg == "frac") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

save_plot(qqgg_nodes_frac_low, type = "qq", scale = "node", 
          agg = "frac", noise = "low", height = 4, width = 5.5)


qqgg_nodes_simple_low <- valdf_gdem %>% 
  filter(agg == "simple") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

qqgg_nodes_simple_low
save_plot(qqgg_nodes_simple_low, type = "qq", scale = "node", 
          agg = "simple", noise = "low", height = 4, width = 5.5)



qqgg_nodes_composite_high <- valdf_srtm %>% 
  filter(agg == "composite") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

save_plot(qqgg_nodes_composite_high, type = "qq", scale = "node", 
          agg = "composite", noise = "high", height = 4, width = 5.5)

qqgg_nodes_frac_high <- valdf_srtm %>% 
  filter(agg == "frac") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

save_plot(qqgg_nodes_frac_high, type = "qq", scale = "node", 
          agg = "frac", noise = "high", height = 4, width = 5.5)


qqgg_nodes_simple_high <- valdf_srtm %>% 
  filter(agg == "simple") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_qq(vars = valvars, groupvars = c("variable", "day")) + 
  geom_point(aes(color = day)) +
  scale_color_brewer(palette = "Set1") + ylab("standarized error") +
  theme(legend.position = "bottom")

qqgg_nodes_simple_high
save_plot(qqgg_nodes_simple_high, type = "qq", scale = "node", 
          agg = "simple", noise = "high", height = 4, width = 5.5)


```

```{r}
badnodes(valdf_frac, variable = "width")


```


#### Scatterplot

```{r}
scattergg1 <- valdf_gdem %>% 
  filter(agg == "composite") %>% 
  mutate(day = as.factor(day)) %>% 
  rt_val_scatter(variables = valvars, yvar = "relerr", plot = FALSE) %>% 
  ggplot(aes(x = xval, y = yval)) +
  # Add ribbons
  geom_ribbon(aes(ymin = -1.96, ymax = 1.96), fill = "#dddddd") +
  geom_ribbon(aes(ymin = -1, ymax = 1), fill = "#aaaaaa") +
  # add points
  geom_point(aes(color = day), alpha = 0.6) +
    facet_wrap(~variable, scales = "free") +
    ylab("relative error") + xlab("Node ID") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

push2manuscript(scattergg1)
scattergg1
# ggplotly(scattergg1)

```

Scatterplots against npixc, xtk dist

```{r}
errggdf <- valdf_gdem %>% 
  # filter(variable == "height") %>% 
  filter(variable %in% valvars) %>% 
  mutate(scaled_err = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  select(run, pass, day, node_id, reach_id, variable,
         pixc_err,
         n_good_pix, xtrk_dist) %>% 
  gather(key = "what", value = "value", -run:-pixc_err)
err_gg1 <- errggdf %>% 
  filter(node_id != 438) %>% 
  ggplot(aes(x = value, color = pass)) +
  facet_grid(variable ~ what, scales = "free") +
  geom_point(aes(y = pixc_err), alpha = 0.25)
err_gg1
push2manuscript(err_gg1)
```

```{r}
uncggdf <- valdf_gdem %>% 
  # filter(variable == "height") %>% 
  filter(variable %in% valvars) %>% 
  mutate(xtrk_dist = abs(xtrk_dist),
         scaled_err = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  select(run, pass, day, node_id, reach_id, variable,
         sigma_est,
         n_good_pix, xtrk_dist) %>% 
  gather(key = "what", value = "value", -run:-sigma_est)
unc_gg1 <- ggplot(uncggdf, aes(x = value, color = pass)) +
  facet_grid(variable ~ what, scales = "free") +
  geom_point(aes(y = sigma_est), alpha = 0.25) +
  scale_y_log10() +
  # scale_x_log10() +
  annotation_logticks(sides = "l")
unc_gg1
push2manuscript(unc_gg1)
```

```{r}
scalerrggdf <- valdf_gdem %>% 
  # filter(variable == "height") %>% 
  filter(variable %in% valvars) %>% 
  mutate(xtrk_dist = abs(xtrk_dist),
         scaled_err = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  group_by(variable) %>% 
  mutate(sigma_adj = sigma_est / max(sigma_est)) %>% 
  ungroup() %>% 
  select(run, pass, day, node_id, reach_id, variable,
         scaled_err,
         # sigma_adj, 
         n_good_pix, xtrk_dist) %>% 
  gather(key = "what", value = "value", -run:-scaled_err)
scalerr_gg1 <- ggplot(scalerrggdf, aes(x = value, color = pass)) +
  facet_grid(variable ~ what, scales = "free") +
  geom_point(aes(y = scaled_err), alpha = 0.25)
scalerr_gg1
push2manuscript(scalerr_gg1)

```

Trying a different way, separating n_good_pix from xtrk_dist

```{r}
goodpixdf <- valdf_gdem %>% 
  filter(variable %in% valvars) %>% 
  mutate(xtrk_dist = abs(xtrk_dist),
         scaled_err = pixc_err / sigma_est,
         pass = as.factor(pass)) %>% 
  select(run, pass, day, node_id, reach_id, variable,
         n_good_pix,
         pixc_err, sigma_est, scaled_err) %>% 
  gather(key = "what", value = "value", -run:-n_good_pix)

glimpse(goodpixdf)

goodpix_gg1 <- ggplot(goodpixdf, aes(x = n_good_pix, color = pass)) +
  facet_wrap(what ~ variable, scales = "free_y") +
  geom_point(aes(y = value), alpha = 0.25) +
  scale_x_log10()
goodpix_gg1

```




### Flow condition

Can I do a violin plot?

```{r flow-cond-violin}
valdf_gdem %>% 
  filter(variable %in% valvars) %>% 
  mutate(scaled_error = pixc_err / sigma_est,
         pass = as.factor(pass), 
         date = lubridate::ymd(sprintf("2009%04d", day))) %>%
  left_join(flowdf, by = "date") %>% 
  ggplot(aes(x = flow, y = scaled_error)) + 
  geom_point(aes(color = pass, group = pass), 
             # position = position_jitterdodge(jitter.width = 0.01, dodge.width = 0.005), 
             alpha = 0.2) + 
  facet_wrap(~variable, scales = "free_y") +
  scale_x_log10() + annotation_logticks(sides = "b")
  geom_violin()
```



## Reach data

scatterplot

```{r}

scatter_reach_simple_low <- reachvaldf_simple %>% 
  filter(refdem == "GDEM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_simple_low, "scatter", "reach", "simple", "low", width = 7, height = 5)


scatter_reach_frac_low <- reachvaldf_frac %>% 
  filter(refdem == "GDEM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_frac_low, "scatter", "reach", "frac", "low", width = 7, height = 5)

scatter_reach_composite_low <- reachvaldf_composite %>% 
  filter(refdem == "GDEM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_composite_low, "scatter", "reach", "composite", "low", width = 7, height = 5)


scatter_reach_simple_high <- reachvaldf_simple %>% 
  filter(refdem == "SRTM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_simple_high, "scatter", "reach", "simple", "high", width = 7, height = 5)


scatter_reach_frac_high <- reachvaldf_frac %>% 
  filter(refdem == "SRTM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_frac_high, "scatter", "reach", "frac", "high", width = 7, height = 5)

scatter_reach_composite_high <- reachvaldf_composite %>% 
  filter(refdem == "SRTM") %>%
  mutate(day = as.factor(day)) %>% #group_by(variable) %>% summarize(n = n())
  rt_val_scatter(yvar = "relerr", variables = valvars) + 
  geom_point(aes(y = yval, color = day)) +
  ylab("Scaled Error") + xlab("Reach ID") +
  scale_color_brewer(palette = "Set1") +
  scale_x_continuous(breaks = 1:10, labels = 1:10)
save_plot(scatter_reach_composite_high, "scatter", "reach", "composite", "high", width = 7, height = 5)



```

Hypothesis test


```{r, eval = FALSE}
reachht <- reachvaldf %>% 
  dplyr::filter(variable %in% valvars) %>% 
  rt_hyptest()

reachht_db <- reachvaldf %>% 
  dplyr::filter(variable %in% valvars) %>% 
  rt_hyptest(debias = TRUE)

reachht$pval_debias <- reachht_db$pval

push2manuscript(reachht)
kable(reachht)
```
