---
title: "random and systematic uncertainty"
author: "Mark Hagemann"
date: "4/11/2019"
output: 
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
library(dplyr)
opts_chunk$set(echo = FALSE)
```

## Uncertainty decomposition


- `height_u` is total 1-sigma uncertainty ($\sigma$)
- `height_u_r` ($\sigma_r$) is component of uncertainty that is independent between features
- The rest is systematic, call that `height_u_s` ($\sigma_s$)

$$
\sigma = \sqrt{\sigma_s^2 + \sigma_r^2}
$$


## Simple example

Average height of 3 nodes

```{r}
exdf <- data.frame(node = 1:3, height = 6:4, height_u = c(2.5, 2.5, 1.5),
                   height_u_r = c(2, 2, 1))

exdf %>% 
  kable()
```

$$
\sigma = \sqrt{\sigma_s^2 + \sigma_r^2}
$$


## Simple example

Average height of 3 nodes

```{r}
exdf2 <- data.frame(node = as.character(1:3), height = 6:4, height_u = c(2.5, 2.5, 1.5),
                   height_u_r = c(2, 2, 1), height_u_s = c(1.5, 1.5, 1.118), 
                   stringsAsFactors = FALSE)

exdf2 %>% 
  kable()
```

$$
\sigma_s = \sqrt{\sigma^2 - \sigma_r^2}
$$



## Simple example

Average height of 3 nodes

```{r}
exdf_agg <- exdf2 %>% 
  summarize(height = mean(height), height_u_s = mean(height_u_s),
            height_u_r = 1 / 3 * sqrt(sum(height_u_r^2))) %>% 
  mutate(node = "mean", height_u = sqrt(height_u_r^2 + height_u_s^2))


exdf2 %>% 
  rbind(exdf_agg) %>% 
  kable(digits = 3)
```

- $\sigma^*_s \le \text{mean}(\sigma_{s})$
- $\sigma^*_r = \frac{1}{N}\sqrt{\sum_{i}\sigma_{r,i}^2}$
- $\sigma^* = \sqrt{\sigma_s^{*2} + \sigma_r^{*2}}$

## Illustration

Cumulative error as aggregate over 100 features

```{r}
sysvec <- runif(100, 0, 0.2)
randvec <- runif(100)
totvec <- sqrt(sysvec^2 + randvec^2)

errvec <- rnorm(100, 0, randvec) + rnorm(1) * sysvec

cumsys <- cumsum(sysvec) / 1:100
cumrand <- sqrt(cumsum(randvec^2)) / 1:100
cumtot <- sqrt(cumrand^2 + cumsys^2)
cumerr <- cumsum(errvec) / 1:100

plotdf <- data.frame(node = 1:100, sys = cumsys, 
                     rand = cumrand, tot = cumtot, err = cumerr)

library(ggplot2)
plotdf %>% 
  ggplot(aes(x = node)) + 
  geom_line(aes(y = sys), color = "blue") + 
  geom_line(aes(y = rand), color = "red") + 
  geom_line(aes(y = tot), color = "gray50") +
  theme_bw()


```

