---
title: "Tools for Validating SWOT River Products"
author: "Mark Hagemann"
date: "3/29/2019"
output: 
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
library(rivertile)
library(leaflet)
library(dplyr)
library(ggplot2)

opts_chunk$set(echo = FALSE)

theme_set(theme_bw())

sacdir <- "~/Documents/swot-error/output/sac18"
```


```{r, echo = FALSE}
sacrtnode <- rt_read(fs::path(sacdir, "rt.nc"), group = "nodes")
sacrtreach <- rt_read(fs::path(sacdir, "rt.nc"), group = "reaches")

sacpixc <- pixc_read(fs::path(sacdir, "pixel_cloud.nc"))
sacpcv <- pixcvec_read(fs::path(sacdir, "pcv.nc"))

sacpixcjoin <- join_pixc(sacdir) %>% 
  dplyr::rename(node_id = node_index, reach_id = reach_index)

sacvalnode <- rt_valdata(sacdir, "nodes")
sacvalreach <- rt_valdata(sacdir, "reaches")

```



## Tools for Validating SWOT River Products

1. **rivertile** R package
2. **rivertile-viz** interactive app (Shiny)

## Motivation

SWOT observations of rivers are processed using **RiverObs**

<div class="columns-2">
```{r, echo = FALSE, fig.width=3.5, fig.height = 4}

nodepixc <- sacpixcjoin %>% 
  dplyr::filter(node_id == 333)

reachids <- sort(unique(sacrtnode$reach_id))
nreaches <- length(reachids)
dkcols <- RColorBrewer::brewer.pal(n = 8, name = "Set3")
pal <- leaflet::colorNumeric(palette = rep(dkcols, length.out = nreaches), 
                             domain = reachids)

classes <- c(1, 2, 3, 4, 22, 23, 24)
classlabs <- c("land", "land_near_water", "water_near_land", "open_water",
               "land_near_dark_water", "dark_water_edge", "dark_water")
classpal <- colorFactor(palette = "Set1", domain = classes)


leaflet(sacrtnode) %>% 
  addTiles() %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   popup = ~paste(sprintf("reach: %s\nnode: %s", 
                                          reach_id, node_id)),
                   opacity = 0.8,
                   color = ~pal(reach_id),
                   radius = 2) %>% 
  addCircleMarkers(~longitude, ~latitude, stroke = FALSE,
                   radius = 8, fillOpacity = 0.7, 
                   popup = ~paste(sprintf("reach: %s\nnode: %s", 
                                          reach_id, node_id)),
                   fillColor = ~classpal(classification),
                   data = nodepixc)
  
```

**Data Products**

- Pixel Cloud
- River Tile
	- Nodes
	- Reaches
  - PixcVEC
\<\div\>

## Motivation

SWOT observations of rivers are processed using **RiverObs**

<div class="columns-2">
```{r, echo = FALSE, fig.width=3.5, fig.height = 4}

nodepixc <- sacpixcjoin %>% 
  dplyr::filter(node_id == 333)

reachids <- sort(unique(sacrtnode$reach_id))
nreaches <- length(reachids)
dkcols <- RColorBrewer::brewer.pal(n = 8, name = "Set3")
pal <- leaflet::colorNumeric(palette = rep(dkcols, length.out = nreaches), 
                             domain = reachids)

classes <- c(1, 2, 3, 4, 22, 23, 24)
classlabs <- c("land", "land_near_water", "water_near_land", "open_water",
               "land_near_dark_water", "dark_water_edge", "dark_water")
classpal <- colorFactor(palette = "Set1", domain = classes)


leaflet(sacrtnode) %>% 
  addTiles() %>% 
  addCircleMarkers(~longitude, ~latitude, 
                   popup = ~paste(sprintf("reach: %s\nnode: %s", 
                                          reach_id, node_id)),
                   opacity = 0.8,
                   color = ~pal(reach_id),
                   radius = 2) %>% 
  addCircleMarkers(~longitude, ~latitude, stroke = FALSE,
                   radius = 8, fillOpacity = 0.7, 
                   popup = ~paste(sprintf("reach: %s\nnode: %s", 
                                          reach_id, node_id)),
                   fillColor = ~classpal(classification),
                   data = nodepixc)
  
```

These contain **Observations** (or **estimates**)

- Location
- Classification (pixels)
- Height
- Area
- Width (nodes, reaches)
- Slope (reaches)
<\div>


## Motivation

**Goal** is to validate SWOT river products against synthetic (gdem) *truth*

- Validate estimates against truth
- Validate uncertainty estimates against empirical errors

## **rivertile** package

An R package with functions to

- Read RiverObs output
- Do simple data joins, filters, transforms
- Compare against synthetic data
- Plot/visualize results\
- Re-aggregate nodes to reaches (soon)

## **rivertile** node example

```{r, echo = TRUE, fig.height=3}
sacdir <- "~/Documents/swot-error/output/sac18" # contains RiverObs output
sacvaldata <- rt_valdata(sacdir, group = "nodes") # Validate against synthetic
rt_val_hist(sacvaldata, vars = c("height", "width", "area_total"), 
            scale = TRUE, curve = TRUE)
```

## **rivertile** reach example

```{r, echo = TRUE, fig.height = 3}
sacvaldata_r <- rt_valdata(sacdir, group = "reaches") # Validate against synthetic

# Plot relative errors against reach ID
rt_val_scatter(sacvaldata_r, variables = c("height", "width", "slope"), 
               yvar = "relerr")
```

## **rivertile-viz** Shiny app

- An interactive visualization tool for RiverObs output/validation
- Built using R's [Shiny](https://shiny.rstudio.com/) app platform
- Uses **rivertile** package

[Link to app](https://markwh.shinyapps.io/rivertile-viz/)

