---
title: "Research update 20190809"
author: "Mark Hagemann"
date: "8/9/2019"
output: 
  ioslides_presentation:
    incremental: true
---




```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE
)

opts_knit$set(root.dir = "~/Documents/swot-error/")
```


```{r}
library(ProjectTemplate)
load.project()

theme_set(theme_bw())

sival_simple <- rt_valdata("output/area-error/orig_si/simple/")
sival_composite <- rt_valdata("output/area-error/orig_si/composite/")
sival_frac <- rt_valdata("output/area-error/orig_si/frac/")

origval_simple <- rt_valdata("output/area-error/orig/simple/")
origval_composite <- rt_valdata("output/area-error/orig/composite/")
origval_frac <- rt_valdata("output/area-error/orig/frac/")

```




## Background

- SWOT will measure river width, height, slope, etc. 
- Measurements are provided with estimated uncertainty
- Task: validate these estimates of uncertainty
- Use simulated SWOT data products from Sacramento River, CA

## Remember QQ plots? 

- Here's one validating river height uncertainty

```{r}
origval_composite %>% 
  filter(variable == "wse") %>% 
  rt_val_qq() + 
  ylab("standardized error")
```

## Width QQ plot

```{r}

bind_rows(composite = origval_composite, 
          frac = origval_frac, 
          simple = origval_simple, .id = "method") %>% 
  filter(variable == "width") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method) + 
  ylab("standardized error") +
  ylim(-8, 15)
```



## Updated uncertainty model

```{r}

bind_rows(composite = sival_composite, 
          frac = sival_frac, 
          simple = sival_simple, .id = "method") %>% 
  filter(variable == "width") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method) +
  ylab("standardized error") +
  ylim(-8, 15)
```


## BREAKING NEWS

- Uncertainty is always calculated using "composite" model?!

```
area_unc = area_uncert(
    pixel_area, water_fraction, water_fraction_uncert, darea_dheight,
    klass, Pfd, Pmd, good, Pca=Pca, Pw=Pw, Ptf=Ptf, ref_dem_std=ref_dem_std,
    interior_water_klass=interior_water_klass,
    water_edge_klass=water_edge_klass, land_edge_klass=land_edge_klass,
    method='composite')
```

## Updated (original water fraction uncertainty)

```{r}
origval_simple_new <- rt_valdata("output/area-error/orig_new/simple/")
origval_composite_new <- rt_valdata("output/area-error/orig_new/composite/")
origval_frac_new <- rt_valdata("output/area-error/orig_new/frac/")

bind_rows(composite = origval_composite_new, 
          frac = origval_frac_new, 
          simple = origval_simple_new, .id = "method") %>% 
  filter(variable == "area_total") %>% 
    rt_val_qq(groupvars = "method") +
  facet_wrap(~method)
```

