---
title: "Sacramento Error Validation--new db"
author: "Mark Hagemann"
date: "2/13/2019"
output: 
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
library(leaflet)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
               cache = TRUE, cache.rebuild = TRUE)
opts_knit$set(root.dir = "~/Documents/swot-error/")
```

```{r}
library(ProjectTemplate)
load.project()
valdata <- rt_valdata("output/sac15", group = "nodes") %>% 
  dplyr::filter(variable != "area_detct") 

```

## Bias, stdev, RMSE

```{r}
valdata %>% 
  # glimpse() %>% 
  mutate(pixc_relerr = pixc_err / sigma_est) %>% 
  group_by(variable) %>% 
  summarize(bias = mean(pixc_err),
            sd = sd(pixc_err),
            rel_bias = mean(pixc_relerr),
            rel_sd = sd(pixc_relerr)) %>% 
  mutate(rmse = sqrt(bias^2 + sd^2), 
         rel_rmse = sqrt(rel_bias^2 + rel_sd^2)) %>% 
  dplyr::select(variable, bias, sd, rmse, rel_bias, rel_sd, rel_rmse) %>% 
  kable(digits = 2)
  
```


## Coverage rates

How well do error percentiles match theoretical confidence intervals?

```{r}
covfun <- function(x, sigma, pctl) {
  pctl <- pctl / 100
  bnd <- -qnorm((1 - pctl) / 2, mean = 0, sd = 1)
  numin <- sum(abs(x / sigma) <= bnd)
  out <- numin / length(x) * 100
  out
}

valdata %>% 
  # glimpse() %>% 
  group_by(variable) %>% 
  summarize(
    `68 (1-sigma)` = covfun(pixc_err, sigma_est, 68),
    `90` = covfun(pixc_err, sigma_est, 90),
    `95 (2-sigma)` = covfun(pixc_err, sigma_est, 95),
    `99` = covfun(pixc_err, sigma_est, 99)
    ) %>% 
  kable(digits = 2)
```

## Coverage rates

The same, with bias removed

```{r}
# Now with bias removed
valdata %>% 
  # glimpse() %>% 
  group_by(variable) %>% 
  mutate(pixc_err = pixc_err - mean(pixc_err, na.rm = TRUE)) %>% 
  summarize(
    `68 (1-sigma)` = covfun(pixc_err, sigma_est, 68),
    `90` = covfun(pixc_err, sigma_est, 90),
    `95 (2-sigma)` = covfun(pixc_err, sigma_est, 95),
    `99` = covfun(pixc_err, sigma_est, 99)
    ) %>% 
  kable(digits = 2)
```



## Error histograms (pixc - gdem)

```{r}
valdata %>% 
  ggplot(aes(x = pixc_err)) +
  geom_histogram(aes(y = ..density..), bins = 15) +
  facet_wrap(~variable, scales = "free")
```


## Relative Error histograms (err / sigma)

Adjusting relative to estimated uncertainty stdev should produce distribution with stdev=1

```{r}
valdata %>% 
  ggplot(aes(x = pixc_err / sigma_est)) +
  geom_histogram(aes(y = ..density..), bins = 15) +
  facet_wrap(~variable, scales = "free")
```

## Relative error with bias removed

Uncertainty estimates don't account for bias/long-wavelength error, validate against bias-adjusted errors. 

```{r}
valdata %>% 
  group_by(variable) %>% 
  mutate(pixc_err_adj = pixc_err - mean(pixc_err, na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::filter(abs(pixc_err_adj / sigma_est) < 125) %>% 
  # dplyr::filter(variable == "height") %>%
  # arrange(pixc_err_adj)
  ggplot(aes(x = pixc_err_adj / sigma_est)) +
  geom_histogram(aes(y = ..density..), bins = 15) +
  facet_wrap(~variable, scales = "free")
```

## Relative error with bias removed

Compare to standard normal distribution

```{r}
valdata %>% 
  group_by(variable) %>% 
  mutate(pixc_err_adj = pixc_err - mean(pixc_err, na.rm = TRUE)) %>% 
  ungroup() %>% 
  dplyr::filter(abs(pixc_err_adj / sigma_est) < 125) %>% 
  # dplyr::filter(variable == "height") %>%
  # arrange(pixc_err_adj)
  ggplot(aes(x = pixc_err_adj / sigma_est)) +
  geom_histogram(aes(y = ..density..), bins = 15) +
  facet_wrap(~variable, scales = "free") +
  stat_function(fun = dnorm, args = list(mean = 0, sd = 1), color = "blue")

```

## Normal quantile-quantile plots - relative errors

If errors are normally distributed, points should lie on the line

```{r}
valdata %>% 
  ggplot(aes(sample = pixc_err / sigma_est)) + 
  geom_qq() +
  geom_qq_line() +
  facet_wrap(~variable, scales = "free")
```

## Worst width error nodes

```{r, eval = FALSE}


lalodata <- valdata %>% 
  dplyr::select(reach_id, node_id, variable, pixc_val) %>% 
  dplyr::filter(variable %in% c("latitude", "longitude")) %>% 
  spread(key = variable, value = pixc_val)
widthdata <- valdata %>% 
  dplyr::filter(variable == "width") %>% 
  dplyr::select(reach_id, node_id, variable, pixc_err) %>% 
  spread(key = variable, value = pixc_err)

mapdata <- left_join(lalodata, widthdata, by = c("reach_id", "node_id"))

pal <- colorFactor(c("blue", "red"), 
                   domain = abs(mapdata$width))

mapdata %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(color = ~pal(abs(width)))
```


```{r}
badnodes <- valdata %>% 
  dplyr::filter(variable == "width") %>% 
  arrange(desc(abs(pixc_err))) %>% 
  `[[`("node_id") %>% 
  `[`(1:4)

pcvdata <- pixcvec_read("output/sac15/pcv.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)

pcvdata_gdem <- pixcvec_read("output/sac15/pcv_gdem.nc") %>% 
  dplyr::filter(node_index %in% badnodes) %>% 
  rename(lat = latitude_vectorproc, lon = longitude_vectorproc)


pcvdata  %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(radius = 1, popup = ~format(node_index)) %>% 
  addCircleMarkers(radius = 1, color = "red", data =pcvdata_gdem)

```


## Heights by node

blue: 1-sigma; pink: 95% confidence interval

```{r}
valdata %>% 
  dplyr::filter(variable == "height") %>% 
  ggplot(aes(x = node_id)) +
  geom_ribbon(aes(ymin = pixc_val - 1.96 * sigma_est, 
                  ymax = pixc_val + 1.96 * sigma_est), 
              fill = "pink") +
  geom_ribbon(aes(ymin = pixc_val - sigma_est, 
                  ymax = pixc_val + sigma_est), 
              fill = "#7780ff") +
  geom_point(aes(y = pixc_val), shape = "+") +
  geom_line(aes(y = gdem_val), color = "black") +
  theme_bw()
```

## Height errors by node

blue: 1-sigma; pink: 95% confidence interval

```{r}
valdata %>% 
  dplyr::filter(variable == "height") %>% 
  ggplot(aes(x = node_id)) +
  geom_ribbon(aes(ymin = -1.96 * sigma_est, 
                  ymax = 1.96 * sigma_est), fill = "pink") +
  geom_ribbon(aes(ymin = -sigma_est, 
                  ymax = sigma_est), fill = "#7780ff") +
  geom_point(aes(y = pixc_err)) +
  theme_bw()
```

## Bias-adjusted height errors by node

blue: 1-sigma; pink: 95% confidence interval

```{r}

valdata %>% 
  dplyr::filter(variable == "height") %>% 
  mutate(err_shift = pixc_err - median(pixc_err, na.rm = TRUE)) %>% 
  ggplot(aes(x = node_id)) +
  geom_ribbon(aes(ymin = -1.96 * sigma_est, 
                  ymax = 1.96 * sigma_est), fill = "pink") +
  geom_ribbon(aes(ymin = -sigma_est, 
                  ymax = sigma_est), fill = "#7780ff") +
  geom_point(aes(y = err_shift)) +
  theme_bw()
```

## Spatial trends in error


```{r}
valdata %>% 
  ggplot(aes(x = node_id, y = pixc_err)) + 
  geom_point() + 
  facet_wrap(~variable, scales = "free") + 
  stat_smooth()
```



## Spatial trends in error

- long-wavelength variations in error are small relative to bias
    - Except in lat/lon
    
```{r, fig.width = 6.5, fig.height = 4.5}
valdata %>% 
  ggplot(aes(x = node_id, y = pixc_err)) + 
  geom_point() + 
  facet_wrap(~variable, scales = "free") + 
  stat_smooth()
```


## Next steps

- Repeat on new dataset (2/11/2019)
- Understand lat/lon errors, improve uncertainty estimate
- Tackle heavy tail of width, area errors
- Quantify long-wavelength height error (bias)
- Understand width, area bias
