---
title: 'Sac, dilation, truth flagging'
author: "Mark Hagemann"
date: "2/26/2019"
output: 
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE)

opts_knit$set(root.dir = "../../")
```

```{r, cache = FALSE}
library(ProjectTemplate)
library(leaflet)
load.project()
devtools::load_all("../rivertile")
```

## Original issue

Large outliers in the node-level width errors. 


```{r}
ridnode <- function(gg) {
  gg$data <- dplyr::filter(gg$data, node_id != 573)
  gg
}


dir15 <- "output/sac15"
valdata <- rt_valdata(dir15)
# rt_valdata(dir15) %>% dplyr::filter(variable == "width") %>% arrange(pixc_err)
rt_val_hist(valdata, vars = c("width")) %>% 
  ridnode()
```

## Diagnosis

- Finer-resolution gdem pixc water search stops before it should:


```{r}
library(leaflet)
plotnodes <- c(290, 303)
val_map_node(dir15, nodes = plotnodes)
```

## Dilation option = 1

- southern node gdem expanded slightly, still does not match

```{r}
val_map_node(dir15, nodes = plotnodes, pcv2 = "pcv_gdem_dil1.nc")
```

## Dilation = 2

- Now a better match between gdem and pixel_cloud

```{r}
val_map_node(dir15, nodes = plotnodes, pcv2 = "pcv_gdem_dil2.nc")
```

## Width error histogram using gdem dilation = 2

- Now we have outliers in the other direction

```{r}

rt_valdata(dir15, gdname = "rt_gdem_dil2.nc") %>% 
  rt_val_hist(vars = c("width")) %>% 
  ridnode()

```


## Worst outliers using dilation=2 gdem

- This is actually 2 different nodes. 

```{r}
valdata1 <- rt_valdata(dir15)
valdata2 <- rt_valdata(dir15, gdname = "rt_gdem_dil1.nc")
valdata3 <- rt_valdata(dir15, gdname = "rt_gdem_dil2.nc")
valdata4 <- rt_valdata(dir15, rtname = "rt_dil.nc", gdname = "rt_gdem_dil2.nc")

val1 <- rt_valdata(dir15, rtname = "rt_gdem_dil1.nc", gdname = "rt_gdem.nc", 
                   keep_na_vars = TRUE) %>% 
    filter(variable == "width") %>% 
    transmute(node_id, pct_disagree = abs(pixc_err) / (pixc_val) * 100) %>% 
    arrange(desc(pct_disagree))
val2 <- rt_valdata(dir15, rtname = "rt_gdem_dil2.nc", gdname = "rt_gdem.nc", 
                   keep_na_vars = TRUE) %>% 
    filter(variable == "width") %>% 
    transmute(node_id, pct_disagree = abs(pixc_err) / (pixc_val) * 100) %>% 
    arrange(desc(pct_disagree))
val3 <- rt_valdata(dir15, rtname = "rt_gdem_dil3.nc", gdname = "rt_gdem.nc", 
                   keep_na_vars = TRUE) %>% 
    filter(variable == "width") %>% 
    transmute(node_id, pct_disagree = abs(pixc_err) / (pixc_val) * 100) %>% 
    arrange(desc(pct_disagree))
val4 <- rt_valdata(dir15, rtname = "rt_gdem_dil4.nc", gdname = "rt_gdem.nc", 
                   keep_na_vars = TRUE) %>% 
    filter(variable == "width") %>% 
    transmute(node_id, pct_disagree = abs(pixc_err) / (pixc_val) * 100) %>% 
    arrange(desc(pct_disagree))



# val_map_node(dir15, nodes = badnodes(valdata1))
# val_map_node(dir15, nodes = badnodes(valdata2), 
#              pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil1.nc")
val_map_node(dir15, nodes = badnodes(valdata3, which = "min", n = 2), 
             pcv1 = "pcv.nc", pcv2 = "pcv_gdem_dil2.nc")
# val_map_node(dir15, nodes = badnodes(valdata4), 
#              pcv1 = "pcv_dil.nc", pcv2 = "pcv_gdem_dil2.nc")
```

## Instead of correcting gdem, flag questionable nodes

```{r}
valorig <- rt_valdata(dir15) %>% 
  dplyr::filter(variable == "width") %>% 
  transmute(node_id, variable, pixc_val, pixc_err, 
            pct_err = pixc_err / gdem_val, gdem_val, sigma_est)

valorig %>% 
  left_join(val1, by = "node_id") %>% 
  #glimpse() %>% 
  dplyr::filter(node_id != 573) %>% 
  ggplot(aes(x = pct_disagree, y = pixc_err)) +
  geom_point() + 
  xlab("% gdem disagreement vs no-dilation") +
  ylab("node width error (vs. gdem-derived)") +
  ggtitle("dilation=1 gdem disagreement as error predictor")
```

## Instead of correcting gdem, flag questionable nodes

```{r}
valorig %>% 
  left_join(val2, by = "node_id") %>% 
  #glimpse() %>% 
  dplyr::filter(node_id != 573) %>% 
  ggplot(aes(x = pct_disagree, y = pixc_err)) +
  geom_point() + 
  xlab("% gdem disagreement vs no-dilation") +
  ylab("node width error (vs. gdem-derived)") +
  ggtitle("dilation=2 gdem disagreement as error predictor")
```

## Instead of correcting gdem, flag questionable nodes

```{r}
valorig %>% 
  left_join(val3, by = "node_id") %>% 
  #glimpse() %>% 
  dplyr::filter(node_id != 573) %>% 
  ggplot(aes(x = pct_disagree, y = pixc_err)) +
  geom_point() + 
  xlab("% gdem disagreement vs no-dilation") +
  ylab("node width error (vs. gdem-derived)") +
  ggtitle("dilation=3 gdem disagreement as error predictor")
```

## Instead of correcting gdem, flag questionable nodes

```{r}
valorig %>% 
  left_join(val4, by = "node_id") %>% 
  #glimpse() %>% 
  dplyr::filter(node_id != 573) %>% 
  ggplot(aes(x = pct_disagree, y = pixc_err)) +
  geom_point() + 
  xlab("% gdem disagreement vs no-dilation") +
  ylab("node width error (vs. gdem-derived)") +
  ggtitle("dilation=4 gdem disagreement as error predictor")
```

## Flag definition

- Best comparison: 
    - dilation=0 gdem, dilation=2 gdem
- Threshold for flag: 
    - 15% difference (relative to larger width)
- Sacramento results:
    - Remove 6 points out of 366
    - 3 are really outliers (50% false-positive rate)
    - Bias (across all nodes) goes from 14.7m to 11.9m 

## Histograms

```{r}
valorig %>% 
  dplyr::filter(!(node_id %in% c(val2$node_id[1:6], 573))) %>% 
  rt_val_hist() + ggtitle("Flagged nodes removed")
```

## Histograms

```{r}
valorig %>% 
  dplyr::filter(!(node_id %in% c(573))) %>%
  rt_val_hist() + ggtitle("Before flagging")
```

